### 2017-10-28 paper/cvpr2018/cvpr2018_draft.tex

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\cvprfinalcopy

\def\cvprPaperID{16} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\begin{document}
\title{DeepTrack: car trajectory prediction for autonomous driving}

\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
{\tt\small dwu,...@szu.edu.cn}}
\maketitle
%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}
%%%%%%%%% BODY TEXT
\section{Introduction}

\section{Related Work}

\section{Proposed Algorithm}

\section{Experiments}
\subsection{Dataset collection}
We collect car trajectory evaluation dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.

\section{Conclusions}

\section*{Details of the Code}

\section*{Acknowledgment}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}
\end{document}

### 2017-11-01 paper/cvpr2018/cvpr2018_draft.tex

@@
 %%%%%%%%% BODY TEXT
+%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/ 
+%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
+%%% https://cs.stanford.edu/people/widom/paper-writing.html
 \section{Introduction}
@@
 \section{Related Work}
+
+%%% TY: write related work for object detection, segmentation, instance segmentation
+
+%%% DW: write related work for visual tracking
+%%% DW: write related dataset for autonoumous driving
+
+%% DW: (1)traditional segmentic segmentation dataset 
+%% DW: (2) synthetic dataset
+%% DW: (3) temporal consistent dataset
+
+Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK.
+However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
+
+Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
+
+KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks.
+However, a limited 430 labelled images are provided for semantic segmentation.
+
+A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city.
+The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
+
+More recently, larger project are constructed:
+Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes.
+
+The use of synthetic data has increased considerably in recent years within computer vision community.
+~\cite{mueller2016benchmark} provides a synthetic dataset generation and online tracker evaluation.
+In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
+Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
+
+A fine annotated images in Cityscape dataset requires on average 1.5 hours which is very labor intensive.
+Thus, the cost of scaling large project would required a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
+For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
+This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.p
+%%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
 

### 2017-11-05 paper/cvpr2018/cvpr2018_draft.tex
Paper writing: introduction and experiment section

@@
 \begin{document}
-\title{DeepTrack: car trajectory prediction for autonomous driving}
+\title{DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving}
 
@@
 
+\textbf{\emph{1. What is the problem?}}
+
+Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and than parse the scene to make a driving policy (usually by a controller with if-then-else rules), and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
+
+In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of cars given its past information.
+
+\textbf{\emph{2. Why is it interesting and important?}}
+
+Driver reaction time is a crucial factor for a human driver to react to the traffic participants.
+Driver reaction time includes recognising the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake).
+Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
+Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.p
+
+\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}
+
+Individually, for computer vision community, it's an unsolved problem. e.g.: object detection, semantic segmentation, instance segmentation, etc.
+
+Currently, most work focus on static images. However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by sequence of input frames instead of simply one static frame.
+
+\textbf{\emph{4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
+
+Scene parsing results contains quite some spurious information.
+
+In traditional vision based tracking problems (\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
+However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).
+
+Currently research community lacks proper evaluation metrics for deciding the temporally future prediction result.
+
+\textbf{\emph{5. What are the key components of my approach and results? Also include any specific limitations.}}
+
+In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction.
+
+% Then have a final paragraph or subsection: "Summary of Contributions".
+It should list the major contributions in bullet form, mentioning in which sections they can be found.
+This material doubles as an outline of the rest of the paper, saving space and eliminating redundancy.
+
+Our contributions are as follows:
+\begin{itemize}
+
+\item We verify the feasibility of predicting the future trajectories of cars for assisting mediated perception framework.
+The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
+
+\item We design various temporal model for the problems of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.
+
+\item We demonstrate the effectiveness of using ``privileged information" further boost the prediction accuracy. [NOT DONE].
+
+\item We construct a time-series dataset for car trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia}.
+
+\end{itemize}
+
 \section{Related Work}
@@
 %%% TY: write related work for object detection, segmentation, instance segmentation
-
+\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
 %%% DW: write related work for visual tracking
 %%% DW: write related dataset for autonoumous driving
+
+\textbf{\emph{2. Visual trackers}}
 
@@
 %% DW: (3) temporal consistent dataset
+
+\textbf{\emph{3. Dataset for autonoumous driving}}
 
@@
 For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
-This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.p
+This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.
+
 %%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
+\textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}
 
 \section{Proposed Algorithm}
+
+\subsection{traffic participants detection}
+
+We utilise two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+
+\subsection{instance tracking}
+
+We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+
+\subsection{trajectory prediction}
+
+We compare two temporal models based on LSTM cells for predicting the car trajectory.
 

### 2017-11-10 code_base/config/synthia_car_trajectory.py
modify for CNN_LSTM_To_FC model

@@ -16,7 +16,7 @@ draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequ
 
 
 # Model
-model_name                   = 'LSTM_ManyToMany'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC']
+model_name                   = 'LSTM_ManyToMany'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
 #random_size_crop             = (350*2, 460*2)      # Random size crop of the image during training
@@ -100,7 +100,7 @@ lstmToFc_output_dim           = 6               # outlayer output: [x,y,w,h, d_m
 # CNN_LSTM_To_FC
 def cnnDict(in_channels, out_channels, kernel_size, stride, padding):
     return {'in_channels': in_channels, 'out_channels': out_channels, 'kernel_size': kernel_size, 'stride': stride, 'padding': padding}
-cnnLstmToFc_conv_paras        = [cnnDict(11,10,3,1,1), cnnDict(10,5,3,1,1),cnnDict(5,2,3,1,1)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
+cnnLstmToFc_conv_paras        = [cnnDict(1,2,3,1,1), cnnDict(2,4,3,1,1),cnnDict(4,4,2,2,0)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
                                                                                       # 'out_channels': ,
                                                                                       # 'kernel_size': ,
                                                                                       # 'stride': ,

### 2017-11-10 code_base/models/PyTorch_PredictModels.py

@@ -193,7 +193,7 @@ class CNN_LSTM_To_FC(nn.Module):
                                   nn.Conv2d(**self.convparas[1]),
                                   nn.ReLU(),
                                   nn.Conv2d(**self.convparas[2]),
-                                  nn.ReLU
+                                  nn.ReLU()
                                   )
 
         # lstm part; build lstm layer, parameters are (input_dim,hidden_size,num_layers)
@@ -220,7 +220,7 @@ class CNN_LSTM_To_FC(nn.Module):
         else:
             self.dtype = torch.FloatTensor
 
-    def forward(self, trajectorys, images, future=0 ):
+    def forward(self, images, trajectorys, future=0 ):
         '''
         :param trajectorys: The moving path train data or test data, type is Variable, size is (batchSize, sequenceSize,featureSize).
         :param images: the input images, may be semantic segmentation or RGB. size as (batchSize, sequenceSize, Cin, Hin, Win)
@@ -228,21 +228,23 @@ class CNN_LSTM_To_FC(nn.Module):
         :return: A list composed of only one element, which is the predicted data, type is Variable, Size is (batchSize, futureSequenceSize, featureSize)
         '''
 
+        batch_size = trajectorys.size(0)
+        sequenceSize = trajectorys.size(1)
         # the return content
         outputs = []
 
         # cnn part:
-        images_data = []
-        for i in range(0, len(images)):
-            cnned_image = self.conv(images[i])
-            image_data = cnned_image.resize(cnned_image.size(0), cnned_image[0].numel())
-            images_data.append(image_data)
+        # images_data = []
+        # for i in range(0, len(images)):
+        images_data = [self.conv(image).view(sequenceSize, -1) for image in images]
+
+            # images_data.append(image_data)
         images_data = torch.stack(images_data, dim=0)
 
         # lstm part:
         # compute with train or test data,the output is hidden_state & cell_state
         # the hn represents hidden_state in each lstm layer, and it involves all the past information through the recurrent process
-        batch_size = trajectorys.size(0)
+
         input_t = trajectorys
         for i in range(0, len(self.hidden_sizes)):
             # init hidden state & cell state, parameters are (numlayers, batchsize, hidden_size)

### 2017-11-10 code_base/models/PyTorch_model_factory.py

@@ -1,6 +1,6 @@
 from code_base.models.PyTorch_fcn import FeatureResNet, SegResNet, iou
 from code_base.models.PyTorch_drn import drn_c_26, drn_d_22, DRNSeg, DRNSegF
-from code_base.models.PyTorch_PredictModels import LSTM_ManyToMany, LSTM_To_FC
+from code_base.models.PyTorch_PredictModels import *
 from code_base.tools.PyTorch_model_training import calc_seq_err_robust
 import torch
 from torchvision import models
@@ -193,6 +193,13 @@ class Model_Factory_LSTM():
                                   future_frame=cf.lstmToFc_future,
                                   output_dim=cf.lstmToFc_output_dim,
                                   cuda=cf.cuda)
+        elif cf.model_name == 'CNN_LSTM_To_FC':
+            self.net = CNN_LSTM_To_FC(conv_paras=cf.cnnLstmToFc_conv_paras,
+                                      input_dims=cf.cnnLstmToFc_input_dims,
+                                      hidden_sizes=cf.cnnLstmToFc_hidden_sizes,
+                                      future_frame=cf.cnnLstmToFc_future,
+                                      output_dim=cf.cnnLstmToFc_output_dim,
+                                      cuda=cf.cuda)
         # Set the loss criterion
         if cf.loss == 'MSE':
             self.crit = nn.MSELoss()
@@ -230,12 +237,17 @@ class Model_Factory_LSTM():
         elif cf.optimizer == 'sgd':
             self.optimiser = optim.SGD(self.net.parameters(), lr=cf.learning_rate, momentum=cf.momentum, weight_decay=cf.weight_decay)
 
-    def train(self, train_input, train_target, cf):
+    def train(self, train_images, train_input, train_target, cf):
         #print('learning rate:', lr)
         # begin to train
+        if cf.model_name == 'CNN_LSTM_To_FC':
+            input = tuple([train_images, train_input])
+        else:
+            input = tuple([train_input])
+
         def closure():
             self.optimiser.zero_grad()
-            out = self.net(train_input)[0]
+            out = self.net(*input)[0]
             loss = self.crit(out, train_target)
             if cf.cuda:
                 print('loss: ', loss.data.cpu().numpy()[0])
@@ -245,17 +257,20 @@ class Model_Factory_LSTM():
             return loss
         self.optimiser.step(closure)
         # output loss
-        out = self.net(train_input)[0]
+        out = self.net(*input)[0]
[…]

### 2017-11-10 code_base/tools/PyTorch_model_training.py

@@ -27,36 +27,34 @@ def prepare_data(cf):
     valid_data = f['valid_data']
     test_data = f['test_data']
     train_data, valid_data, test_data, data_mean, data_std = normalise_data(train_data, valid_data, test_data)
+
     if cf.cuda:
         print('Data using CUDA')
         dtype = torch.cuda.FloatTensor  # Uncomment this to run on GPU
-        valid_input = Variable(torch.from_numpy(valid_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True), requires_grad=False)
-        valid_target = Variable(torch.from_numpy(valid_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True), requires_grad=False)
-        test_input = Variable(torch.from_numpy(test_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True), requires_grad=False)
-        test_target = Variable(torch.from_numpy(test_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True),requires_grad=False)
-        # Many to many input
-        if cf.model_name == 'LSTM_ManyToMany':
-            train_input = Variable(torch.from_numpy(train_data[:, :-1, :]).type(dtype).cuda(async=True), requires_grad=False)
-            train_target = Variable(torch.from_numpy(train_data[:, 1:, :]).type(dtype).cuda(async=True), requires_grad=False)
-        elif cf.model_name == 'LSTM_To_FC':
-            train_input = Variable(torch.from_numpy(train_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True),
-                                   requires_grad=False)
-            train_target = Variable(torch.from_numpy(train_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True),
-                                    requires_grad=False)
     else:
-        valid_input = Variable(torch.from_numpy(valid_data[:, :cf.lstm_input_frame, :]).float(), requires_grad=False)
-        valid_target = Variable(torch.from_numpy(valid_data[:, cf.lstm_input_frame:, :]).float(), requires_grad=False)
-        test_input = Variable(torch.from_numpy(test_data[:, :cf.lstm_input_frame, :]).float(), requires_grad=False)
-        test_target = Variable(torch.from_numpy(test_data[:, cf.lstm_input_frame:, :]).float(), requires_grad=False)
-        # Many to many input
-        if cf.model_name == 'LSTM_ManyToMany':
[…]

### 2017-11-10 code_base/tools/PyTorch_model_training.py
modify for CNN_LSTM_To_FC model

@@ -54,7 +54,7 @@ def prepare_data(cf):
     valid_images = Variable(torch.zeros(valid_input.size(0), valid_input.size(1), 1, 100, 100).type(dtype), requires_grad=False)
     test_images = Variable(torch.zeros(test_input.size(0), test_input.size(1), 1, 100, 100).type(dtype), requires_grad=False)
 
-    return train_images, valid_images, test_images, train_input, train_target, valid_input, valid_target, test_input, test_target, data_mean, data_std,train_images
+    return train_images, valid_images, test_images, train_input, train_target, valid_input, valid_target, test_input, test_target, data_mean, data_std
 
 
 def calc_seq_err_robust(results, rect_anno, focal_length):

### 2017-11-10 code_base/Synthia_car_trajectory.py
for cudadecives

@@ -1,6 +1,7 @@
 import argparse
 import os
 import sys
+os.environ('CUDA_VISIBLE_DEVICES')='1'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-10 code_base/Synthia_car_trajectory.py
for local

@@ -1,7 +1,8 @@
 import argparse
 import os
 import sys
-os.environ('CUDA_VISIBLE_DEVICES')='1'
+import os
+os.environ['CUDA_VISIBLE_DEVICES']='3'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-10 code_base/Synthia_semantic.py
pool figure add

@@ -1,0 +1,90 @@
+import argparse
+import os
+os.environ['CUDA_VISIBLE_DEVICES'] = '3'
+import sys
+# Di Wu add the following really ugly code so that python can find the path
+sys.path.append(os.getcwd())
+import time
+from datetime import datetime
+
+from code_base.tools.PyTorch_data_generator import Dataset_Generators_Cityscape, Dataset_Generators_Synthia
+from code_base.models.PyTorch_model_factory import Model_Factory
+from code_base.config.configuration import Configuration
+from code_base.tools.utils import HMS, configurationPATH
+
+
+# Train the network
+def process(cf):
+
+    print(' ---> Init experiment: ' + cf.exp_name + ' <---')
+    # Create the data generators
+    # DG = Dataset_Generators_Cityscape(cf)
+    DG = Dataset_Generators_Synthia(cf)
+    #show_DG(DG, 'train')  # this script will draw an image
+
+    # Build model
+    print('\n > Building model...')
+    model = Model_Factory(cf)
+    # model.test_and_save(DG.val_loader)
+
+    # model.test(DG.val_loader, 0)
+    if cf.train_model:
+        for epoch in range(1, cf.n_epochs + 1):
+            model.train(DG.train_loader, epoch)
+            if epoch % cf.test_epoch == 0:
+                if cf.test_model:
+                    model.test(DG.val_loader, epoch)
+
+    # Finish
+    print(' ---> Finish experiment: ' + cf.exp_name + ' <---')
+
+
+# Main function
+def main():
+    # Get parameters from arguments
+    parser = argparse.ArgumentParser(description='Semantic segmentation')
+    parser.add_argument('-c', '--config_path', type=str,
+                        default='/home/ty/code/autonomous_driving/code_base/config/cityscapes_segmentation.py', help='Configuration file')
+    parser.add_argument('-e', '--exp_name', type=str,
+                        default='cityscape_segmentation', help='Name of the experiment')
+    parser.add_argument('-s', '--shared_path', type=str,
+                        default='/home/public', help='Path to shared data folder')
+    parser.add_argument('-l', '--local_path', type=str,
+                        default='/home/ty/code/autonomous_driving', help='Path to local data folder')
+
+    arguments = parser.parse_args()
+
+    assert arguments.config_path is not None, 'Please provide a configuration path using -c config/pathname'
[…]

### 2017-11-11 code_base/config/synthia_car_trajectory.py
complete pipeline update'

@@ -1,23 +1,44 @@
-# Dataset
-problem_type                 = 'car_trajectory_prediction'  # ['classification' | 'detection' | 'segmentation']
-#dataset_name                 = 'synthia_rand_cityscapes'        # Dataset
+############################# Overall logic here
+problem_type                 = 'car_trajectory_prediction'  # ['car_tracking', 'car_detection', 'car_trajectory_prediction']
+sequence_name                = 'SYNTHIA-SEQS-01'
 
+car_detection                = False
+car_tracking                 = True
+tracker                      = 'dlib_dsst'  #['dlib_dsst', 'ECO_HC', 'KCF']
+draw_flag                    = True
+car_detection_method         = 'ssd512'
+get_sequence_car_detection   = True
+get_sequence_car_tracking    = True
+depth_threshold_method       = 'yen'   #['yen', 'ostu', 'li'
+iou_threshold                = 0.3
+start_tracking_idx           = 850
+threshold_car_POR_start      = 2e-3  # threshold for car start tracking using pixel occupant rate
+threshold_car_POR_end        = 1e-3  # threshold for car start tracking using pixel occupant rate
+minimum_detection_length     = 3
+
+####  SSD parameters (currently, we only suppose keras with Tensorflow backend, TODO: use Pytorch!
+ssd_prior_boxes              = '/home/stevenwudi/PycharmProjects/autonomous_driving/code_base/models/prior_boxes_ssd512.pkl'
+ssd_number_classes           = 2
+ssd_model_checkpoint         = '/home/public/synthia/ssd_car_fine_tune/weights_512.54-0.19.hdf5'
+ssd_input_shape              = (512, 512, 3)
+ssd_conf                     = 0.5
+
+
+# Dataset
 local_path                   = '/home/stevenwudi/PycharmProjects/autonomous_driving'
 shared_path                  = '/home/public/synthia'
 dataset_name2                = None            # Second dataset name. None if not Domain Adaptation
 perc_mb2                     = None            # Percentage of data from the second dataset in each minibatch
 class_mode                   = problem_type
-
-sequence_name                = 'SYNTHIA-SEQS-01'
 collect_data                 = False
-get_ground_truth_sequence_car_trajectory = False  # flag to get get_ground_truth_sequence_car_trajectory
+get_ground_truth_sequence_car_trajectory = True  # flag to get get_ground_truth_sequence_car_trajectory
 formatting_ground_truth_sequence_car_trajectory = True
[…]

### 2017-11-11 code_base/config/synthia_segmentation.py

@@ -15,7 +15,7 @@ freeze_layers_from           = None            # Freeze layers from 0 to this la
 show_model                   = False           # Show the architecture layers
 load_imageNet                = False           # Load Imagenet weights and normalize following imagenet procedure
 load_trained_model           = True           # Load a pretrained model for doing finetuning
-train_model_path             = '/home/stevenwudi/PycharmProjects/autonomous_driving/Experiments/segmentation/SYNTHIA_RAND_CVPR16___Tue, 07 Nov 2017-11-07 16:31:48_drn_d_38/epoch_1_mIOU:.0.554515_net.pth'  # Training weight file name
+train_model_path             = '/home/stevenwudi/PycharmProjects/autonomous_driving/Experiments/segmentation/SYNTHIA_RAND_CVPR16___Wed, 08 Nov 2017-11-08 11:21:17_drn_d_38/epoch_35_mIOU:.0.605787_net.pth'
 
 # Parameters
 train_model                  = True            # Train the model
@@ -59,9 +59,9 @@ seed_test                    = 1924            # Random seed for the testing shu
 
 # Training parameters
 optimizer                    = 'sgd'       # Optimizer
-learning_rate                = 0.0001          # Training learning rate
+learning_rate                = 0.001          # Training learning rate
 weight_decay                 = 0.              # Weight decay or L2 parameter norm penalty
-n_epochs                     = 25            # Number of epochs during training
+n_epochs                     = 100            # Number of epochs during training
 momentum                     = 0.9
 
 # Data augmentation for training and normalization
@@ -110,6 +110,6 @@ test_epoch                          = 1
 batch_size                          = 8
 crop_size                           = 720
 train_ratio                         = 0.9
-cb_weights_method                   = None #'rare_freq_cost'   # Label weight balance [None | 'median_freq_cost' | 'rare_freq_cost']
+cb_weights_method                   = 'rare_freq_cost' #'rare_freq_cost'   # Label weight balance [None | 'median_freq_cost' | 'rare_freq_cost']
 cb_weights                          = [1.65697855,   0.23748228,   0.29841721, 0.63769955,   9.23991394,   1.66974087,
                                        6.60188582, 0.92809024,  19.85701845,   2.60712632,  14.72396384]

### 2017-11-11 code_base/tools/PyTorch_model_training.py

@@ -63,6 +63,49 @@ def prepare_data(cf):
     return train_input, train_target, valid_input, valid_target, test_input, test_target, data_mean, data_std
 
 
+def prepare_data_image_list(cf):
+    import pickle
+    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_train.npy'), 'rb') as fp:
+        train_data = pickle.load(fp)
+    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_valid.npy'), 'rb') as fp:
+        valid_data = pickle.load(fp)
+    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_test.npy'), 'rb') as fp:
+        test_data = pickle.load(fp)
+
+    train_data, valid_data, test_data, data_mean, data_std = normalise_data(train_data, valid_data, test_data)
+    if cf.cuda:
+        print('Data using CUDA')
+        dtype = torch.cuda.FloatTensor  # Uncomment this to run on GPU
+        valid_input = Variable(torch.from_numpy(valid_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True), requires_grad=False)
+        valid_target = Variable(torch.from_numpy(valid_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True), requires_grad=False)
+        test_input = Variable(torch.from_numpy(test_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True), requires_grad=False)
+        test_target = Variable(torch.from_numpy(test_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True),requires_grad=False)
+        # Many to many input
+        if cf.model_name == 'LSTM_ManyToMany':
+            train_input = Variable(torch.from_numpy(train_data[:, :-1, :]).type(dtype).cuda(async=True), requires_grad=False)
+            train_target = Variable(torch.from_numpy(train_data[:, 1:, :]).type(dtype).cuda(async=True), requires_grad=False)
+        elif cf.model_name == 'LSTM_To_FC':
+            train_input = Variable(torch.from_numpy(train_data[:, :cf.lstm_input_frame, :]).type(dtype).cuda(async=True),
+                                   requires_grad=False)
+            train_target = Variable(torch.from_numpy(train_data[:, cf.lstm_input_frame:, :]).type(dtype).cuda(async=True),
+                                    requires_grad=False)
[…]

### 2017-11-11 code_base/tools/gt_acquisition.py

@@ -11,10 +11,9 @@ import h5py
 from code_base.tools.PyTorch_data_generator_car_trajectory import Dataset_Generators_Synthia_Car_trajectory
 import pickle
 from scipy.misc import imresize
-# Slow import from below!
-from keras.applications.imagenet_utils import preprocess_input
-from code_base.models.Keras_SSD import SSD512v2, BBoxUtility
-import collections
+from skimage.filters import threshold_otsu
+from skimage.filters import threshold_yen
+from skimage.filters import threshold_li
 
 
 def convert_key_to_string(car_tracking_dict):
@@ -412,12 +411,14 @@ def formatting_ground_truth_sequence_car_trajectory(cf, sequence_name, time_step
                 for im_num in range(0, len(car_tracking_dict[instance_number_in_seq]['tracking_rect'][track_num])-total_frame+1, time_step):
                     features_temp = []
                     for frame_num in range(im_num, im_num+total_frame, time_step):
+                        feature_img_name = sequence_name + '/' + car_tracking_dict[instance_number_in_seq]['img_list'][track_num][frame_num]
                         [centreX, centreY, height, width, d_min, d_max, d_centre, d_mean] = \
                         car_tracking_dict[instance_number_in_seq]['tracking_rect'][track_num][frame_num]
-                        features_temp.append([centreX, centreY, height, width, d_min, d_max])
-                    features.append(np.asarray(features_temp))
+                        features_temp.append([centreX, centreY, height, width, d_min, d_max, feature_img_name])
+                    #features.append(np.asarray(features_temp))
+                    features.append(features_temp)
 
-    features = np.asarray(features)
+    #features = np.asarray(features)
     num_total_seq = len(features)
     train_len = int(num_total_seq * 0.8)
     valid_len = int(num_total_seq * 0.1)
@@ -442,7 +443,7 @@ def gt_collection_examintion(cf):
         if cf.get_ground_truth_sequence_car_trajectory:
             if sequence_name+'.json' not in processed_list:
                 get_ground_truth_sequence_car_trajectory(DG, cf, sequence_name)
-        elif cf.formatting_ground_truth_sequence_car_trajectory:
+        if cf.formatting_ground_truth_sequence_car_trajectory:
[…]

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
pool figure add

@@
 Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
-Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.p
+Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.
 
@@
 
+\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving to robustly track a car.
+The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.
+
 \item We design various temporal model for the problems of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.
@@
 \item We demonstrate the effectiveness of using ``privileged information" further boost the prediction accuracy. [NOT DONE].
+
+\item We formalise the car trajectory problem into a 3D occupancy grid problem given depth information.
 
@@
 
-We utilise two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+\subsection{instance tracking}
+
+We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+
+\subsection{trajectory prediction}
+
+We compare two temporal models based on LSTM cells for predicting the car trajectory.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Experiments}
+
+\subsection{Dataset collection}
+
+Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
+We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
+SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
+There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
+Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
+
+Scene diversity: European style town, modern city, highway and green areas
+Variety of dynamic objects: cars, pedestrians and cyclists
+
+Multiple seasons: dedicated themes for winter, fall, spring and summer
+
+Lighting conditions and weather: dynamic lights and shadows, several day-time modes, rain mode and night mode
+
+Automatic groundtruth: individual instances for semantic segmentation (pixelwise annotations), depth, car ego-motion
+ of photo-realistic frames rendered from a virtual city and comes with precise pixel-level semantic annonations for 13 classes, \emph{i.e.}: miscellaneous, sky, building, road, sidewalk, fence, vegetation, pole, car, sign, pedestrian, cyclist, lanemarking.
+
+The focus of this paper is on car trajectory prediction on high ways. In the SYNTHIA
+
+Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
+\subsection{traffic participants detection}
+
+We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+We use the pretrained detection network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA. Curretnly
+
+A comprehensive survey of speed/accuracy trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer the keen readers to
 
@@
 
-\section{Experiments}
-\subsection{Dataset collection}
-We collect car trajectory evaluation dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
+\section{Conclusions}
 
-\section{Conclusions}
+Future works include conducting experiment on the real-world images.
 

### 2017-11-11 code_base/CityScape_semantic.py
synthia update

@@ -7,7 +7,7 @@ sys.path.append(os.getcwd())
 import time
 from datetime import datetime
 
-from code_base.tools.PyTorch_data_generator import Dataset_Generators_Cityscape
+from code_base.tools.PyTorch_data_generator import Dataset_Generators_Cityscape, Dataset_Generators_Synthia
 from code_base.models.PyTorch_model_factory import Model_Factory
 from code_base.config.configuration import Configuration
 from code_base.tools.utils import HMS, configurationPATH
@@ -19,20 +19,21 @@ def process(cf):
     print(' ---> Init experiment: ' + cf.exp_name + ' <---')
     # Create the data generators
     DG = Dataset_Generators_Cityscape(cf)
+    # DG = Dataset_Generators_Synthia(cf)
     #show_DG(DG, 'train')  # this script will draw an image
 
     # Build model
     print('\n > Building model...')
     model = Model_Factory(cf)
-    model.test_and_save(DG.val_loader)
+    # model.test_and_save(DG.val_loader)
 
     # model.test(DG.val_loader, 0)
-    # if cf.train_model:
-    #     for epoch in range(1, cf.n_epochs + 1):
-    #         model.train(DG.train_loader, epoch)
-    #         if epoch % cf.test_epoch == 0:
-    #             if cf.test_model:
-    #                 model.test(DG.val_loader, epoch)
+    if cf.train_model:
+        for epoch in range(1, cf.n_epochs + 1):
+            model.train(DG.train_loader, epoch)
+            if epoch % cf.test_epoch == 0:
+                if cf.test_model:
+                    model.test(DG.val_loader, epoch)
 
     # Finish
     print(' ---> Finish experiment: ' + cf.exp_name + ' <---')
@@ -70,9 +71,7 @@ def main():
     shared_experiments_path = os.path.join(shared_path, 'Experiments')
 
     # Load configuration files
-    configuration = Configuration(arguments.config_path, arguments.exp_name,
-                                  dataset_path, shared_dataset_path,
-                                  experiments_path, shared_experiments_path)
+    configuration = Configuration(arguments.config_path)
     cf = configuration.load()
     configurationPATH(cf)
 

### 2017-11-11 code_base/SSD_synthia_car_detection_fine_tune.py

@@ -504,6 +504,23 @@ def ssd_synthia_car_fine_tune():
      [ 0.698  0.7    0.7    0.696  0.696  0.682  0.655  0.59   0.401  0.095]
      [ 0.678  0.682  0.684  0.681  0.681  0.67   0.647  0.585  0.398  0.095]
      [ 0.655  0.659  0.662  0.663  0.665  0.659  0.639  0.578  0.395  0.094]]
+
+     POR = 2e-3 fastercnn result
+     Conf: [ 0.5   0.55  0.6   0.65  0.7   0.75  0.8   0.85  0.9   0.95]
+    Total GT: 1433.
+    Total prediction: [ 1614.  1601.  1593.  1585.  1576.  1561.  1557.  1544.  1532.  1507.]
+    Precision: [ 0.812  0.812  0.811  0.811  0.811  0.81   0.81   0.807  0.805  0.8  ]
+    Recall: [ 0.914  0.914  0.913  0.913  0.913  0.913  0.913  0.909  0.907  0.902]
+    F score: [[ 0.86   0.843  0.808  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.86   0.843  0.808  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.859  0.842  0.807  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.859  0.842  0.807  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.859  0.842  0.807  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.859  0.842  0.807  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.859  0.842  0.807  0.75   0.666  0.577  0.459  0.311  0.14   0.016]
+     [ 0.855  0.839  0.804  0.748  0.665  0.576  0.458  0.311  0.14   0.016]
+     [ 0.853  0.838  0.804  0.747  0.664  0.575  0.458  0.311  0.14   0.016]
+     [ 0.848  0.834  0.8    0.745  0.662  0.574  0.457  0.31   0.139  0.016]]
  """
 
 

### 2017-11-11 code_base/Synthia_semantic.py

@@ -1,6 +1,6 @@
 import argparse
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '3'
+os.environ['CUDA_VISIBLE_DEVICES'] = '0'
 import sys
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
@@ -11,7 +11,7 @@ from code_base.tools.PyTorch_data_generator import Dataset_Generators_Cityscape,
 from code_base.models.PyTorch_model_factory import Model_Factory
 from code_base.config.configuration import Configuration
 from code_base.tools.utils import HMS, configurationPATH
-
+from matplotlib import pyplot as plt
 
 # Train the network
 def process(cf):
@@ -28,12 +28,17 @@ def process(cf):
     # model.test_and_save(DG.val_loader)
 
     # model.test(DG.val_loader, 0)
-    if cf.train_model:
-        for epoch in range(1, cf.n_epochs + 1):
-            model.train(DG.train_loader, epoch)
-            if epoch % cf.test_epoch == 0:
-                if cf.test_model:
-                    model.test(DG.val_loader, epoch)
+    test_json_file = '/home/public/synthia/ssd_car_test_faster-shuffle.json'
+    model.test_synthia_json2(test_json_file)
+
+
+    # if cf.train_model:
+    #     for epoch in range(1, cf.n_epochs + 1):
+    #
+    #         model.train_synthia(DG.dataloader['train_rand'], epoch)
+    #         if epoch % cf.test_epoch == 0:
+    #             if cf.test_model:
+    #                 model.test_synthia(epoch)
 
     # Finish
     print(' ---> Finish experiment: ' + cf.exp_name + ' <---')
@@ -44,7 +49,7 @@ def main():
     # Get parameters from arguments
     parser = argparse.ArgumentParser(description='Semantic segmentation')
     parser.add_argument('-c', '--config_path', type=str,
-                        default='/home/ty/code/autonomous_driving/code_base/config/cityscapes_segmentation.py', help='Configuration file')
+                        default='/home/ty/code/autonomous_driving/code_base/config/synthia_segmentation.py', help='Configuration file')
     parser.add_argument('-e', '--exp_name', type=str,
                         default='cityscape_segmentation', help='Name of the experiment')
     parser.add_argument('-s', '--shared_path', type=str,
@@ -65,10 +70,10 @@ def main():
     # Define the user paths
     shared_path = arguments.shared_path
[…]

### 2017-11-11 code_base/config/configuration.py

@@ -14,8 +14,11 @@ class Configuration():
         # Load configuration file...
         print(self.config_path)
         cf = imp.load_source('config', self.config_path)
-        dataset_path = os.path.join(cf.local_path, 'Datasets')
-        shared_dataset_path = os.path.join(cf.shared_path)
+        if cf.data_path:
+            dataset_path = os.path.join(cf.data_path)
+        else:
+            dataset_path = os.path.join(cf.local_path, 'Datasets')
+        # shared_dataset_path = os.path.join(cf.shared_path)
         experiments_path = os.path.join(cf.local_path, 'Experiments')
         shared_experiments_path = os.path.join(cf.shared_path, 'Experiments')
 
@@ -70,7 +73,7 @@ class Configuration():
                     os.mkdir(cf.savepath)
 
             else:
-                cf.dataset_path = os.path.join(dataset_path, self.sequence_name)
+                cf.dataset_path = os.path.join(dataset_path, cf.sequence_name)
                 # Create output folders
                 cf.savepath = os.path.join(experiments_path, cf.exp_name, cf.dataset_name)
 

### 2017-11-11 code_base/config/synthia_segmentation.py

@@ -1,13 +1,16 @@
 # Dataset
 problem_type                 = 'segmentation'  # ['classification' | 'detection' | 'segmentation']
 dataset_name                 = 'synthia_rand_cityscapes'        # Dataset
-dataset_name                 = 'SYNTHIA_RAND_CVPR16'
+sequence_name                 = 'SYNTHIA_RAND_CVPR16'
 dataset_name2                = None            # Second dataset name. None if not Domain Adaptation
 perc_mb2                     = None            # Percentage of data from the second dataset in each minibatch
 class_mode                   = problem_type
-
+local_path                   = '/home/ty/code/autonomous_driving'
+shared_path                  = '/home/public'
+data_path                    = '/home/stevenwudi/PycharmProjects/autonomous_driving/Datasets/segmentation'
+dataroot_dir                 = '/home/stevenwudi/PycharmProjects/autonomous_driving/Datasets/segmentation'
 # Model
-model_name                   = 'fcn8'          # Model to use ['fcn8' | 'lenet' | 'alexNet' | 'vgg16' |  'vgg19' | 'resnet50' | 'InceptionV3']
+model_name                   = 'drn_d_38'          # Model to use ['fcn8' | 'lenet' | 'alexNet' | 'vgg16' |  'vgg19' | 'resnet50' | 'InceptionV3']
 freeze_layers_from           = None            # Freeze layers from 0 to this layer during training (Useful for finetunning) [None | 'base_model' | Layer_id]
 show_model                   = False           # Show the architecture layers
 load_imageNet                = False           # Load Imagenet weights and normalize following imagenet procedure
@@ -27,7 +30,7 @@ debug_images_test            = 30              # N images for testing in debug m
 debug_n_epochs               = 3               # N of training epochs in debug mode
 
 # Batch sizes
-batch_size_train             = 10              # Batch size during training
+batch_size_train             = 20              # Batch size during training
 batch_size_valid             = 10              # Batch size during validation
 batch_size_test              = 10              # Batch size during testing
 dataloader_num_workers_train = batch_size_train# Number of dataload works during training
@@ -40,7 +43,7 @@ crop_size_test               = None            # Crop size during testing
 resize_train                 = (270, 480)      # Resize the image during training (Height, Width) or None
[…]

### 2017-11-11 code_base/models/PyTorch_model_factory.py

@@ -11,6 +11,7 @@ from torch.nn import functional as F
 from torchvision.utils import save_image
 from code_base.tools.logger import Logger
 from datetime import datetime
+import numpy as np
 
 from matplotlib import pyplot as plt
 import os
@@ -32,7 +33,6 @@ def save_output_images(predictions, filenames, output_dir):
     # pdb.set_trace()
     root = '/home/public/CITYSCAPE'
     from PIL import Image
-    import numpy as np
     for ind in range(len(filenames)):
         im = Image.fromarray(predictions[ind].astype(np.uint8))
         name = filenames[ind].replace(root, output_dir)
@@ -41,6 +41,16 @@ def save_output_images(predictions, filenames, output_dir):
         if not os.path.exists(out_dir):
             os.makedirs(out_dir)
         im.save(name)
+
+def load_net_synthia(state_dict, net):
+    for k, v in net.state_dict().items():
+        pre_param = state_dict[k]
+        if pre_param.size() == v.size():
+            # param = torch.from_numpy(pre_param)
+            v.copy_(pre_param)
+
+        else:
+            print (k)
 
 # Build the model
 class Model_Factory():
@@ -78,7 +88,8 @@ class Model_Factory():
         # Construct optimiser
         if cf.load_trained_model:
             print("Load from pretrained_model weight: "+cf.train_model_path)
-            self.net.load_state_dict(torch.load(cf.train_model_path))
+            load_net_synthia(torch.load(cf.train_model_path), self.net)
+            # self.net.load_state_dict(torch.load(cf.train_model_path))
 
         # self.net = DRNSegF(self.net, 20)
         params_dict = dict(self.net.named_parameters())
@@ -108,6 +119,19 @@ class Model_Factory():
         for i, (input, target_one_hot, target, _) in enumerate(train_loader):
             self.optimiser.zero_grad()
             input, target, target_one_hot = Variable(input.cuda(async=True)), Variable(target.cuda(async=True)), Variable(target_one_hot.cuda(async=True))
+            output = F.log_softmax(self.net(input))
+            self.loss = self.crit(output, target)
+            print(epoch, i, self.loss.data[0])
+            self.loss.backward()
+            self.optimiser.step()
+
+    def train_synthia(self, train_loader, epoch):
[…]

### 2017-11-11 code_base/tools/PyTorch_data_generator.py

@@ -99,7 +99,9 @@ class ToTensor(object):
         # numpy image: H x W x C
         # torch image: C X H X W
         image = image.transpose((2, 0, 1))
-        return {'image': torch.from_numpy(image),
+        image_tensor = torch.from_numpy(image)
+        image_tensor = image_tensor.float().div(255)
+        return {'image': image_tensor,
                 'label': torch.from_numpy(label)}
 
 
@@ -115,6 +117,25 @@ class RandomHorizontalFlip(object):
             results = [image, label]
         return results
 
+class Normalize(object):
+    """Given mean: (R, G, B) and std: (R, G, B),
+    will normalize each channel of the torch.*Tensor, i.e.
+    channel = (channel - mean) / std
+    """
+
+    def __init__(self, mean, std):
+        self.mean = torch.FloatTensor(mean)
+        self.std = torch.FloatTensor(std)
+
+    def __call__(self, image, label=None):
+        img = image['image']
+        label = image['label']
+        for t, m, s in zip(img, self.mean, self.std):
+            t.sub_(m).div_(s)
+        if label is None:
+            return image,
+        else:
+            return {'image': img, 'label': label.long()}
 
 class Dataset_Generators_Synthia():
     """ Initially we use synthia dataset"""
@@ -124,34 +145,40 @@ class Dataset_Generators_Synthia():
         self.dataloader = {}
 
         # Load training set
-        print('\n > Loading training, valid, test set')
+        print('\n > Loading training, valid, test set, train_rand set')
         dataloaders_single = {x: ImageDataGenerator_Synthia(
             root_dir=os.path.join(cf.dataset_path, x),
             transform=T.Compose([
-                Rescale(cf.resize_train),
                 RandomCrop(cf.random_size_crop),
                 ToTensor(),
-            ]))
-            for x in ['train', 'valid', 'test']}
+                Normalize(self.cf.rgb_mean, self.cf.rgb_std)
+            ]),
+            error_images=self.cf.error_images)
+            # for x in ['train', 'valid', 'test', 'train_rand']}
+            for x in ['train_rand']}
 
-        self.dataloader['train'] = DataLoader(dataset=dataloaders_single['train'],
-                                              batch_size=cf.batch_size_train,
-                                              shuffle=cf.shuffle_train,
-                                              num_workers=cf.dataloader_num_workers_train)
-        self.dataloader['valid'] = DataLoader(dataset=dataloaders_single['valid'],
[…]

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
latex paper writing

@@
 \usepackage{bm}
-\usepackage{subcaption}
-\usepackage{slashbox}
+%\usepackage{subcaption}
+%\usepackage{slashbox}
 \usepackage{color}
@@
 \begin{abstract}
-
+TODO: abstract
+This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad.
+I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some.
+Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience.
+Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research).
+But disclaimers are boring, lets get to it!
 \end{abstract}
@@
 
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
+        \caption{ {\small TODO: Pull figure caption goes here.}}
+        \label{fig:response_map}
+\end{figure}
 \textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}
@@
 
+~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.
+
+~\cite{behl2017bounding} Bounding Boxes, Segmentations and Object Coordinates: How Important is Recognition for 3D Scene Flow Estimation in Autonomous Driving Scenarios?
+
+~\cite{chen2015deepdriving} DeepDriving: Learning Affordance for Direct Perception
+
+~\cite{kim2017interpretable} Interpretable Learning for Self-driving cars
+
 \section{Proposed Algorithm}
@@
 SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
+The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
+The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
+
 There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
 Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
+In our experiment, we used only left front camera view data.
+The focus of this paper is on car trajectory prediction on high ways. We list our logic for collecting continuous car tracking in List~\ref{Dataset_collection}. (TODO: make a list).
+Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
 
-Scene diversity: European style town, modern city, highway and green areas
-Variety of dynamic objects: cars, pedestrians and cyclists
+\begin{algorithm}
+\caption{Multimodal Deep Dynamic Networks -- training}\label{Dataset_collection}
+\LinesNumbered
+\SetAlgoLined
+\SetAlgoNoEnd
+\DontPrintSemicolon
+\SetKwFunction{zeroes}{zeroes}
+\KwData{\;
+          $ \mathbf{X^1=\{ x^1_i\}_{i \in [1 \ldots t]}}$ - raw input(skeletal) feature sequence.\;
+          $ \mathbf{X^2=\{ x^2_i\}_{i \in [1 \ldots t]}}$ - raw input(depth) feature sequence in the form of \;
+          \hspace{1cm}$M_1 \times M_2 \times T$, where $M_1, M_2$ are the height and width of the input \;
+          \hspace{1cm}  image and $T$ is the number of contiguous frames of the \;
+          \hspace{1cm} spatio-temporal cuboid. \;
+          \hspace{1cm}  {\scriptsize{}Note that the GPU library \emph{cuda-convnet}~\cite{krizhevsky2012imagenet} used requires square size images and $T$ is a multiple of $4$}.\;
+          $ \mathbf{Y=\{ y_i\}_{i \in [1 \ldots t]}}$  - frame based local label (achieved by semi-supervised \; \hspace{1cm} forced-aligment), \;
+          \hspace{1cm}  where $ \mathbf{y_i} \in \{ C * S + \textbf{\emph{1}} \} $ with $C$ is the number of class, $S$ is the  \;
+          \hspace{1cm}  number of hidden states for each class, $\textbf{\emph{1}}$ as ergodic state.
+            }
+\For{$m \leftarrow 1$ to $2$}{
+    \SetAlgoVlined
+    \eIf{$m$ is $1$}{
+        Preprocessing the dataCordts2016Cityscapes $ \mathbf{X^1}$ as in Eq.\ref{sk_features}.\;
+        Normalizing(zero mean, unit variance per dimension) the above features and feed to to Eq.\ref{GRBMenergy}. \;
+        Pre-training the networks using \emph{Contrastive Divergence}. \;
+        Supervised fine-tuning the Deep Belief Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} backpropagation.\;
+    }{
+        Preprocessing the data $ \mathbf{X^2}$ (normalizing, median filtering the depth data) Algo.\ref{normalization_scheme_1} or Algo.\ref{normalization_scheme_2}.\;
+        Feeding the above features to Eq.\ref{ReLU}. \;
+        Supervised fine-tuning the Deep 3D Convolutional Neural Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} Backpropagation.\;
+    }
+}
+\KwResult{\;
+        $\mathbf{GDBN}$ - a gaussian bernoulli visible layer Deep Belief Network to \;
+                \hspace{1cm} generate the emission probabilities for hidden markov model.\;
+        $\mathbf{3DCNN}$ - a 3D Deep Convolutional Neural Networks to generate the\;
+                \hspace{1cm}   emission probabilities for hidden markov model.\;
+        $\mathbf{p(H_1)}$ - prior probability for $ \mathbf{Y}$.\;
+        $ \mathbf{p(H_t | H_{t-1})}$ - transition probability for $ \mathbf{Y}$,  enforcing the beginning and \;
+                    \hspace{1cm} ending of a sequence can only start from the first or the last state.
+}
+\end{algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Multiple seasons: dedicated themes for winter, fall, spring and summer
+\subsection{Implementations}
 
-Lighting conditions and weather: dynamic lights and shadows, several day-time modes, rain mode and night mode
-
-Automatic groundtruth: individual instances for semantic segmentation (pixelwise annotations), depth, car ego-motion
- of photo-realistic frames rendered from a virtual city and comes with precise pixel-level semantic annonations for 13 classes, \emph{i.e.}: miscellaneous, sky, building, road, sidewalk, fence, vegetation, pole, car, sign, pedestrian, cyclist, lanemarking.
-
-The focus of this paper is on car trajectory prediction on high ways. In the SYNTHIA
-
-Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
-\subsection{traffic participants detection}
+\subsubsection{Traffic participants detection}
 
@@
 
-\subsection{instance tracking}
+\subsubsection{Instance tracking}
 
@@
 
-\subsection{trajectory prediction}
+\subsubsection{Trajectory prediction}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Evaluation}
+
+\begin{table}[t]
+\small
+   \centering
+        \begin{tabular}{|l|| *{2}{c}| *{2}{c} |}\hline
+            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}  & \multicolumn{2}{|c|}{\small 3D}  \\ \hline \hline
+                                                    & P20       & AUC       & P20       & AUC  \\ \hline \hline
+
+            {\small MTM }                          &  58.0     &  38.4     & 64.3      & 44.0   \\
+            \hline
+            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$    &  71.4 ${\color{red}(7.1\uparrow)}$     &  49.1 ${\color{red}(5.1\uparrow)}$\\
+            \hline
+            \hline
+            {\small MaxRes }                        &  57.5     &  38.8     &  65.8     &  45.9  \\
+            \hline
+            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   &  77.8 ${\color{red}(12.0\uparrow)}$    &  53.6 ${\color{red}(7.7\uparrow)}$ \\
+            \hline
+            \hline
+            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$      &  79.8${\color{red}(2.0\uparrow)}$      &  57.0${\color{red}(3.4\uparrow)}$    \\
+            \hline
+            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$     &  79.9${\color{red}(0.1\uparrow)}$     &  57.4${\color{red}(0.4\uparrow)}$\\\hline
+
+        \end{tabular}
+
+    \caption{ {\small
+          Baseline comparisons with arrows indicating performance changes comparing with the upper row parallel experiment.
+          First two rows investigate the impact of projecting deep features into a kernel space \emph{vs.} using linear deep features.
+          Next two rows compare the traditional using max location \emph{vs.} the proposed multi-resolution convnets paradigm for decoding target translational movement.
+          Last two rows illustrate the benefit of adaptive learning rate through time (with scale update). }
+          } \label{table_baseline}
+\end{table}
+
+\begin{table}[t]
+\small
+   \centering
+        \begin{tabular}{|l|| *{2}{c}|}\hline
+            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}    \\ \hline \hline
+                                                  & P20       & AUC   \\ \hline \hline
+
+            {\small MTM }                          &  58.0     &  38.4      \\
+            \hline
+            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$  \\
+            \hline
+            \hline
+            {\small MaxRes }                        &  57.5     &  38.8   \\
+            \hline
+            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   \\
+            \hline
+            \hline
+            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$     \\
+            \hline
+            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$    \\\hline
+
+        \end{tabular}
+
+    \caption{ {\small
+          Comparison with the most recent methods }
+          } \label{table_baseline2}
+\end{table}
 \section{Conclusions}

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
lstm related work

--- 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
@@
 \usepackage{subcaption}
-\usepackage{slashbox}
+%\usepackage{slashbox}
 \usepackage{color}
@@
 
+Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
+Most of these works exploit LSTM as component of an end-to-end driving model.
+~\cite{xu2017end} used the combination of a fully-convolutional network and an LSTM to learn from large-scale vehicle action data, to predict future egomotion including multi-modal discrete and continuous driving behaviors.
+~\cite{kim2017interpretable} used a LSTM network to predict the inverse turning radius and generate a heat map of attention at each timestep conditioned on the previous hidden states and a current convolutional feature cube.
+~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
+In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
+
 \section{Proposed Algorithm}

### 2017-11-11 code_base/Synthia_car_trajectory.py
sementic segmentation dataloader

@@ -14,7 +14,7 @@ from code_base.config.configuration import Configuration
 from code_base.tools.utils import HMS, configurationPATH
 from code_base.tools.gt_acquisition import gt_collection_examintion
 from code_base.models.PyTorch_model_factory import Model_Factory_LSTM
-from code_base.tools.PyTorch_model_training import prepare_data, prepare_data_image_list
+from code_base.tools.PyTorch_data_generator import DataGenerator_Synthia_car_trajectory
 
 
 def process(cf):
@@ -24,8 +24,8 @@ def process(cf):
         print(' ---> Collecting data: ' + cf.sequence_name + ' <---')
         gt_collection_examintion(cf)
 
-    # Build model
-    train_input, train_target, valid_input, valid_target, test_input, test_target, data_mean, data_std = prepare_data_image_list(cf)
+    print('Create dataloader')
+    DG = DataGenerator_Synthia_car_trajectory(cf)
 
     print('\n > Building model...')
     model = Model_Factory_LSTM(cf)

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex

--- 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
@@
 \usepackage{bm}
+
 %\usepackage{subcaption}
+
 %\usepackage{slashbox}
@@
 \textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}
+
+Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
+Most of these works exploit LSTM as component of an end-to-end driving model.
+~\cite{xu2017end} used the combination of a fully-convolutional network and an LSTM to learn from large-scale vehicle action data, to predict future egomotion including multi-modal discrete and continuous driving behaviors.
+~\cite{kim2017interpretable} used a LSTM network to predict the inverse turning radius and generate a heat map of attention at each timestep conditioned on the previous hidden states and a current convolutional feature cube.
+~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
+In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
 

### 2017-11-11 code_base/config/synthia_car_trajectory.py
for local

@@ -24,14 +24,9 @@ ssd_input_shape              = (512, 512, 3)
 ssd_conf                     = 0.5
 
 
-<<<<<<< HEAD
+
 local_path                   = '/home/wzn/PycharmProjects/autonomous_driving'
-||||||| merged common ancestors
-local_path                   = '/home/stevenwudi/PycharmProjects/autonomous_driving'
-=======
 # Dataset
-local_path                   = '/home/stevenwudi/PycharmProjects/autonomous_driving'
->>>>>>> pre-master
 shared_path                  = '/home/public/synthia'
 dataset_name2                = None            # Second dataset name. None if not Domain Adaptation
 perc_mb2                     = None            # Percentage of data from the second dataset in each minibatch

### 2017-11-12 code_base/tools/PyTorch_data_generator.py
modify dataloader getitem

@@ -306,13 +306,16 @@ class BB_ImageDataGenerator_Synthia(Dataset):
             semantic_image_t = torch.Tensor(semantic_image_one_hot)
             return semantic_image_t
 
-        semantic_images = torch.stack([semantic_image(img_name(i)) for i in range(self.cf.lstm_input_frame)], dim=0)
-
         # trajectory
         trajectory = self.trajectory_data[item]
         trajectory_t = torch.FloatTensor(trajectory)
         input_trajectorys = trajectory_t[:self.cf.lstm_input_frame, :]
         target_trajectorys = trajectory_t[self.cf.lstm_input_frame:, :]
+        # semantics
+        if self.cf.model_name == 'CNN_LSTM_To_FC':
+            semantic_images = torch.stack([semantic_image(img_name(i)) for i in range(self.cf.lstm_input_frame)], dim=0)
+        else:
+            semantic_images = torch.FloatTensor(torch.zeros(input_trajectorys.size()))
 
         return semantic_images, input_trajectorys, target_trajectorys
 

### 2017-11-12 code_base/config/synthia_car_trajectory.py
for local

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
+model_name                   = 'CNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None

### 2017-11-12 code_base/models/PyTorch_model_factory.py

@@ -263,7 +263,7 @@ class Model_Factory_LSTM():
             self.optimiser.step()
 
         train_loss = np.array(train_losses).mean()
-        print('Train Loss', epoch, train_loss )
+        print('Train Loss', epoch, train_loss)
 
 
         # # output loss

### 2017-11-12 code_base/config/synthia_car_trajectory.py
for local

@@ -42,8 +42,8 @@ debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
 #random_size_crop             = (350*2, 460*2)      # Random size crop of the image during training
-workers                      = 4              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
-batch_size_train             = 4              # Batch size during training
+workers                      = 6              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
+batch_size_train             = 6              # Batch size during training
 batch_size_valid             = 1              # Batch size during validation
 batch_size_test              = 1              # Batch size during testing
 dataloader_num_workers_train = 1        # Number of dataload works during training

### 2017-11-12 code_base/models/PyTorch_model_factory.py

@@ -266,12 +266,7 @@ class Model_Factory_LSTM():
         print('Train Loss', epoch, train_loss)
 
 
-        # # output loss
-        # out = self.net(*input)[0]
-        # loss = self.crit(out, train_target)
-        # if cf.cuda:
-        #     return loss.data.cpu().numpy()[0]
-        # else:
+
         return train_loss
 
     def test(self, cf, valid_loader, data_mean, data_std, epoch=None):

### 2017-11-12 paper/cvpr2018/cvpr2018_draft.tex
Abstract draft completed.

@@
 \usepackage{bm}
-
 %\usepackage{subcaption}
-
 %\usepackage{slashbox}
@@
 \newcommand{\argmin}{\operatornamewithlimits{argmin}}
-\cvprfinalcopy
+%\cvprfinalcopy
 
@@
 \begin{abstract}
-TODO: abstract
-This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad.
-I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some.
-Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience.
-Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research).
-But disclaimers are boring, lets get to it!
+% State the problem, your approach and solution, and the main contributions of the paper.
+Include little if any background and motivation.
+Be factual but comprehensive.
+The material in the abstract should not be repeated later word for word in the paper.
+
+Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
+These models need to be temporally consistent and visually interpretable.
+Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
+In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
+The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
+Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
+Then, a novel DRN-LSTM network is incorporated to fuse the multiple-streams from past frames to predict targets' future trajectories.
+We demonstrate the feasibility of predicting future trajectories of cars for assisting mediated perception.
+ We also show the effectiveness of using privileged information (e.g., scene semantics and car pose information) further boost the prediction accuracy across diverse traffic conditions.
+
 \end{abstract}
@@
 \end{figure}
-\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}
+\textbf{\emph{3. Why is it hard? (E.g. why do naive approaches fail?)}}
 
@@
 
-In traditional vision based tracking problems (\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
+In traditional vision based tracking problems(\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
 However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).

### 2017-11-12 code_base/config/synthia_car_trajectory.py
cnn model

@@ -123,7 +123,7 @@ lstmToFc_output_dim           = 6               # outlayer output: [x,y,w,h, d_m
 cnn_class_num                 = 15
 def cnnDict(in_channels, out_channels, kernel_size, stride, padding):
     return {'in_channels': in_channels, 'out_channels': out_channels, 'kernel_size': kernel_size, 'stride': stride, 'padding': padding}
-cnnLstmToFc_conv_paras        = [cnnDict(cnn_class_num,2,3,1,1), cnnDict(2,4,3,1,1),cnnDict(4,4,2,2,0)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
+cnnLstmToFc_conv_paras        = [cnnDict(cnn_class_num,15,3,1,1), cnnDict(15,15,3,2,1),cnnDict(15,15,5,2,1)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
                                                                                       # 'out_channels': ,
                                                                                       # 'kernel_size': ,
                                                                                       # 'stride': ,

### 2017-11-12 code_base/models/PyTorch_PredictModels.py

@@ -190,10 +190,13 @@ class CNN_LSTM_To_FC(nn.Module):
         self.convparas = conv_paras
         self.conv = nn.Sequential(nn.Conv2d(**self.convparas[0]),
                                   nn.ReLU(),
+                                  nn.MaxPool2d(2),
                                   nn.Conv2d(**self.convparas[1]),
                                   nn.ReLU(),
+                                  nn.MaxPool2d(2),
                                   nn.Conv2d(**self.convparas[2]),
-                                  nn.ReLU()
+                                  nn.ReLU(),
+                                  nn.MaxPool2d(2)
                                   )
 
         # lstm part; build lstm layer, parameters are (input_dim,hidden_size,num_layers)

### 2017-11-12 code_base/models/PyTorch_model_factory.py

@@ -300,7 +300,6 @@ class Model_Factory_LSTM():
 
         self.loss = self.crit(output_trajectories, target_trajectories)
 
-
         # evaluations
         if cf.cuda:
             results = output_trajectories.data.cpu().numpy() * data_std + data_mean

### 2017-11-12 code_base/config/synthia_car_trajectory.py
for local

@@ -43,9 +43,9 @@ im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
 #random_size_crop             = (350*2, 460*2)      # Random size crop of the image during training
 workers                      = 6              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
-batch_size_train             = 6              # Batch size during training
-batch_size_valid             = 1              # Batch size during validation
-batch_size_test              = 1              # Batch size during testing
+batch_size_train             = 20              # Batch size during training
+batch_size_valid             = 20              # Batch size during validation
+batch_size_test              = 20              # Batch size during testing
 dataloader_num_workers_train = 1        # Number of dataload works during training
 dataloader_num_workers_valid = 1        # Number of dataload works during valid
 dataloader_num_workers_test  = 1        # Number of dataload works during test
@@ -124,12 +124,12 @@ lstmToFc_output_dim           = 6               # outlayer output: [x,y,w,h, d_m
 cnn_class_num                 = 15
 def cnnDict(in_channels, out_channels, kernel_size, stride, padding):
     return {'in_channels': in_channels, 'out_channels': out_channels, 'kernel_size': kernel_size, 'stride': stride, 'padding': padding}
-cnnLstmToFc_conv_paras        = [cnnDict(cnn_class_num,15,3,1,1), cnnDict(15,15,3,2,1),cnnDict(15,15,5,2,1)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
+cnnLstmToFc_conv_paras        = [cnnDict(cnn_class_num,15,3,1,1), cnnDict(15,15,3,2,1),cnnDict(15,15,5,2,2)]              # a list composed of dicts representing parameters of each conv, {'in_channels': ,
                                                                                       # 'out_channels': ,
                                                                                       # 'kernel_size': ,
                                                                                       # 'stride': ,
                                                                                       # 'padding': }
-cnnLstmToFc_input_dims        = [6, 200, 300]              # a list involving each lstm_layer's input_dim
-cnnLstmToFc_hidden_sizes      = [100, 300, 300]              # a list involving each lstm_layer's hidden_size
+cnnLstmToFc_input_dims        = [6, 325, 350]              # a list involving each lstm_layer's input_dim
[…]

### 2017-11-12 code_base/tools/PyTorch_model_training.py

@@ -127,7 +127,7 @@ def prepare_data_image_list(cf):
 
     train_img_list, valid_img_list, test_img_list = get_img_list(train_data, valid_data, test_data)
 
-    return train_data_array, valid_data_array, test_data_array, data_mean, data_std, train_img_list, valid_img_list, test_img_list
+    return train_data_array[:10, :, :], valid_data_array[:3, :, :], test_data_array[:3, :, :], data_mean, data_std, train_img_list, valid_img_list, test_img_list
 
 
 def calc_seq_err_robust(results, rect_anno, focal_length):

### 2017-11-12 code_base/config/synthia_car_trajectory.py
for local

@@ -100,7 +100,7 @@ focal_length                 = 532.740352  # camera focal lense
 # Training parameters
 test_epoch                   = 1
 weight_decay                 = 0.              # Weight decay or L2 parameter norm penalty
-n_epochs                     = 30            # Number of epochs during training
+n_epochs                     = 50            # Number of epochs during training
 cuda                         = True
 loss                         = 'SmoothL1Loss'       # 'MSE', 'SmoothL1Loss'
 optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'

### 2017-11-12 code_base/Synthia_car_trajectory.py
modify learning_rate decay & loss_ figure

@@ -38,20 +38,22 @@ def process(cf):
             train_losses += [model.train(cf, DG.train_loader, epoch)]
             if cf.valid_model:
                 valid_losses += [model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, epoch)]
-        print('---> Train losses:')
-        print(train_losses)
-        print('---> Valid losses:')
-        print(valid_losses)
-        # losses figure
-        plt.figure()
-        plt.title('Losses')
-        plt.xlabel('steps')
-        plt.ylabel('losses')
-        p1 = plt.plot(train_losses, color='b')
-        p2 = plt.plot(valid_losses, color='r')
-        plt.legend((p1[0], p2[0]), ('trainLosses', 'validLosses'))
-        figure_path = os.path.join(model.exp_dir, 'loss_figure.jpg')
-        plt.savefig(figure_path)
+            if epoch > 0 and epoch%cf.figure_epoch == 0:
+                print('---> Train losses:')
+                print(train_losses)
+                print('---> Valid losses:')
+                print(valid_losses)
+                # losses figure
+                plt.figure()
+                plt.title('Losses')
+                plt.xlabel('steps')
+                plt.ylabel('losses')
+                p1 = plt.plot(train_losses, color='b')
+                p2 = plt.plot(valid_losses, color='r')
+                plt.legend((p1[0], p2[0]), ('trainLosses', 'validLosses'))
+                figure_name = 'loss_figure_' + str(epoch) + '.jpg'
+                figure_path = os.path.join(model.exp_dir, figure_name)
+                plt.savefig(figure_path)
 
     if cf.test_model:
         test_loss = model.test(cf, DG.test_loader, DG.data_mean, DG.data_std, epoch=None)

### 2017-11-12 code_base/config/synthia_car_trajectory.py

@@ -97,6 +97,8 @@ test_model                   = True           # Predict using the model
 focal_length                 = 532.740352  # camera focal lense
 
 # Training parameters
+lr_decay_epoch               = 10          # every lr_decay_epoch, decay learning_rate by 10
+figure_epoch                 = 5           # every fugure_epoch, figure out the losses
 test_epoch                   = 1
 weight_decay                 = 0.             # Weight decay or L2 parameter norm penalty
 n_epochs                     = 3            # Number of epochs during training

### 2017-11-13 code_base/Synthia_car_trajectory.py
for local

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '2'
+os.environ['CUDA_VISIBLE_DEVICES'] = '3'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-13 code_base/config/synthia_car_trajectory.py

@@ -42,7 +42,7 @@ debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
 #random_size_crop             = (350*2, 460*2)      # Random size crop of the image during training
-workers                      = 6              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
+workers                      = 32              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
 batch_size_train             = 64            # Batch size during training
 batch_size_valid             = 20              # Batch size during validation
 batch_size_test              = 20              # Batch size during testing
@@ -108,7 +108,7 @@ loss                         = 'SmoothL1Loss'       # 'MSE', 'SmoothL1Loss'
 optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
-load_trained_model           = False
+load_trained_model           = True
 train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01___Mon, 06 Nov 2017-11-06 16:08:14/Epoch:100_net_aveErrCoverage:0.8343_aveErrCenter:17.47___.pth'
 #### LSTM training variables #################
 # LSTM_ManyToMany

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex

--- 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
@@
 \section{Introduction}
+
+\begin{figure}
+
+\includegraphics[width=8.8cm]{pool_figure}
+\caption{pool figure}
+\label{figure10}
+\end{figure}
 
@@
 %%% DW: write related dataset for autonoumous driving
+Object detection is an important component in our system.
+Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
+However, after the proposal of R-CNN \cite{girshick2014rich}, which combines Selective Search and deep learning features to detect objects, the architecture of CNN has attracted more attention.
+At the beginning, R-CNN is a step-by-step and inefficient method.
+Then, SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features and Fast R-CNN \cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network.
+At last, Faster R-CNN \cite{Ren2015Faster} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture.
+Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class.
+In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.
+
+At the field of semantic segmentation, many methods with CNN also bring a dramatic improvement.
+FCN \cite{long2015fully} firstly transfers the fully-connected layers into convolution layers, which turns segmentation task into pixel-wise classification task.
+Deeplab \cite{chen2016deeplab} considers the limitation of receptive field of CNN, and then proposes a dilated convolution layer to solve this problem.
+DRN \cite{yu2017dilated} further proposes a semantic network by integrating residual structure and dilated convolution.
+With the modification of neural network, conditional random field (CRF) is employed into refining the output of network in \cite{chen2016deeplab}.
+After that, CRF is merged into neural network to become an end-to-end architecture \cite{liu2015semantic,zheng2015conditional,arnab2016higher}
 
@@
 \textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}
-
-Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
-Most of these works exploit LSTM as component of an end-to-end driving model.
-~\cite{xu2017end} used the combination of a fully-convolutional network and an LSTM to learn from large-scale vehicle action data, to predict future egomotion including multi-modal discrete and continuous driving behaviors.
-~\cite{kim2017interpretable} used a LSTM network to predict the inverse turning radius and generate a heat map of attention at each timestep conditioned on the previous hidden states and a current convolutional feature cube.
-~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
-In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
 

### 2017-11-13 code_base/Synthia_car_trajectory.py
for conflict

@@ -38,7 +38,7 @@ def process(cf):
         valid_losses = []
         print(' ---> Training data: ' + cf.sequence_name + ' <---')
         for epoch in range(1, cf.n_epochs + 1):
-            train_losses += [model.train(cf, DG.train_loader, epoch)]
+            train_losses += [model.train(cf, DG.train_loader, epoch, train_losses)]
             if cf.valid_model:
                 valid_losses += [model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, epoch)]
                 if epoch > 0 and epoch%cf.figure_epoch == 0:

### 2017-11-13 code_base/Synthia_car_trajectory.py
modify learningrate_decay

@@ -37,7 +37,7 @@ def process(cf):
         valid_losses = []
         print(' ---> Training data: ' + cf.sequence_name + ' <---')
         for epoch in range(1, cf.n_epochs + 1):
-            train_losses += [model.train(cf, DG.train_loader, epoch)]
+            train_losses += [model.train(cf, DG.train_loader, epoch, train_losses)]
             if cf.valid_model:
                 valid_losses += [model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, epoch)]
                 if epoch > 0 and epoch%cf.figure_epoch == 0:

### 2017-11-13 code_base/config/synthia_car_trajectory.py

@@ -109,7 +109,7 @@ optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = True
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01___Mon, 06 Nov 2017-11-06 16:08:14/Epoch:100_net_aveErrCoverage:0.8343_aveErrCenter:17.47___.pth'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Mon, 13 Nov 2017-11-13 00:27:55_CNN_LSTM_To_FC/Epoch:13_net_Coverage:0.0883_Center:231.14_CoverageR:0.0300_CenterR:1.82.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
 lstm_input_dims               = [6, 150, 150]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]

### 2017-11-13 code_base/models/PyTorch_model_factory.py

@@ -19,12 +19,31 @@ import sys
 
 
 
-def adjust_learning_rate(lr, optimizer, epoch, decrease_epoch=10):
+def adjust_learning_rate(lr, optimizer, epoch,train_losses, decrease_epoch=10):
     """Sets the learning rate to the initial LR decayed by 10 every 30 epochs"""
-    lr = lr * (0.1 ** (epoch // decrease_epoch))
-    if lr >= 1.0e-6:
-        for param_group in optimizer.param_groups:
-            param_group['lr'] = lr
+
+    if len(train_losses) < 5:
+        return lr
+
+    eva_losses = train_losses[-5:]
+
+    max_value = eva_losses.max()
+    min_value = eva_losses.min()
+    max_loction = eva_losses.argmax()
+    min_location = eva_losses.argmin()
+
+    if np.abs(max_value-min_value)/max_value < 1e-3 or max_loction>min_location:
+        lr = optimizer.param_groups[-1]['lr']
+        lr =lr * 0.1
+        if lr >= 1.0e-6:
+            for param_group in optimizer.param_groups:
+                param_group['lr'] = lr
+    #
+    # lr = lr * (0.1 ** (epoch // decrease_epoch))
+    # if lr >= 1.0e-6:
+    #     for param_group in optimizer.param_groups:
+    #         param_group['lr'] = lr
+
     return lr
 
 
@@ -224,10 +243,10 @@ class Model_Factory_LSTM():
         elif cf.optimizer == 'sgd':
             self.optimiser = optim.SGD(self.net.parameters(), lr=cf.learning_rate, momentum=cf.momentum, weight_decay=cf.weight_decay, nesterov=True)
 
-    def train(self, cf, train_loader, epoch):
+    def train(self, cf, train_loader, epoch, train_losses):
         # begin to train
         self.net.train()
-        lr = adjust_learning_rate(self.cf.learning_rate, self.optimiser, epoch, decrease_epoch=cf.lr_decay_epoch)
+        lr = adjust_learning_rate(self.cf.learning_rate, self.optimiser, epoch,train_losses , decrease_epoch=cf.lr_decay_epoch)
         print('learning rate:', lr)
 
         # if cf.model_name == 'CNN_LSTM_To_FC':

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex
paper writing: dataset collection'

--- 2017-11-12 paper/cvpr2018/cvpr2018_draft.tex
@@
 \usepackage[english]{babel}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
 \usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
+\DeclareCaptionLabelFormat{noname}{#2}
+\captionsetup[algorithm]{labelformat=noname}
+
+\newlength\myindent
+\setlength\myindent{2em}
+\newcommand\bindent[1][\myindent]{%
+  \begingroup
+  \setlength{\itemindent}{#1}
+  \addtolength{\algorithmicindent}{#1}
+}
+\newcommand\eindent{\endgroup}
+
+\usepackage{multirow}
+\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
 
@@
         \caption{ {\small TODO: Pull figure caption goes here.}}
-        \label{fig:response_map}
+        \label{fig:pull_figure}
 \end{figure}
@@
 
-\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving to robustly track a car.
+\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving for robustly vehicle tracking.
 The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.
 
-\item We design various temporal model for the problems of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.
+\item We design various temporal models for the problem of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.
 
-\item We demonstrate the effectiveness of using ``privileged information" further boost the prediction accuracy. [NOT DONE].
+\item We demonstrate the effectiveness of using ``privileged information"(e.g., scene semantics and car pose information) further boost the prediction accuracy. [NOT DONE YET].
 
@@
 \textbf{\emph{1. Object detection, segmentation, instance segmentation}}
+
+TODO: TY
 %%% DW: write related work for visual tracking
@@
 
+TODO: DW
 %% DW: (1)traditional segmentic segmentation dataset
@@
 %%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
+        \caption{ {\small TODO: framework caption goes here.}}
+        \label{fig:framework}
+\end{figure*}
+
 \textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}
@@
 
+TODO: cite below papers;
 ~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.
@@
 
-\subsection{traffic participants detection}
+We first describe our overall approach for car trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
+Our goal is via collecting the visual information from the past to predict the traffic participants future trajectory.
+Fig.~\ref{fig:framework} shows the overall architecture of our proposed framework.
 
-\subsection{instance tracking}
+\subsection{Traffic Participants detection}
+
+\subsection{Instance tracking}
 
 We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
+        \caption{ {\small TODO: Instance association caption goes here.}}
+        \label{fig:Instance_associationn}
+\end{figure}
 
-\subsection{trajectory prediction}
+\subsection{Semantic segmentation}
+We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
+
+\subsection{Trajectory prediction}
 
@@
 The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
-
 There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
@@
 In our experiment, we used only left front camera view data.
-The focus of this paper is on car trajectory prediction on high ways. We list our logic for collecting continuous car tracking in List~\ref{Dataset_collection}. (TODO: make a list).
+
+The focus of this paper is on car trajectory prediction on high ways which corresponds to sequence number 1 in the SYNTHIA dataset.
+We especially concern about the cars that are relatively close to the driver.
+Hence, we start tracking the vehicle when the vehicle's pixel occupancy rate \emph{(POR)} is larger than 0.2\% and stop tracking the instance when the POR is smaller than 0.1\%.
+The POR of 0.2\% and 0.1\% correspond to roughly 30 and 50 meters of relative distance between the driver and tracking vehicle so as to suffice the safety distance for drivers to make timely reaction.
+We follow the traditional paradigm for tracking to collect target's bounding box: $[x, y, w, h]$ of each frame.
+Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
+We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}. 
 Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
 
-\begin{algorithm}
-\caption{Multimodal Deep Dynamic Networks -- training}\label{Dataset_collection}
-\LinesNumbered
-\SetAlgoLined
-\SetAlgoNoEnd
-\DontPrintSemicolon
-\SetKwFunction{zeroes}{zeroes}
-\KwData{\;
-          $ \mathbf{X^1=\{ x^1_i\}_{i \in [1 \ldots t]}}$ - raw input(skeletal) feature sequence.\;
-          $ \mathbf{X^2=\{ x^2_i\}_{i \in [1 \ldots t]}}$ - raw input(depth) feature sequence in the form of \;
-          \hspace{1cm}$M_1 \times M_2 \times T$, where $M_1, M_2$ are the height and width of the input \;
-          \hspace{1cm}  image and $T$ is the number of contiguous frames of the \;
-          \hspace{1cm} spatio-temporal cuboid. \;
-          \hspace{1cm}  {\scriptsize{}Note that the GPU library \emph{cuda-convnet}~\cite{krizhevsky2012imagenet} used requires square size images and $T$ is a multiple of $4$}.\;
-          $ \mathbf{Y=\{ y_i\}_{i \in [1 \ldots t]}}$  - frame based local label (achieved by semi-supervised \; \hspace{1cm} forced-aligment), \;
-          \hspace{1cm}  where $ \mathbf{y_i} \in \{ C * S + \textbf{\emph{1}} \} $ with $C$ is the number of class, $S$ is the  \;
-          \hspace{1cm}  number of hidden states for each class, $\textbf{\emph{1}}$ as ergodic state.
+TODO: generate a table for total number of frames and sequence tracklets!
+
+\begin{algorithm}[h]
+\begin{algorithmic}
+\caption{\textbf{Dataset ground truth construction}}\label{list:dataset_collection}
+\STATE \textbf{Step 1} $\rightarrow $ get traffic participants from ground truth annotation with only cars as instances.
+\STATE \textbf{Step 2} {$\rightarrow $ { 
+\bindent
+  \IF{POR $> 0.2\%$}
+    %\bindent[1.45cm]
+    \STATE $\Rightarrow$ start tracking instance , 
+    \STATE $\Rightarrow$ collecting 3D tracking rectangular: $[x, y, w, h, d_{min}, d_{max}]$
+    \STATE $\Rightarrow$ collecting semantic segmentation image, $I_{seg}$.
+    \STATE $\Rightarrow$ collecting 2d car pose from RGB input $I_{car}$.
+    %\eindent
+  \ELSIF{POR $< 0.1\%$}
+    \STATE $\Rightarrow$ stop tracking 
+    \ENDIF\eindent}
   }
-\For{$m \leftarrow 1$ to $2$}{
-    \SetAlgoVlined
-    \eIf{$m$ is $1$}{
-        Preprocessing the dataCordts2016Cityscapes $ \mathbf{X^1}$ as in Eq.\ref{sk_features}.\;
-        Normalizing(zero mean, unit variance per dimension) the above features and feed to to Eq.\ref{GRBMenergy}. \;
-        Pre-training the networks using \emph{Contrastive Divergence}. \;
-        Supervised fine-tuning the Deep Belief Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} backpropagation.\;
-    }{
-        Preprocessing the data $ \mathbf{X^2}$ (normalizing, median filtering the depth data) Algo.\ref{normalization_scheme_1} or Algo.\ref{normalization_scheme_2}.\;
-        Feeding the above features to Eq.\ref{ReLU}. \;
-        Supervised fine-tuning the Deep 3D Convolutional Neural Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} Backpropagation.\;
-    }
-}
-\KwResult{\;
-        $\mathbf{GDBN}$ - a gaussian bernoulli visible layer Deep Belief Network to \;
-                \hspace{1cm} generate the emission probabilities for hidden markov model.\;
-        $\mathbf{3DCNN}$ - a 3D Deep Convolutional Neural Networks to generate the\;
-                \hspace{1cm}   emission probabilities for hidden markov model.\;
-        $\mathbf{p(H_1)}$ - prior probability for $ \mathbf{Y}$.\;
-        $ \mathbf{p(H_t | H_{t-1})}$ - transition probability for $ \mathbf{Y}$,  enforcing the beginning and \;
-                    \hspace{1cm} ending of a sequence can only start from the first or the last state.
-}
+\STATE \textbf{Step 3} $\rightarrow $ split sequences into tracklets of 23 frames:
+{\bindent
+    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input
+    \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
+\eindent}    
+\end{algorithmic}
 \end{algorithm}
@@
 
-\subsection{Implementations}
+\subsection{Implementations}\label{sec:Implementations}
 
@@
 We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
-We use the pretrained detection network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA. Curretnly
+We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
+A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.
 
-A comprehensive survey of speed/accuracy trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer the keen readers to
+As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
+In this paper, we concerns mostly about cars that are closer to the driver.
+Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
+Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
+
+\begin{table*}\centering
+\ra{1.}
+\begin{tabular}{@{}llllllllllll@{}}\toprule
+\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
+\hline
+\multirow{3}{*}{SSD}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+                    &    recall   & \textbf{92.3}  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+                    &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+\multirow{3}{*}{Faster-RCNN}
+                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
+                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
+                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+\bottomrule
+\end{tabular}
+\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
+\label{tab:ssd_fasterrcnn}
+\end{table*}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Evaluation}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
+        \caption{ {\small TODO: evaluation caption goes here.}}
+        \label{fig:evaluation}
+\end{figure}
 
@@
     \caption{ {\small
-          Baseline comparisons with arrows indicating performance changes comparing with the upper row parallel experiment.
-          First two rows investigate the impact of projecting deep features into a kernel space \emph{vs.} using linear deep features.
-          Next two rows compare the traditional using max location \emph{vs.} the proposed multi-resolution convnets paradigm for decoding target translational movement.
-          Last two rows illustrate the benefit of adaptive learning rate through time (with scale update). }
+         TODO: this table is just a place holder, currently has no meaning.}
           } \label{table_baseline}
@@
     \caption{ {\small
+    TODO: this table is just a place holder, currently has no meaning. WZN will update the numbers
           Comparison with the most recent methods }
@@
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Evaluation Metrics}
+
 \section{Conclusions}
@@
 \section*{Details of the Code}
+ The code will be made public alongside the publication.
 

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex

@@
 \newcommand{\argmin}{\operatornamewithlimits{argmin}}
-%\cvprfinalcopy
+\cvprfinalcopy
 
@@
 \begin{abstract}
-% State the problem, your approach and solution, and the main contributions of the paper.
-Include little if any background and motivation.
-Be factual but comprehensive.
-The material in the abstract should not be repeated later word for word in the paper.
-
-Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
-These models need to be temporally consistent and visually interpretable.
-Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
-In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
-The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
-Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
-Then, a novel DRN-LSTM network is incorporated to fuse the multiple-streams from past frames to predict targets' future trajectories.
-We demonstrate the feasibility of predicting future trajectories of cars for assisting mediated perception.
- We also show the effectiveness of using privileged information (e.g., scene semantics and car pose information) further boost the prediction accuracy across diverse traffic conditions.
-
+TODO: abstract
+This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad.
+I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some.
+Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience.
+Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research).
+But disclaimers are boring, lets get to it!
 \end{abstract}
@@
 \end{figure}
-\textbf{\emph{3. Why is it hard? (E.g. why do naive approaches fail?)}}
+\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}
 
@@
 
-In traditional vision based tracking problems(\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
+In traditional vision based tracking problems (\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
 However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).
@@
 TODO: DW
+
 %% DW: (1)traditional segmentic segmentation dataset
@@
 TODO: cite below papers;
+
 ~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.
@@
 
-\subsubsection{Traffic participants detection}
-
-We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
-We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
-A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.
-
-As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
-In this paper, we concerns mostly about cars that are closer to the driver.
-Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
-Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
-
 \begin{table*}\centering
@@
 \end{table*}
+\subsubsection{Traffic participants detection}
+
+We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
+A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.
+
+As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
+In this paper, we concerns mostly about cars that are closer to the driver.
+Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
+Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
 

### 2017-11-13 code_base/Synthia_car_trajectory.py
for local

@@ -31,7 +31,8 @@ def process(cf):
 
     print('\n > Building model...')
     model = Model_Factory_LSTM(cf)
-
+    #model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, 0)
+    model.test(cf, DG.test_loader, DG.data_mean, DG.data_std, epoch=None)
     if cf.train_model:
         train_losses = []
         valid_losses = []

### 2017-11-13 code_base/config/synthia_car_trajectory.py

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'CNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
+model_name                   = 'LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -109,7 +109,7 @@ optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = True
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Mon, 13 Nov 2017-11-13 00:27:55_CNN_LSTM_To_FC/Epoch:13_net_Coverage:0.0883_Center:231.14_CoverageR:0.0300_CenterR:1.82.PTH'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Sun, 12 Nov 2017-11-12 15:34:35_LSTM_To_FC_Noshuffle_Sixpoint_Nosemantics/Epoch:30_net_Coverage:0.6430_Center:55.87_CoverageR:0.2335_CenterR:0.41.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
 lstm_input_dims               = [6, 150, 150]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]

### 2017-11-13 code_base/models/PyTorch_model_factory.py
ouput evaluation

@@ -16,7 +16,7 @@ import numpy as np
 from matplotlib import pyplot as plt
 import os
 import sys
-
+import json
 
 
 def adjust_learning_rate(lr, optimizer, epoch,train_losses, decrease_epoch=10):
@@ -315,6 +315,11 @@ class Model_Factory_LSTM():
         aveErrCoverage_realworld = []
         aveErrCenter_realworld = []
         valid_losses = []
+        errCoverage = []
+        iou_2d = []
+        errCenter_realworld =[]
+        iou_3d = []
+
         for i, (sementic, input_trajectory, target_trajectory) in enumerate(valid_loader):
             print(i)
             sementic, input_trajectory, target_trajectory = Variable(sementic.cuda(async=True)), \
@@ -335,10 +340,20 @@ class Model_Factory_LSTM():
             aveErrCenter.append(evalua_values[1])
             aveErrCoverage_realworld.append(evalua_values[4])
             aveErrCenter_realworld.append(evalua_values[5])
+            errCoverage.append(evalua_values[2])
+            iou_2d.append(evalua_values[3])
+            errCenter_realworld.append(evalua_values[6])
+            iou_3d.append(evalua_values[7])
             # output_trajectories.append(output)
             # target_trajectories.append(target_trajectory)
 
         # loss mean
+        track_plot = {}
+        track_plot['errCoverage'] = errCoverage
+        track_plot['iou_2d'] = iou_2d
+        track_plot['errCenter_realworld'] = errCenter_realworld
+        track_plot['iou_3d'] = iou_3d
+
         self.loss = np.array(valid_losses).mean()
         # print('Valid Loss', epoch, self.loss)
 
@@ -363,6 +378,9 @@ class Model_Factory_LSTM():
 
             model_checkpoint = 'Epoch:%2d_net_Coverage:%.4f_Center:%.2f_CoverageR:%.4f_CenterR:%.2f.PTH' % \
                                (epoch, aveErrCoverage, aveErrCenter, aveErrCoverage_realworld, aveErrCenter_realworld)
+            np.save('/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/tracking_plot/' + 'valid', track_plot)
+
+
         else:
             print('############### TEST #############################################')
             print('Test Loss', epoch, self.loss)
@@ -371,6 +389,8 @@ class Model_Factory_LSTM():
[…]

### 2017-11-13 code_base/tools/PyTorch_data_generator.py

@@ -230,6 +230,51 @@ class DataGenerator_Synthia_car_trajectory():
             self.cf = cf
             print('Loading data')
             train_data, valid_data, test_data, self.data_mean, self.data_std, train_img_list, valid_img_list, test_img_list = prepare_data_image_list(cf)
+
+            # deal images and relocate train_img_list & valid_img_list & test_img_list
+            self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
+
+
+            # def deal_img_list(img_list, item):
+            #
+            #     # parent dir
+            #     img_dir = self.root_dir + '/' + img_list[item][0].split('/')[
+            #         0] + '/' + 'GT/LABELS' + '/' + self.cf.data_stereo + '/' + self.cf.data_camera
+            #
+            #     def img_name(i):
+            #         return os.path.join(img_dir, img_list[item][i].split('/')[1])
+            #
+            #     def semantic_image(img_name):
+            #         try:
+            #             input = cv.imread(img_name, -1)
+            #             semantic_image = np.int8(input[:, :, 2])
+            #         except IOError:
+            #             # unfortunately, some images are corrupted. Hence, we need to manually exclude them.
+            #             print("Image failed loading: ", img_name)
+            #
+            #         # resize
+            #         semantic_image = imresize(semantic_image, size=0.125, interp='nearest', mode='F')
+            #         # Convert to training labels
+            #         w, h = semantic_image.shape
+            #         # Create one-hot encoding
+            #         semantic_image_one_hot = np.zeros(shape=(self.cf.cnn_class_num, w, h))
+            #         for c in range(self.cf.cnn_class_num):
+            #             semantic_image_one_hot[c][semantic_image == c] = 1
+            #
+            #         # Convert to tensors
+            #         semantic_image_t = torch.Tensor(semantic_image_one_hot)
+            #         return semantic_image_t
+            #
+            #     if self.cf.model_name == 'CNN_LSTM_To_FC':
+            #         semantic_images = torch.stack(
+            #             [semantic_image(img_name(i)) for i in range(self.cf.lstm_input_frame)], dim=0)
+            #
+            #
+            #     return semantic_images
+
+
+
+
             # Load training set
             print('\n > Loading training, valid, test set')
             train_dataset = BB_ImageDataGenerator_Synthia(cf, train_data, train_img_list, crop=False, flip=False)

### 2017-11-13 code_base/tools/PyTorch_model_training.py

@@ -171,7 +171,7 @@ def calc_seq_err_robust(results, rect_anno, focal_length):
         aveErrCoverage_realworld = totalerrCoverage_realworld / float(seq_length)
         aveErrCenter_realworld = totalerrCenter_realworld / float(seq_length)
 
-    return aveErrCoverage, aveErrCenter, errCoverage, iou_2d, \
+    return aveErrCoverage, aveErrCenter, errCenter, iou_2d, \
            aveErrCoverage_realworld, aveErrCenter_realworld, errCenter_realworld, iou_3d
 
 

### 2017-11-13 code_base/models/PyTorch_model_factory.py
ouput evaluation

@@ -16,7 +16,7 @@ import numpy as np
 from matplotlib import pyplot as plt
 import os
 import sys
-
+import json
 
 
 def adjust_learning_rate(lr, optimizer, epoch,train_losses, decrease_epoch=10):
@@ -316,6 +316,11 @@ class Model_Factory_LSTM():
         aveErrCoverage_realworld = []
         aveErrCenter_realworld = []
         valid_losses = []
+        errCoverage = []
+        iou_2d = []
+        errCenter_realworld =[]
+        iou_3d = []
+
         for i, (sementic, input_trajectory, target_trajectory) in enumerate(valid_loader):
             print(i)
             sementic, input_trajectory, target_trajectory = Variable(sementic.cuda(async=True)), \
@@ -336,10 +341,20 @@ class Model_Factory_LSTM():
             aveErrCenter.append(evalua_values[1])
             aveErrCoverage_realworld.append(evalua_values[4])
             aveErrCenter_realworld.append(evalua_values[5])
+            errCoverage.append(evalua_values[2])
+            iou_2d.append(evalua_values[3])
+            errCenter_realworld.append(evalua_values[6])
+            iou_3d.append(evalua_values[7])
             # output_trajectories.append(output)
             # target_trajectories.append(target_trajectory)
 
         # loss mean
+        track_plot = {}
+        track_plot['errCoverage'] = errCoverage
+        track_plot['iou_2d'] = iou_2d
+        track_plot['errCenter_realworld'] = errCenter_realworld
+        track_plot['iou_3d'] = iou_3d
+
         self.loss = np.array(valid_losses).mean()
         # print('Valid Loss', epoch, self.loss)
 
@@ -364,6 +379,9 @@ class Model_Factory_LSTM():
 
             model_checkpoint = 'Epoch:%2d_net_Coverage:%.4f_Center:%.2f_CoverageR:%.4f_CenterR:%.2f.PTH' % \
                                (epoch, aveErrCoverage, aveErrCenter, aveErrCoverage_realworld, aveErrCenter_realworld)
+            np.save('/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/tracking_plot/' + 'valid', track_plot)
+
+
         else:
             print('############### TEST #############################################')
             print('Test Loss', epoch, self.loss)
@@ -372,6 +390,8 @@ class Model_Factory_LSTM():
[…]

### 2017-11-13 code_base/config/synthia_car_trajectory.py
for conflict

@@ -113,23 +113,11 @@ load_trained_model           = False
 train_model_path             = '/home/stevenwudi/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01___Mon, 06 Nov 2017-11-06 16:08:14/Epoch:100_net_aveErrCoverage:0.8343_aveErrCenter:17.47___.pth'
 #### LSTM training variables #################
 # LSTM_ManyToMany
-<<<<<<< HEAD
 lstm_input_dims               = [6, 150, 150]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]
 lstm_hidden_sizes             = [150, 150, 150]    # [layer1_hidden_size, layer2_hidden_size,...]
 outlayer_input_dim            = 150          # outlayer's input dim.Generally, identify to hidden_sizes[-1]
 outlayer_output_dim           = 6            # outlayer output: [x,y,w,h, d_min, d_max]
-||||||| parent of deb295e... add smoothL1Loss
-lstm_inputsize               = 6   # LSTM input: [x,y,w,h, d_min, d_max]
-lstm_hiddensize              = 50
-lstm_numlayers               = 2
-lstm_outputsize              = 6
-=======
-lstm_inputsize               = 6   # LSTM input: [x,y,w,h, d_min, d_max]
-lstm_hiddensize              = 50
-lstm_hiddensize              = 50
-lstm_numlayers               = 2
-lstm_outputsize              = 6
->>>>>>> deb295e... add smoothL1Loss
+
 # LSTM_To_FC
 lstmToFc_input_dims           = [6, 100, 300]              # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]
 lstmToFc_hidden_sizes         = [100, 300, 300]            # [layer1_hidden_size, layer2_hidden_size,...]

### 2017-11-13 code_base/models/PyTorch_model_factory.py
adjust learning rate

@@ -19,13 +19,13 @@ import sys
 import json
 
 
-def adjust_learning_rate(lr, optimizer, epoch,train_losses, decrease_epoch=10):
+def adjust_learning_rate(lr, optimizer, epoch, train_losses, decrease_epoch=10):
     """Sets the learning rate to the initial LR decayed by 10 every 30 epochs"""
 
     if len(train_losses) < 5:
         return lr
 
-    eva_losses = train_losses[-5:]
+    eva_losses = np.array(train_losses[-5:])
 
     max_value = eva_losses.max()
     min_value = eva_losses.min()

### 2017-11-13 code_base/Synthia_car_trajectory.py
for local

@@ -31,8 +31,7 @@ def process(cf):
 
     print('\n > Building model...')
     model = Model_Factory_LSTM(cf)
-    #model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, 0)
-    model.test(cf, DG.test_loader, DG.data_mean, DG.data_std, epoch=None)
+
     if cf.train_model:
         train_losses = []
         valid_losses = []

### 2017-11-13 code_base/config/synthia_car_trajectory.py

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
+model_name                   = 'CNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -106,10 +106,10 @@ n_epochs                     = 200            # Number of epochs during training
 cuda                         = True
 loss                         = 'SmoothL1Loss'       # 'MSE', 'SmoothL1Loss'
 optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
-learning_rate                = 0.01          # Training learning rate
+learning_rate                = 0.001          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = True
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Sun, 12 Nov 2017-11-12 15:34:35_LSTM_To_FC_Noshuffle_Sixpoint_Nosemantics/Epoch:30_net_Coverage:0.6430_Center:55.87_CoverageR:0.2335_CenterR:0.41.PTH'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Mon, 13 Nov 2017-11-13 11:27:35_CNN_LSTM_To_FC/Epoch: 5_net_Coverage:0.0859_Center:231.26_CoverageR:0.0423_CenterR:1.22.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
 lstm_input_dims               = [6, 150, 150]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]

### 2017-11-13 code_base/tools/PyTorch_data_generator.py

@@ -234,48 +234,6 @@ class DataGenerator_Synthia_car_trajectory():
             # deal images and relocate train_img_list & valid_img_list & test_img_list
             self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
 
-
-            # def deal_img_list(img_list, item):
-            #
-            #     # parent dir
-            #     img_dir = self.root_dir + '/' + img_list[item][0].split('/')[
-            #         0] + '/' + 'GT/LABELS' + '/' + self.cf.data_stereo + '/' + self.cf.data_camera
-            #
-            #     def img_name(i):
-            #         return os.path.join(img_dir, img_list[item][i].split('/')[1])
-            #
-            #     def semantic_image(img_name):
-            #         try:
-            #             input = cv.imread(img_name, -1)
-            #             semantic_image = np.int8(input[:, :, 2])
-            #         except IOError:
-            #             # unfortunately, some images are corrupted. Hence, we need to manually exclude them.
-            #             print("Image failed loading: ", img_name)
-            #
-            #         # resize
-            #         semantic_image = imresize(semantic_image, size=0.125, interp='nearest', mode='F')
-            #         # Convert to training labels
-            #         w, h = semantic_image.shape
-            #         # Create one-hot encoding
-            #         semantic_image_one_hot = np.zeros(shape=(self.cf.cnn_class_num, w, h))
-            #         for c in range(self.cf.cnn_class_num):
-            #             semantic_image_one_hot[c][semantic_image == c] = 1
-            #
-            #         # Convert to tensors
-            #         semantic_image_t = torch.Tensor(semantic_image_one_hot)
-            #         return semantic_image_t
-            #
-            #     if self.cf.model_name == 'CNN_LSTM_To_FC':
-            #         semantic_images = torch.stack(
-            #             [semantic_image(img_name(i)) for i in range(self.cf.lstm_input_frame)], dim=0)
-            #
-            #
-            #     return semantic_images
-
-
-
-
-            # Load training set
             print('\n > Loading training, valid, test set')
             train_dataset = BB_ImageDataGenerator_Synthia(cf, train_data, train_img_list, crop=False, flip=False)
             valid_dataset = BB_ImageDataGenerator_Synthia(cf, valid_data, valid_img_list,  crop=False, flip=False)

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex

@@
 \begin{abstract}
-TODO: abstract
-This guide is patterned after my “Doing well in your courses”, a post I wrote a long time ago on some of the tips/tricks I’ve developed during my undergrad.
-I’ve received nice comments about that guide, so in the same spirit, now that my PhD has come to an end I wanted to compile a similar retrospective document in hopes that it might be helpful to some.
-Unlike the undergraduate guide, this one was much more difficult to write because there is significantly more variation in how one can traverse the PhD experience.
-Therefore, many things are likely contentious and a good fraction will be specific to what I’m familiar with (Computer Science / Machine Learning / Computer Vision research).
-But disclaimers are boring, lets get to it!
+% State the problem, your approach and solution, and the main contributions of the paper.
+Include little if any background and motivation.
+Be factual but comprehensive.
+The material in the abstract should not be repeated later word for word in the paper.
+
+Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
+These models need to be temporally consistent and visually interpretable.
+Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
+In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
+The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
+Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
+Then, a novel DRN-LSTM network is incorporated to fuse the multiple-streams from past frames to predict targets' future trajectories.
+We demonstrate the feasibility of predicting future trajectories of cars for assisting mediated perception.
+ We also show the effectiveness of using privileged information (e.g., scene semantics and car pose information) further boost the prediction accuracy across diverse traffic conditions.
 \end{abstract}
@@
 \section{Introduction}
-
-\begin{figure}
-
-\includegraphics[width=8.8cm]{pool_figure}
-\caption{pool figure}
-\label{figure10}
-\end{figure}
 
@@
 
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
+        \caption{ {\small TODO: framework caption goes here.}}
+        \label{fig:framework}
+\end{figure*}
+
 \textbf{\emph{3. Dataset for autonoumous driving}}
@@
 %%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
-\begin{figure*}[t]
-        \centering
-        \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
-        \caption{ {\small TODO: framework caption goes here.}}
-        \label{fig:framework}
-\end{figure*}
 
@@
 We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
-        \caption{ {\small TODO: Instance association caption goes here.}}
-        \label{fig:Instance_associationn}
-\end{figure}
 
@@
 \subsection{Trajectory prediction}
-
 We compare two temporal models based on LSTM cells for predicting the car trajectory.
@@
 
+\subsubsection{Traffic participants detection}
+
+We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
+A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.
+
+As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
+In this paper, we concerns mostly about cars that are closer to the driver.
+Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
+Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
+
 \begin{table*}\centering
@@
 \end{table*}
-\subsubsection{Traffic participants detection}
-
-We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
-We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
-A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.
-
-As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
-In this paper, we concerns mostly about cars that are closer to the driver.
-Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
-Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
 
@@
 We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
+        \caption{ {\small TODO: Instance association caption goes here.}}
+        \label{fig:Instance_associationn}
+\end{figure}
 

### 2017-11-13 code_base/Synthia_car_trajectory.py
add config variable for dataloader

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '3'
+os.environ['CUDA_VISIBLE_DEVICES'] = '2'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-13 code_base/config/synthia_car_trajectory.py
add config variable for dataloader

@@ -42,6 +42,7 @@ debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
 #random_size_crop             = (350*2, 460*2)      # Random size crop of the image during training
+#------ DataLoader ------#
 workers                      = 32              #  how many subprocesses to use for data loading. 0 means that the data will be loaded in the main process
 batch_size_train             = 64            # Batch size during training
 batch_size_valid             = 20              # Batch size during validation
@@ -49,6 +50,10 @@ batch_size_test              = 20              # Batch size during testing
 dataloader_num_workers_train = 1        # Number of dataload works during training
 dataloader_num_workers_valid = 1        # Number of dataload works during valid
 dataloader_num_workers_test  = 1        # Number of dataload works during test
+dataloader_load_prepare_data = True     # whether or not load prepare_data for DataLoader
+dataloader_load_prepare_data_path = ''
+dataloader_save_prepare_data = True     # whether or not save generated prepare_data for DataLoader
+dataloader_save_prepare_data_path = ''  
 # Data shuffle
 shuffle_train                = False            # No shuffling because the time sequence matters
 shuffle_valid                = False           # Whether to shuffle the validation data

### 2017-11-13 code_base/tools/PyTorch_data_generator.py
add Resized_BB_ImageDataGenerator_Synthia

@@ -235,15 +235,16 @@ class DataGenerator_Synthia_car_trajectory():
             self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
 
             print('\n > Loading training, valid, test set')
-            train_dataset = BB_ImageDataGenerator_Synthia(cf, train_data, train_img_list, crop=False, flip=False)
-            valid_dataset = BB_ImageDataGenerator_Synthia(cf, valid_data, valid_img_list,  crop=False, flip=False)
-            test_dataset = BB_ImageDataGenerator_Synthia(cf, test_data, test_img_list, crop=False, flip=False)
+            train_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, train_data, train_img_list, crop=False, flip=False)
+            valid_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, valid_data, valid_img_list,  crop=False, flip=False)
+            test_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, test_data, test_img_list, crop=False, flip=False)
 
             self.train_loader = DataLoader(train_dataset, batch_size=cf.batch_size_train, shuffle=True,
                                            num_workers=cf.workers, pin_memory=True)
-            self.valid_loader = DataLoader(valid_dataset, batch_size=cf.batch_size_valid, num_workers=cf.workers, pin_memory=True)
-            self.test_loader = DataLoader(test_dataset, batch_size=cf.batch_size_test, num_workers=cf.workers, pin_memory=True)
-
+            self.valid_loader = DataLoader(valid_dataset, batch_size=cf.batch_size_valid, num_workers=cf.workers,
+                                           pin_memory=True)
+            self.test_loader = DataLoader(test_dataset, batch_size=cf.batch_size_test, num_workers=cf.workers,
+                                          pin_memory=True)
 
 
 class BB_ImageDataGenerator_Synthia(Dataset):
@@ -324,6 +325,45 @@ class BB_ImageDataGenerator_Synthia(Dataset):
 
         return semantic_images, input_trajectorys, target_trajectorys
 
+# resized semantic image
+class Resized_BB_ImageDataGenerator_Synthia(Dataset):
+    def __init__(self, cf, trajectory_data, img_list, crop=True, flip=True):
+        """
+        :param root_dir: Directory will all the images
+        :param label_dir: Directory will all the label images
+        :param transform:  (callable, optional): Optional tra
[…]

### 2017-11-13 code_base/config/synthia_car_trajectory.py
add config for dataloader

@@ -53,7 +53,7 @@ dataloader_num_workers_test  = 1        # Number of dataload works during test
 dataloader_load_prepare_data = True     # whether or not load prepare_data for DataLoader
 dataloader_load_prepare_data_path = ''
 dataloader_save_prepare_data = True     # whether or not save generated prepare_data for DataLoader
-dataloader_save_prepare_data_path = ''  
+dataloader_save_prepare_data_path = ''
 # Data shuffle
 shuffle_train                = False            # No shuffling because the time sequence matters
 shuffle_valid                = False           # Whether to shuffle the validation data

### 2017-11-13 code_base/tools/PyTorch_data_generator.py
modify Resized_BB_ImageDataGenerator_Synthia

@@ -338,7 +338,6 @@ class Resized_BB_ImageDataGenerator_Synthia(Dataset):
         self.cf = cf
         self.img_list = img_list
         self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
-
         self.crop = crop
         # self.crop_size = cf.crop_size
         self.flip = flip

### 2017-11-13 code_base/tools/PyTorch_model_training.py
add get_img_resized_list

@@ -1,6 +1,8 @@
 import h5py
 import os
 import numpy as np
+import cv2 as cv
+from scipy.misc import imresize
 import torch
 import torch.nn as nn
 import torch.optim as optim
@@ -113,6 +115,62 @@ def get_img_list(train_data, valid_data, test_data):
 
     return train_img_list, valid_img_list, test_img_list
 
+def get_img_resized_list(cf, train_data, valid_data, test_data):
+
+    root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
+    def data_img_dir(data):
+        return root_dir + '/' + data[0][0][6].split('/')[
+            0] + '/' + 'GT/LABELS' + '/' + cf.data_stereo + '/' + cf.data_camera
+
+    train_img_dir = data_img_dir(train_data)
+    valid_img_dir = data_img_dir(valid_data)
+    test_img_dir = data_img_dir(test_data)
+
+    def img_name(img_dir, item):
+        return os.path.join(img_dir, item.split('/')[1])
+
+    def semantic_image(img_name):
+        try:
+            input = cv.imread(img_name, -1)
+            semantic_image = np.int8(input[:, :, 2])
+        except IOError:
+            # unfortunately, some images are corrupted. Hence, we need to manually exclude them.
+            print("Image failed loading: ", img_name)
+        # resize
+        semantic_image = imresize(semantic_image, size=0.125, interp='nearest', mode='F')
+        # Convert to training labels
+        w, h = semantic_image.shape
+        # Create one-hot encoding
+        semantic_image_one_hot = np.zeros(shape=(cf.cnn_class_num, w, h))
+        for c in range(cf.cnn_class_num):
+            semantic_image_one_hot[c][semantic_image == c] = 1
+        # Convert to tensors
+        semantic_image_t = torch.Tensor(semantic_image_one_hot)
+        return semantic_image_t
+
+    train_img_list = []
+    for d in train_data:
+        item_list = [x[6] for x in d[:cf.lstm_input_frame]]
+        item_list = [semantic_image(img_name(train_img_dir, item)) for item in item_list]
+        item_list = torch.stack(item_list, dim=0)
+        train_img_list.append(item_list)
+
+    valid_img_list = []
+    for d in valid_data:
+        item_list = [x[6] for x in d[:cf.lstm_input_frame]]
+        item_list = [semantic_image(img_name(valid_img_dir, item)) for item in item_list]
+        item_list = torch.stack(item_list, dim=0)
[…]

### 2017-11-13 code_base/config/synthia_car_trajectory.py
add load or save prepared_data

@@ -50,10 +50,10 @@ batch_size_test              = 20              # Batch size during testing
 dataloader_num_workers_train = 1        # Number of dataload works during training
 dataloader_num_workers_valid = 1        # Number of dataload works during valid
 dataloader_num_workers_test  = 1        # Number of dataload works during test
-dataloader_load_prepare_data = True     # whether or not load prepare_data for DataLoader
-dataloader_load_prepare_data_path = ''
+dataloader_load_prepare_data = False     # whether or not load prepare_data for DataLoader
+dataloader_load_prepare_data_path = '/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/prepared_data.npy'
 dataloader_save_prepare_data = True     # whether or not save generated prepare_data for DataLoader
-dataloader_save_prepare_data_path = ''
+dataloader_save_prepare_data_path = '/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/prepared_data.npy'
 # Data shuffle
 shuffle_train                = False            # No shuffling because the time sequence matters
 shuffle_valid                = False           # Whether to shuffle the validation data

### 2017-11-13 code_base/models/PyTorch_model_factory.py

@@ -321,7 +321,7 @@ class Model_Factory_LSTM():
         iou_3d = []
 
         for i, (sementic, input_trajectory, target_trajectory) in enumerate(valid_loader):
-            print(i)
+            # print(i)
             sementic, input_trajectory, target_trajectory = Variable(sementic.cuda(async=True)), \
                                                             Variable(input_trajectory.cuda(async=True)), \
                                                             Variable(target_trajectory.cuda(async=True))

### 2017-11-13 code_base/tools/PyTorch_model_training.py

@@ -148,13 +148,6 @@ def get_img_resized_list(cf, train_data, valid_data, test_data):
         semantic_image_t = torch.Tensor(semantic_image_one_hot)
         return semantic_image_t
 
-    train_img_list = []
-    for d in train_data:
-        item_list = [x[6] for x in d[:cf.lstm_input_frame]]
-        item_list = [semantic_image(img_name(train_img_dir, item)) for item in item_list]
-        item_list = torch.stack(item_list, dim=0)
-        train_img_list.append(item_list)
-
     valid_img_list = []
     for d in valid_data:
         item_list = [x[6] for x in d[:cf.lstm_input_frame]]
@@ -169,23 +162,38 @@ def get_img_resized_list(cf, train_data, valid_data, test_data):
         item_list = torch.stack(item_list, dim=0)
         test_img_list.append(item_list)
 
+    train_img_list = []
+    for d in train_data:
+        item_list = [x[6] for x in d[:cf.lstm_input_frame]]
+        item_list = [semantic_image(img_name(train_img_dir, item)) for item in item_list]
+        item_list = torch.stack(item_list, dim=0)
+        train_img_list.append(item_list)
+
     return train_img_list, valid_img_list, test_img_list
 
-
+#
 def prepare_data_image_list(cf):
-    import pickle
-    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_train.npy'), 'rb') as fp:
-        train_data = pickle.load(fp)
-    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_valid.npy'), 'rb') as fp:
-        valid_data = pickle.load(fp)
-    with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_test.npy'), 'rb') as fp:
-        test_data = pickle.load(fp)
+    if cf.dataloader_load_prepare_data:
+        # load data
+        prepared_data = np.load(cf.dataloader_load_prepare_data_path)
+    else:
+        import pickle
+        with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_train.npy'), 'rb') as fp:
+            train_data = pickle.load(fp)
+        with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_valid.npy'), 'rb') as fp:
+            valid_data = pickle.load(fp)
+        with open(os.path.join(cf.shared_path, cf.problem_type, cf.sequence_name + '_test.npy'), 'rb') as fp:
[…]

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex
paper writing: dataset section

@@
 \subsection{Trajectory prediction}
+
 We compare two temporal models based on LSTM cells for predicting the car trajectory.
@@
 
-Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
+Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
 We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
@@
 The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
-The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
+The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
 There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
@@
 
-The focus of this paper is on car trajectory prediction on high ways which corresponds to sequence number 1 in the SYNTHIA dataset.
+The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset.
 We especially concern about the cars that are relatively close to the driver.
-Hence, we start tracking the vehicle when the vehicle's pixel occupancy rate \emph{(POR)} is larger than 0.2\% and stop tracking the instance when the POR is smaller than 0.1\%.
-The POR of 0.2\% and 0.1\% correspond to roughly 30 and 50 meters of relative distance between the driver and tracking vehicle so as to suffice the safety distance for drivers to make timely reaction.
-We follow the traditional paradigm for tracking to collect target's bounding box: $[x, y, w, h]$ of each frame.
+In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
+As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
+Since depth information is also provided alongside in the SYNTHIA dataset, we back-projecting the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracking vehicle.
+Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
+We follow the prediction time allocation as in~\cite{xu2017end} that the historical time-span is 3 seconds (corresponds to 15 frames with 5 Hz frame rate in the SYNTHIA dataset).
+However, in contrast with~\cite{xu2017end} where only the next 1/3rd of a second is predicted, we strive to predict the next 1.5 second's future trajectory as mentioned previously that it's the reaction time accident reconstruction specialists commonly used~\cite{mcgehee2000driver}.
+
+We follow the traditional paradigm for visual tracking to collect target's bounding box: $[x, y, w, h]$ of each frame.
 Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
+The train/valid/test are split as 80\%/10\%/10\% of the total tracklets.
 We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
-Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
+Some sample frames with semantic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
 
@@
 \begin{algorithmic}
-\caption{\textbf{Dataset ground truth construction}}\label{list:dataset_collection}
-\STATE \textbf{Step 1} $\rightarrow $ get traffic participants from ground truth annotation with only cars as instances.
-\STATE \textbf{Step 2} {$\rightarrow $ {
+\caption{\textbf{Car trajectory ground truth collection}}\label{list:dataset_collection}
+\STATE \textbf{Step 1} $\rightarrow $ acquiring traffic participants from ground truth annotations with only ``car" as instances.
+\STATE \textbf{Step 2} {$\rightarrow $ acquiring frame-based instance information:
+{
 \bindent
@@
     %\bindent[1.45cm]
-    \STATE $\Rightarrow$ start tracking instance ,
-    \STATE $\Rightarrow$ collecting 3D tracking rectangular: $[x, y, w, h, d_{min}, d_{max}]$
-    \STATE $\Rightarrow$ collecting semantic segmentation image, $I_{seg}$.
-    \STATE $\Rightarrow$ collecting 2d car pose from RGB input $I_{car}$.
+    \STATE $\Rightarrow$ start tracking instance;
+    \STATE $\Rightarrow$ collecting 3D tracking boundingbox: $[x, y, w, h, d_{min}, d_{max}]$;
+    \STATE $\Rightarrow$ collecting semantic labeling image $I_{seg}$;
+    \STATE $\Rightarrow$ collecting 2D car pose from RGB input $I_{car}$;
     %\eindent
   \ELSIF{POR $< 0.1\%$}
-    \STATE $\Rightarrow$ stop tracking
+    \STATE $\Rightarrow$ stop tracking.
     \ENDIF\eindent}
   }
-\STATE \textbf{Step 3} $\rightarrow $ split sequences into tracklets of 23 frames:
+\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with step size 1:
 {\bindent
-    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input
+    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input;
   \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
   \eindent}
+
 \end{algorithmic}

### 2017-11-13 code_base/tools/PyTorch_model_training.py
modify calc_seq_err_robust

@@ -138,6 +138,14 @@ def calc_seq_err_robust(results, rect_anno, focal_length):
 
     seq_length = results.shape[1]
 
+    aveErrCoverages = []
+    aveErrCenters = []
+    errCenters = []
+    iou_2ds = []
+    aveErrCoverage_realworlds = []
+    aveErrCenter_realworlds = []
+    errCenter_realworlds = []
+    iou_3ds = []
     for batch_num in range(len(results)):
         res = results[batch_num]
         anno = rect_anno[batch_num]
@@ -169,9 +177,23 @@ def calc_seq_err_robust(results, rect_anno, focal_length):
         aveErrCoverage_realworld = totalerrCoverage_realworld / float(seq_length)
         aveErrCenter_realworld = totalerrCenter_realworld / float(seq_length)
 
-    return aveErrCoverage, aveErrCenter, errCenter, iou_2d, \
-           aveErrCoverage_realworld, aveErrCenter_realworld, errCenter_realworld, iou_3d
+        aveErrCoverages.append(aveErrCoverage)
+        aveErrCenters.append(aveErrCenter)
+        errCenters.append(errCenter)
+        iou_2ds.append(iou_2d)
 
+        aveErrCoverage_realworlds.append(aveErrCoverage_realworld)
+        aveErrCenter_realworlds.append(aveErrCenter_realworld)
+        errCenter_realworlds.append(errCenter_realworld)
+        iou_3ds.append(iou_3d)
+
+    aveErrCoverage = np.array(aveErrCoverages).mean()
+    aveErrCenter = np.array(aveErrCenters).mean()
+    aveErrCoverage_realworld = np.array(aveErrCoverage_realworlds).mean()
+    aveErrCenter_realworld = np.array(aveErrCenter_realworlds).mean()
+
+    return aveErrCoverage, aveErrCenter, errCenters, iou_2ds, \
+           aveErrCoverage_realworld, aveErrCenter_realworld, errCenter_realworlds, iou_3ds
 
 def ssd_2d(x, y):
     s = 0

### 2017-11-13 code_base/tools/PyTorch_model_training.py
modify calc_seq_err_robust

@@ -223,6 +223,14 @@ def calc_seq_err_robust(results, rect_anno, focal_length):
 
     seq_length = results.shape[1]
 
+    aveErrCoverages = []
+    aveErrCenters = []
+    errCenters = []
+    iou_2ds = []
+    aveErrCoverage_realworlds = []
+    aveErrCenter_realworlds = []
+    errCenter_realworlds = []
+    iou_3ds = []
     for batch_num in range(len(results)):
         res = results[batch_num]
         anno = rect_anno[batch_num]
@@ -254,9 +262,23 @@ def calc_seq_err_robust(results, rect_anno, focal_length):
         aveErrCoverage_realworld = totalerrCoverage_realworld / float(seq_length)
         aveErrCenter_realworld = totalerrCenter_realworld / float(seq_length)
 
-    return aveErrCoverage, aveErrCenter, errCenter, iou_2d, \
-           aveErrCoverage_realworld, aveErrCenter_realworld, errCenter_realworld, iou_3d
+        aveErrCoverages.append(aveErrCoverage)
+        aveErrCenters.append(aveErrCenter)
+        errCenters.append(errCenter)
+        iou_2ds.append(iou_2d)
 
+        aveErrCoverage_realworlds.append(aveErrCoverage_realworld)
+        aveErrCenter_realworlds.append(aveErrCenter_realworld)
+        errCenter_realworlds.append(errCenter_realworld)
+        iou_3ds.append(iou_3d)
+
+    aveErrCoverage = np.array(aveErrCoverages).mean()
+    aveErrCenter = np.array(aveErrCenters).mean()
+    aveErrCoverage_realworld = np.array(aveErrCoverage_realworlds).mean()
+    aveErrCenter_realworld = np.array(aveErrCenter_realworlds).mean()
+
+    return aveErrCoverage, aveErrCenter, errCenters, iou_2ds, \
+           aveErrCoverage_realworld, aveErrCenter_realworld, errCenter_realworlds, iou_3ds
 
 def ssd_2d(x, y):
     s = 0

### 2017-11-13 code_base/config/synthia_car_trajectory.py
for local

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'CNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
+model_name                   = 'LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -109,7 +109,7 @@ optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.001          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = True
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Mon, 13 Nov 2017-11-13 11:27:35_CNN_LSTM_To_FC/Epoch: 5_net_Coverage:0.0859_Center:231.26_CoverageR:0.0423_CenterR:1.22.PTH'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Sun, 12 Nov 2017-11-12 15:34:35_LSTM_To_FC_Noshuffle_Sixpoint_Nosemantics/Final_test:Coverage:0.3915_Center:109.21_CoverageR:0.0674_CenterR:0.94.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
 lstm_input_dims               = [6, 150, 150]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]

### 2017-11-14 code_base/Synthia_car_trajectory.py
modify adjust learning rate

@@ -35,8 +35,10 @@ def process(cf):
         train_losses = []
         valid_losses = []
         print(' ---> Training data: ' + cf.sequence_name + ' <---')
+        lastupdate_epoch = 0
         for epoch in range(1, cf.n_epochs + 1):
-            train_losses += [model.train(cf, DG.train_loader, epoch, train_losses)]
+            train_loss, lastupdate_epoch = model.train(cf, DG.train_loader, epoch, lastupdate_epoch, train_losses)
+            train_losses.append(train_loss)
             if cf.valid_model:
                 valid_losses += [model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, epoch)]
                 if epoch > 0 and epoch%cf.figure_epoch == 0:

### 2017-11-14 code_base/models/PyTorch_model_factory.py

@@ -19,13 +19,13 @@ import sys
 import json
 
 
-def adjust_learning_rate(lr, optimizer, epoch, train_losses, decrease_epoch=10):
+def adjust_learning_rate(lr, optimizer, epoch, lastupdate_epoch, train_losses, decrease_epoch=10):
     """Sets the learning rate to the initial LR decayed by 10 every 30 epochs"""
 
-    if len(train_losses) < 10:
-        return lr
+    if epoch-lastupdate_epoch < 10:
+        return optimizer.param_groups[-1]['lr']
 
-    eva_losses = np.array(train_losses[-5:])
+    eva_losses = np.array(train_losses[-10:])
 
     max_value = eva_losses.max()
     min_value = eva_losses.min()
@@ -34,17 +34,21 @@ def adjust_learning_rate(lr, optimizer, epoch, train_losses, decrease_epoch=10):
 
     if np.abs(max_value-min_value)/max_value < 1e-4 or max_loction>min_location:
         lr = optimizer.param_groups[-1]['lr']
-        lr =lr * 0.1
+        lr = lr * 0.1
+
         if lr >= 1.0e-6:
             for param_group in optimizer.param_groups:
                 param_group['lr'] = lr
+            lastupdate_epoch = epoch
+        else:
+            lr = lr*10
     #
     # lr = lr * (0.1 ** (epoch // decrease_epoch))
     # if lr >= 1.0e-6:
     #     for param_group in optimizer.param_groups:
     #         param_group['lr'] = lr
 
-    return lr
+    return lr, lastupdate_epoch
 
 
 def save_output_images(predictions, filenames, output_dir):
@@ -243,10 +247,10 @@ class Model_Factory_LSTM():
         elif cf.optimizer == 'sgd':
             self.optimiser = optim.SGD(self.net.parameters(), lr=cf.learning_rate, momentum=cf.momentum, weight_decay=cf.weight_decay, nesterov=True)
 
-    def train(self, cf, train_loader, epoch, train_losses):
+    def train(self, cf, train_loader, epoch, lastupdate_epoch, train_losses):
         # begin to train
         self.net.train()
-        lr = adjust_learning_rate(self.cf.learning_rate, self.optimiser, epoch,train_losses , decrease_epoch=cf.lr_decay_epoch)
[…]

### 2017-11-14 code_base/tools/PyTorch_model_training.py

@@ -118,16 +118,16 @@ def get_img_list(train_data, valid_data, test_data):
 def get_img_resized_list(cf, train_data, valid_data, test_data):
 
     root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
-    def data_img_dir(data):
-        return root_dir + '/' + data[0][0][6].split('/')[
-            0] + '/' + 'GT/LABELS' + '/' + cf.data_stereo + '/' + cf.data_camera
+    # def data_img_dir(data):
+    #     return root_dir + '/' + data[0][0][6].split('/')[
+    #         0] + '/' + 'GT/LABELS' + '/' + cf.data_stereo + '/' + cf.data_camera
+    #
+    # train_img_dir = data_img_dir(train_data)
+    # valid_img_dir = data_img_dir(valid_data)
+    # test_img_dir = data_img_dir(test_data)
 
-    train_img_dir = data_img_dir(train_data)
-    valid_img_dir = data_img_dir(valid_data)
-    test_img_dir = data_img_dir(test_data)
-
-    def img_name(img_dir, item):
-        return os.path.join(img_dir, item.split('/')[1])
+    def img_name(item):
+        return os.path.join(root_dir + '/' + item.split('/')[0] + '/' + 'GT/LABELS' + '/' + cf.data_stereo + '/' + cf.data_camera, item.split('/')[1])
 
     def semantic_image(img_name):
         try:
@@ -161,7 +161,7 @@ def get_img_resized_list(cf, train_data, valid_data, test_data):
     for d in valid_data:
         i += 1
         item_list = [x[6] for x in d[:cf.lstm_input_frame]]
-        item_list = [semantic_image(img_name(valid_img_dir, item)) for item in item_list]
+        item_list = [semantic_image(img_name(item)) for item in item_list]
         item_list = torch.stack(item_list, dim=0)
         valid_img_list.append(save_semantics_itemlist('valid_'+str(i), item_list))
 
@@ -170,7 +170,7 @@ def get_img_resized_list(cf, train_data, valid_data, test_data):
     for d in test_data:
         i += 1
         item_list = [x[6] for x in d[:cf.lstm_input_frame]]
-        item_list = [semantic_image(img_name(test_img_dir, item)) for item in item_list]
+        item_list = [semantic_image(img_name(item)) for item in item_list]
         item_list = torch.stack(item_list, dim=0)
[…]

### 2017-11-14 paper/cvpr2018/cvpr2018_draft.tex
paper writing: object detection. Next: tracking

@@
 \usepackage{bm}
-%\usepackage{subcaption}
+\usepackage{subcaption}
 %\usepackage{slashbox}
@@
 
-%%% TY: write related work for object detection, segmentation, instance segmentation
 \textbf{\emph{1. Object detection, segmentation, instance segmentation}}
 
-TODO: TY
-%%% DW: write related work for visual tracking
-%%% DW: write related dataset for autonoumous driving
 Object detection is an important component in our system.
@@
 
-TODO: DW
+Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.
+~\cite{behl2017bounding} estimate the 3D scene flow by exploiting recognition to overcome the challenging scenarios in the present of large displacement or local ambiguities.
+Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
+However, a total runtime of 10 minutes per frame is way to prohibitive for the deployment in the context of autonomous driving.
 
@@
 
-TODO: cite below papers;
-
-~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.
-
-~\cite{behl2017bounding} Bounding Boxes, Segmentations and Object Coordinates: How Important is Recognition for 3D Scene Flow Estimation in Autonomous Driving Scenarios?
-
-~\cite{chen2015deepdriving} DeepDriving: Learning Affordance for Direct Perception
-
-~\cite{kim2017interpretable} Interpretable Learning for Self-driving cars
-
 \section{Proposed Algorithm}
@@
 Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
-The train/valid/test are split as 80\%/10\%/10\% of the total tracklets.
+The train/valid/test are split as 80\%/10\%/10\% of the total tracklets and the total numbers are shown in Tab.~\ref{tab:dataset_statistics}.
 We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
-Some sample frames with semantic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
+Some sample frames with semantic labels and depth information is shown in Fig.~\ref{fig:dataset}.
 
-TODO: generate a table for total number of frames and sequence tracklets!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/dataset.pdf}
+        \caption{ {\small Examples of collected dataset for car trajectory prediction.
+From top to bottom: RGB, semantic labeling, depth maps for three continuous frames of two dynamic light conditions.}}
+        \label{fig:dataset}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}\centering
+\ra{1.}
+\begin{tabular}{@{}llll@{}}\toprule
+
+                & \#train & \#valid & \#test\\
+ \hline
+ tracklets      &  10400    &  1300    & 1280 \\
+ \hline
+ car detection  &   7832     & 976     & 986 \\
+ \hline
+ semantic segmentation  &  7841  & 977  & 987 \\
+ \hline
+\end{tabular}
+\caption{Dataset statistics}
+\label{tab:dataset_statistics}
+\end{table}
 \subsection{Implementations}\label{sec:Implementations}
@@
 
-We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
+To reliably detect traffic participants, we compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN ~\cite{ren2015faster_nips}.
 We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
@@
 As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
-In this paper, we concerns mostly about cars that are closer to the driver.
-Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection.
-Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.
+In this paper, we concerns mostly about cars that are close to the driver.
+Hence, given 0.1\% POR as the the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
+Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when objects of interest are large in our problem set.
+We also compare the influence of confident score cut-off threshold and non-maximum suppression (NMS) threshold.
+It can been seen that both meta-architectures are robust to the cut-off confident scores.
+In terms of the effect of NMS cut-off threshold, allowing larger threshold enables the detector to have slightly higher recall, it comes at a cost of multiple redundant overlapping detections and much lower f-score overall.
+In the following experiment, we adopt SSD with confident score of 0.5 as the cut-off threshold and 0.45 as the default jaccard overlap for NMS.
 
@@
 \hline
-\multirow{3}{*}{SSD}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
-                    &    recall   & \textbf{92.3}  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
-                    &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
 \multirow{3}{*}{Faster-RCNN}
@@
                     &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+                    \cline{2-12}
+\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
+                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
+                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
+                    \cline{2-12}
+\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+
 \bottomrule
@@
 
-We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
+However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
+In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
+Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
+For this task, we adopt the real-time scale adaptive tracker fDSST~\cite{danelljan2017discriminative}.
+
 \begin{figure}[t]
@@
 We compare two temporal models based on LSTM cells for predicting the car trajectory.
+
+TODO: compare the results using Kalman filtering.
 
@@
 
+\begin{figure*}[t]
+   \centering
+    \begin{subfigure}[c]{0.4\textwidth}
+    \centering
+    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot.png}
+    \caption{\small{Precision plot for 2D}}
+    \end{subfigure}%
+    \begin{subfigure}[c]{0.4\textwidth}
+    \centering
+        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot.png}
+        \caption{\small{Success plot 2D}}
+    \end{subfigure}
+    \\
+     \begin{subfigure}[c]{0.4\textwidth}
+     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot.png}
+    \caption{\small{Precision plot for 2D}}
+    \end{subfigure}%
+    \begin{subfigure}[c]{0.4\textwidth}
+    \centering
+        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot.png}
+        \caption{\small{Success plot 2D}}
+    \end{subfigure}
+\caption{Precision plot and success plot of the state-of-the-art, 2D, and 3D(TODO).
+}
+\label{fig:precision_plot_and_success_plot_OBT100}
+\end{figure*}
+
 \section{Conclusions}

### 2017-11-14 code_base/test_synthia.py

@@ -1,8 +1,0 @@
-from code_base.SSD_synthia_car_detection_fine_tune import calculate_iou
-
-
-test_gt_file = '/home/public/synthia/ssd_car_fine_tune/ssd_car_test_gt.pkl'
-test_json_file = '/home/public/synthia/ssd_car_test_faster.json'
-
-
-calculate_iou(test_gt_file, test_json_file, POR=1e-3)

### 2017-11-14 code_base/draw_tracking_success_precision_graph.py
Tracking plot update

@@ -1,0 +1,89 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+thresholdSetOverlap = [x/float(20) for x in range(21)]
+thresholdSetError = range(0, 51)
+LINE_COLORS = ['b','g','r','c','m','y','k', '#880015', '#FF7F27', '#00A2E8', '#880015', '#FF7F27', '#00A2E8']
+
+
+def main():
+    valid_dict = np.load(r'C:\Users\steve\Desktop\Figures\tracking_plot\valid.npy')
+    test_dict = np.load(r'C:\Users\steve\Desktop\Figures\tracking_plot\test.npy')
+
+    v_dict = valid_dict.item()
+    t_dict = test_dict.item()
+
+    v_errCenter = np.vstack(v_dict['errCoverage'])
+    v_iou_2d =np.vstack(v_dict['iou_2d'])
+    v_errCenter_realworld = v_dict['errCenter_realworld']
+    ################################################################
+    successRateList = []
+    length = v_iou_2d.shape[1]
+    for threshold in thresholdSetOverlap:
+        seqSuccessList = []
+        for seq_iou_2d in v_iou_2d:
+            seqSuccess = [score for score in seq_iou_2d if score > threshold]
+            seqSuccessList.append(len(seqSuccess)/float(length))
+        successRateList.append(seqSuccessList)
+
+    successRateList_plot = [np.mean(x) for x in successRateList]
+    ################################################################
+    precisionRateList = []
+    for threshold in thresholdSetError:
+        seqPrecisionRateList = []
+        for seq_errCenter in v_errCenter:
+            seqPrecisions = [score for score in seq_errCenter if score < threshold]
+            seqPrecisionRateList.append(len(seqPrecisions)/float(length))
+        precisionRateList.append(seqPrecisionRateList)
+    precisionRateList_plot = [np.mean(x) for x in precisionRateList]
+
+
+    plot_graph_success(successRateList_plot, name='GT_detector')
+    plot_graph_precision(precisionRateList_plot, name='GT_detector')
+    plt.show()
+
+
+def plot_graph_success(successRateList_plot, name='GT_detector'):
+    plt.figure(num=0, figsize=(9, 6), dpi=70)
+    figManager = plt.get_current_fig_manager()
+    figManager.window.showMaximized()
[…]

### 2017-11-14 code_base/test.py
test synthia

@@ -1,0 +1,17 @@
+import os
+from skimage import io
+path = '/home/stevenwudi/PycharmProjects/autonomous_driving/Datasets/segmentation/SYNTHIA_RAND_CVPR16/RGB'
+imgs = os.listdir(path)
+errors = ['ap_000_02-11-2015_18-02-19_000062_3_Rand_2.png',
+                'ap_000_02-11-2015_18-02-19_000129_2_Rand_16.png',
+                'ap_000_01-11-2015_19-20-57_000008_1_Rand_0.png']
+
+for name in imgs:
+    # n, s = os.path.splitext(name)
+    if name in ['ap_000_02-11-2015_18-02-19_000062_3_Rand_2.png',
+                'ap_000_02-11-2015_18-02-19_000129_2_Rand_16.png',
+                'ap_000_01-11-2015_19-20-57_000008_1_Rand_0.png']:
+        continue
+    else:
+        print (name)
+        tmp = io.imread(path + '/' + name)

### 2017-11-14 code_base/test_synthia.py

@@ -1,8 +1,19 @@
-from code_base.SSD_synthia_car_detection_fine_tune import calculate_iou
+from code_base.SSD_synthia_car_detection_fine_tune import calculate_iou, test_ssd512, gt_classification_convert
+import pickle
+import json
+test_gt_file = '/home/public/synthia/ssd_car_fine_tune/ssd_car_test_gt-shuffle.pkl'
+test_json_file = '/home/public/synthia/ssd_car_test_faster-shuffle.json'
 
 
-test_gt_file = '/home/public/synthia/ssd_car_fine_tune/ssd_car_test_gt.pkl'
-test_json_file = '/home/public/synthia/ssd_car_test_faster.json'
-
-
-calculate_iou(test_gt_file, test_json_file, POR=1e-3)
+calculate_iou(test_gt_file, test_json_file, POR=2e-3, draw=False)
+# test_gt_file = '/home/public/synthia/ssd_car_fine_tune/ssd_car_test_gt-shuffle.pkl'
+# test_json_file = '/home/public/synthia/ssd_car_fine_tune/ssd_car_test-shuffle.json'
+# gt = pickle.load(open(test_gt_file, 'rb'))
+# gt = gt_classification_convert(gt)
+# keys = sorted(gt.keys())
+# with open(test_json_file, 'r') as fp:
+#     predict_dict = json.load(fp)
+# a = sorted(predict_dict.keys())
+#
+# for key in a:
+#     print (key)

### 2017-11-14 code_base/models/PyTorch_model_factory.py
adjust learning rate

@@ -23,16 +23,16 @@ def adjust_learning_rate(lr, optimizer, epoch, lastupdate_epoch, train_losses, d
     """Sets the learning rate to the initial LR decayed by 10 every 30 epochs"""
 
     if epoch-lastupdate_epoch < 10:
-        return optimizer.param_groups[-1]['lr']
+        return optimizer.param_groups[-1]['lr'], lastupdate_epoch
 
     eva_losses = np.array(train_losses[-10:])
 
     max_value = eva_losses.max()
     min_value = eva_losses.min()
-    max_loction = eva_losses.argmax()
-    min_location = eva_losses.argmin()
+    # max_loction = eva_losses.argmax()
+    # min_location = eva_losses.argmin()
 
-    if np.abs(max_value-min_value)/max_value < 1e-4 or max_loction>min_location:
+    if np.abs(max_value-min_value)/max_value < 1e-4:
         lr = optimizer.param_groups[-1]['lr']
         lr = lr * 0.1
 

### 2017-11-14 code_base/tools/PyTorch_model_training.py

@@ -202,9 +202,9 @@ def prepare_data_image_list(cf):
         train_data_array, valid_data_array, test_data_array, data_mean, data_std = normalise_data_with_img_list(train_data,
                                                                                                                 valid_data,
                                                                                                                 test_data)
-        train_img_list, valid_img_list, test_img_list = get_img_resized_list(cf, train_data[:100,:,:], valid_data[:40,:,:], test_data[:40,:,:])
+        train_img_list, valid_img_list, test_img_list = get_img_resized_list(cf, train_data, valid_data, test_data)
 
-        prepared_data = (train_data_array[:100,:,:], valid_data_array[:40,:,:], test_data_array[:40,:,:], data_mean, data_std, train_img_list, valid_img_list, test_img_list)
+        prepared_data = (train_data_array, valid_data_array, test_data_array, data_mean, data_std, train_img_list, valid_img_list, test_img_list)
 
         if cf.dataloader_save_prepare_data:
             # save data

### 2017-11-14 code_base/models/PyTorch_model_factory.py
save valid & test IOU plot

@@ -382,8 +382,8 @@ class Model_Factory_LSTM():
 
             model_checkpoint = 'Epoch:%2d_net_Coverage:%.4f_Center:%.2f_CoverageR:%.4f_CenterR:%.2f.PTH' % \
                                (epoch, aveErrCoverage, aveErrCenter, aveErrCoverage_realworld, aveErrCenter_realworld)
-            np.save('/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/tracking_plot/' + 'valid', track_plot)
-
+            if epoch == cf.n_epochs:
+                np.save(os.path.join(self.exp_dir, 'valid'), track_plot)
 
         else:
             print('############### TEST #############################################')
@@ -393,7 +393,7 @@ class Model_Factory_LSTM():
             aveErrCoverage_realworld, aveErrCenter_realworld))
             model_checkpoint = 'Final_test:Coverage:%.4f_Center:%.2f_CoverageR:%.4f_CenterR:%.2f.PTH' % \
                                (aveErrCoverage, aveErrCenter, aveErrCoverage_realworld, aveErrCenter_realworld)
-            np.save('/media/samsumg_1tb/synthia/SYNTHIA-SEQS-01/tracking_plot/' + 'test', track_plot)
+            np.save(os.path.join(self.exp_dir, 'test'), track_plot)
 
             # Plot scores
             # self.aveErrCoverage.append(aveErrCoverage.mean())

### 2017-11-14 code_base/Synthia_car_trajectory.py
for experiment

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '0'
+os.environ['CUDA_VISIBLE_DEVICES'] = '2'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time
@@ -30,6 +30,9 @@ def process(cf):
 
     print('\n > Building model...')
     model = Model_Factory_LSTM(cf)
+
+    # # for experimentt
+    # model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, 63)
 
     if cf.train_model:
         train_losses = []

### 2017-11-14 code_base/config/synthia_car_trajectory.py

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
+model_name                   = 'CNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -104,7 +104,7 @@ focal_length                 = 532.740352  # camera focal lense
 
 # Training parameters
 lr_decay_epoch               = 10          # every lr_decay_epoch, decay learning_rate by 10
-figure_epoch                 = 5           # every fugure_epoch, figure out the losses
+figure_epoch                 = 10           # every fugure_epoch, figure out the losses
 test_epoch                   = 1
 weight_decay                 = 0.              # Weight decay or L2 parameter norm penalty
 n_epochs                     = 200            # Number of epochs during training
@@ -114,7 +114,7 @@ optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = False
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Mon, 13 Nov 2017-11-13 11:27:35_CNN_LSTM_To_FC/Epoch: 5_net_Coverage:0.0859_Center:231.26_CoverageR:0.0423_CenterR:1.22.PTH'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Tue, 14 Nov 2017-11-14 17:47:21_LSTM_To_FC_Noshuffle_Nosemantics-TrainBatch4/Epoch:63_net_Coverage:0.6020_Center:35.22_CoverageR:0.2917_CenterR:0.79.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
[…]

### 2017-11-14 paper/cvpr2018/cvpr2018_draft.tex
introduction revision

@@
 \begin{document}
-\title{DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving}
+\title{DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving}
 
@@
 Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
-Then, a novel DRN-LSTM network is incorporated to fuse the multiple-streams from past frames to predict targets' future trajectories.
-We demonstrate the feasibility of predicting future trajectories of cars for assisting mediated perception.
- We also show the effectiveness of using privileged information (e.g., scene semantics and car pose information) further boost the prediction accuracy across diverse traffic conditions.
+Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
+We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
+ We also show the effectiveness of using privileged information (e.g., scene semantics) further boost the prediction accuracy across diverse traffic conditions.
 \end{abstract}
@@
 
-\textbf{\emph{1. What is the problem?}}
+%\textbf{\emph{1.1 What is the problem?}}
 
-Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and than parse the scene to make a driving policy (usually by a controller with if-then-else rules), and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
+Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and then parse the scene to make a driving policy (usually by a controller with if-then-else rules); and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
+In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of vehicles given its past information.
 
-In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of cars given its past information.
+%\textbf{\emph{1.2. Why is it interesting and important?}}
 
-\textbf{\emph{2. Why is it interesting and important?}}
+ Being able to predict other traffic participants' future trajectories is important because it can help to prevent self-driving car from running into other cars.
+We need to know not just where other cars are, as in the localization case, but also how fast they are moving in order to avoid collisions.
+For a human driver, reaction time is a crucial factor that includes recognizing the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake).
+Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
+Therefore, the ability to predict traffic participants' \emph{future} trajectories will greatly benefits the mediated perception approach's driving policy decision making.
 
-Driver reaction time is a crucial factor for a human driver to react to the traffic participants.
-Driver reaction time includes recognising the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake).
-Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
-Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.
+%\textbf{\emph{1.3. Why is it hard? (Or why do naive approaches fail?)}}
+
+Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
+In addition, scene parsing results contain quite some spurious information. 
+Existing methods for scene parsing also mainly focus on static images. 
+However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by sequence of input frames instead of simply one static frame.
+Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.
 
@@
 \end{figure}
-\textbf{\emph{3. Why is it hard? (E.g., why do naive approaches fail?)}}
 
-Individually, for computer vision community, it's an unsolved problem. e.g.: object detection, semantic segmentation, instance segmentation, etc.
+%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
+Vehicles trajectory prediction is also very related to visual tracking.
+In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
+However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks).
+Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
+Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.
 
-Currently, most work focus on static images. However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by sequence of input frames instead of simply one static frame.
-
-\textbf{\emph{4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
-
-Scene parsing results contains quite some spurious information.
-
-In traditional vision based tracking problems (\emph{e.g.} ~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement of the target in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
-However, traffic participants generally exhibit regular trajectories (e.g., cars driving on the road and pedestrian walking on the sidewalks).
-
-Currently research community lacks proper evaluation metrics for deciding the temporally future prediction result.
-
-\textbf{\emph{5. What are the key components of my approach and results? Also include any specific limitations.}}
-
-In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction.
+%\textbf{\emph{1.5. What are the key components of my approach and results? Also include any specific limitations.}}
 
@@
 This material doubles as an outline of the rest of the paper, saving space and eliminating redundancy.
+In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction as shown in Fig.~\ref{fig:pull_figure}.Our contributions are as follows:
 
-Our contributions are as follows:
 \begin{itemize}
 
-\item We verify the feasibility of predicting the future trajectories of cars for assisting mediated perception framework.
+\item We verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception.
 The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
 
-\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving for robustly vehicle tracking.
-The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.
+\item We present a novel ``tracking-by-detection" framework for robust vehicle tracking.
+By updating tracker's target representation via detection association, we also solve the problem of instance association between frames.
 
-\item We design various temporal models for the problem of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.
+\item We design various temporal models for the problem of predicting future trajectories based on historical data.
+Results show that the temporal model generating intermediate represenation performs better than the frame-to-frame based temporal model.
 
-\item We demonstrate the effectiveness of using ``privileged information"(e.g., scene semantics and car pose information) further boost the prediction accuracy. [NOT DONE YET].
+\item We demonstrate the effectiveness of using ``privileged information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.
 
-\item We formalise the car trajectory problem into a 3D occupancy grid problem given depth information.
-
-\item We construct a time-series dataset for car trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia}.
+\item We construct a time-series dataset for car trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
 
@@
 We compare two temporal models based on LSTM cells for predicting the car trajectory.
+Results show that the temporal model generating intermediate output utilizing the whole historical data performs better than the frame-to-frame based output temporal model.
 
@@
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/dataset.pdf}
+        \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
         \caption{ {\small Examples of collected dataset for car trajectory prediction.
@@
 
+\subsubsection{Baselines}
+The Kalman filter is a popular technique for estimating the state of a system.
+Kalman filters estimate a continuous state and gives a uni-modal distribution.
+The Kalman filter represents all distributions of the Gaussians and iterates two things: (1) measurement updates; (2) motion updates
+
 \begin{figure*}[t]
@@
 
-Future works include conducting experiment on the real-world images.
+Future works include incorporating vehicle pose from the RGB input as extra source of ``privileged information"; conducting experiment on the real-world images.
 

### 2017-11-14 paper/cvpr2018/cvpr2018_draft.tex
Paper writing: related works update

@@
 \usepackage{booktabs}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage{algorithm}
@@
 \item We design various temporal models for the problem of predicting future trajectories based on historical data.
-Results show that the temporal model generating intermediate represenation performs better than the frame-to-frame based temporal model.
+Results show that the temporal model generating intermediate representation performs better than the frame-to-frame based temporal model.
 
@@
 
-\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
-
-Object detection is an important component in our system.
-Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
-However, after the proposal of R-CNN \cite{girshick2014rich}, which combines Selective Search and deep learning features to detect objects, the architecture of CNN has attracted more attention.
-At the beginning, R-CNN is a step-by-step and inefficient method.
-Then, SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features and Fast R-CNN \cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network.
-At last, Faster R-CNN \cite{Ren2015Faster} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture.
+%\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
+%\subsection{Traffic participants detection and tracking: object detection and instance association}
+\subsection{Object detection}
+Vehicle detection is one key component of an autonomous driving system. Typical algorithms output bounding boxes on detected vehicles.
+A lot of progess has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
+Modern object detectors based on these networks -- such as the line of works on the R-CNN~\cite{girshick2014rich},
+Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
+% Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
+% However, after the proposal of 
+ R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
+ % At the beginning, R-CNN is a step-by-step and inefficient method. Then, 
+  SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features.
+Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network.
+At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture.
 Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class.
@@
 
-At the field of semantic segmentation, many methods with CNN also bring a dramatic improvement.
-FCN \cite{long2015fully} firstly transfers the fully-connected layers into convolution layers, which turns segmentation task into pixel-wise classification task.
-Deeplab \cite{chen2016deeplab} considers the limitation of receptive field of CNN, and then proposes a dilated convolution layer to solve this problem.
-DRN \cite{yu2017dilated} further proposes a semantic network by integrating residual structure and dilated convolution.
-With the modification of neural network, conditional random field (CRF) is employed into refining the output of network in \cite{chen2016deeplab}.
+%In the field of semantic segmentation, FCN~\cite{long2015fully} firstly transfers the fully-connected layers into convolution layers, turning the segmentation task into a pixel-wise classification task.
+Deeplab~\cite{chen2016deeplab} proposes a dilated convolution layer to explicitly control the resolution at
+%which feature responses are computed within Deep Convolutional Neural Networks. DRN~\cite{yu2017dilated} further proposes a semantic network by integrating residual structure and dilated convolution.
+
+%With the modification of neural network, conditional random field (CRF) is employed into refining the output of network in \cite{chen2016deeplab}.
 After that, CRF is merged into neural network to become an end-to-end architecture \cite{liu2015semantic,zheng2015conditional,arnab2016higher}
 
-\textbf{\emph{2. Visual trackers}}
-
+\subsection{Instance association}
 Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.
-~\cite{behl2017bounding} estimate the 3D scene flow by exploiting recognition to overcome the challenging scenarios in the present of large displacement or local ambiguities.
-Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
-However, a total runtime of 10 minutes per frame is way to prohibitive for the deployment in the context of autonomous driving.
-
-%% DW: (1)traditional segmentic segmentation dataset
-%% DW: (2) synthetic dataset
-%% DW: (3) temporal consistent dataset
+3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the present of large displacement or local ambiguities.
+%Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark. 
+However, a total runtime of 10 minutes per frame is way too prohibitive for the deployment in the context of autonomous driving.
+To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking. 
+Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
+Built upon their seminal work, there has been a plethora of recent improvements~\cite{wang2016stct, wang2015visual, hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.
 
@@
 
-\textbf{\emph{3. Dataset for autonoumous driving}}
+\subsection{Recurrent neural networks}
 
-Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK.
+Recent advances in recurrent neural network for modeling visual sequential data are also related to our work.
+%Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
+Mostly, RNN is trained as a pilot network in the context of behaviour reflex approaches.
+Long Short Term Memory (LSTM) cells are usually exploited as one intermediate component of an end-to-end driving model.
+ A combination of a fully-convolutional network and an LSTM is proposed in~\cite{xu2017end} to learn from large-scale vehicle action data.
+Their goal is to predict future egomotion including multi-modal discrete and continuous driving behaviors.
+ Inverse turning radius is predicted by a LSTM network in~\cite{kim2017interpretable}: they generate a heat map of attention at each time step conditioned on the previous hidden states and a current convolutional feature cube  to produce more succinct visual explanations.
+~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
+In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
+
+\subsection{Dataset for autonomous driving}
+
+Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
+%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK.
 However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
-
-Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
-
+%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
 KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks.
 However, a limited 430 labelled images are provided for semantic segmentation.
-
-A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city.
+%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city.
 The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
-
 More recently, larger project are constructed:
 Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes.
-
+Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving.
+Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
 The use of synthetic data has increased considerably in recent years within computer vision community.
-~\cite{mueller2016benchmark} provides a synthetic dataset generation and online tracker evaluation.
-In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
+A synthetic dataset named Synthia is\cite{mueller2016benchmark} provide originally for urban scene semantic segmentation generation.
+%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
 Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
-
-A fine annotated images in Cityscape dataset requires on average 1.5 hours which is very labor intensive.
+Synthetic dataset has an obvious advantage: a fine annotated images in Cityscape dataset requires on average 1.5 hours which is very labor intensive.
 Thus, the cost of scaling large project would required a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
-For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
-This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.
-
-%%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
-
-\textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}
-
-Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
-Most of these works exploit LSTM as component of an end-to-end driving model.
-~\cite{xu2017end} used the combination of a fully-convolutional network and an LSTM to learn from large-scale vehicle action data, to predict future egomotion including multi-modal discrete and continuous driving behaviors.
-~\cite{kim2017interpretable} used a LSTM network to predict the inverse turning radius and generate a heat map of attention at each timestep conditioned on the previous hidden states and a current convolutional feature cube.
-~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
-In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
+%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
+%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.
 
@@
 \section*{Details of the Code}
- The code will be made public alongside the publication.
+ The code will be made public upon publication.
 

### 2017-11-15 code_base/Synthia_car_trajectory.py
add dropoutmodel

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '2'
+os.environ['CUDA_VISIBLE_DEVICES'] = '1'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-15 code_base/models/PyTorch_PredictModels.py

@@ -276,3 +276,118 @@ class CNN_LSTM_To_FC(nn.Module):
         outputs.append(output_linear2)
 
         return outputs
+
+
+class DropoutCNN_LSTM_To_FC(nn.Module):
+    """
+    This model use an LSTM to fuse features of all past frames into a single state, which inputs to a following Fully Connected model to predict next some frames' features.
+    The lstm model can be seen as a encoder, while the FC model as a decoder.
+    """
+
+    def __init__(self, conv_paras, input_dims, hidden_sizes, future_frame, output_dim, cuda=True):
+        '''
+        :param convs: a list composed of dicts representing parameters of each conv, {'in_channels': ,
+                                                                                      'out_channels': ,
+                                                                                      'kernel_size': ,
+                                                                                      'stride': ,
+                                                                                      'padding': }
+        :param input_dims: a list involving each lstm_layer's input_dim
+        :param hidden_sizes: a list involving each lstm_layer's hidden_size
+        :param future_frame: the number of predicting frames
+        :param output_dim: the number of features in each predicting frame
+        :param cuda: whether or not to use GPU
+        '''
+        super(DropoutCNN_LSTM_To_FC, self).__init__()
+        # cnn part
+        self.convparas = conv_paras
+        self.conv = nn.Sequential(nn.Conv2d(**self.convparas[0]),
+                                  nn.ReLU(),
+                                  nn.Dropout2d(p=0.5),
+                                  nn.MaxPool2d(2),
+                                  nn.Conv2d(**self.convparas[1]),
+                                  nn.ReLU(),
+                                  nn.Dropout2d(p=0.5),
+                                  nn.MaxPool2d(2),
+                                  nn.Conv2d(**self.convparas[2]),
+                                  nn.ReLU(),
+                                  nn.Dropout2d(p=0.5),
+                                  nn.MaxPool2d(2),
+                                  nn.Conv2d(**self.convparas[3]),
+                                  nn.ReLU(),
+                                  nn.Dropout2d(p=0.5),
+                                  nn.MaxPool2d(2)
+                                  )
+
+        # lstm part; build lstm layer, parameters are (input_dim,hidden_size,num_layers)
+        self.input_dims = input_dims
+        self.hidden_sizes = hidden_sizes
[…]

### 2017-11-15 code_base/models/PyTorch_model_factory.py

@@ -22,7 +22,7 @@ import json
 def adjust_learning_rate(lr, optimizer, epoch, lastupdate_epoch, train_losses, decrease_epoch=10):
     """Sets the learning rate to the initial LR decayed by 10 every 30 epochs"""
 
-    if epoch-lastupdate_epoch < 10:
+    if epoch - lastupdate_epoch < 10:
         return optimizer.param_groups[-1]['lr'], lastupdate_epoch
 
     eva_losses = np.array(train_losses[-10:])
@@ -32,7 +32,7 @@ def adjust_learning_rate(lr, optimizer, epoch, lastupdate_epoch, train_losses, d
     # max_loction = eva_losses.argmax()
     # min_location = eva_losses.argmin()
 
-    if np.abs(max_value-min_value)/max_value < 1e-4:
+    if np.abs(max_value - min_value) / max_value < 1e-3:
         lr = optimizer.param_groups[-1]['lr']
         lr = lr * 0.1
 
@@ -41,7 +41,7 @@ def adjust_learning_rate(lr, optimizer, epoch, lastupdate_epoch, train_losses, d
                 param_group['lr'] = lr
             lastupdate_epoch = epoch
         else:
-            lr = lr*10
+            lr = lr * 10
     #
     # lr = lr * (0.1 ** (epoch // decrease_epoch))
     # if lr >= 1.0e-6:
@@ -74,7 +74,8 @@ def save_output_images(predictions, filenames, output_dir):
 class Model_Factory_semantic_seg():
     def __init__(self, cf):
         # If we load from a pretrained model
-        self.exp_dir = cf.savepath + '___' + datetime.now().strftime('%a, %d %b %Y-%m-%d %H:%M:%S') + '_' + cf.model_name
+        self.exp_dir = cf.savepath + '___' + datetime.now().strftime(
+            '%a, %d %b %Y-%m-%d %H:%M:%S') + '_' + cf.model_name
         os.mkdir(self.exp_dir)
         # Enable log file
         self.log_file = os.path.join(self.exp_dir, "logfile.log")
@@ -94,13 +95,11 @@ class Model_Factory_semantic_seg():
             self.net = DRNSeg('drn_d_38', cf.num_classes, pretrained=True, linear_up=False)
         # Set the loss criterion
         if cf.cb_weights_method == 'rare_freq_cost':
-            print('Use ' +cf.cb_weights_method+', loss weight method!')
[…]

### 2017-11-15 code_base/Synthia_car_trajectory.py
add dropoutAfterMaxpooling config

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '1'
+os.environ['CUDA_VISIBLE_DEVICES'] = '3'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time

### 2017-11-15 code_base/config/synthia_car_trajectory.py

@@ -136,6 +136,7 @@ cnnLstmToFc_conv_paras        = [cnnDict(2,4,3,1,1), cnnDict(4,4,3,1,1),cnnDict(
                                                                                       # 'kernel_size': ,
                                                                                       # 'stride': ,
                                                                                       # 'padding': }
+dropoutAfterMaxpooling        = True
 cnnLstmToFc_input_dims        = [6, 300, 300]              # a list involving each lstm_layer's input_dim
 cnnLstmToFc_hidden_sizes      = [100, 300, 300]              # a list involving each lstm_layer's hidden_size
 cnnLstmToFc_future            = lstm_predict_frame # the number of predicting frames

### 2017-11-15 code_base/models/PyTorch_PredictModels.py

@@ -284,7 +284,7 @@ class DropoutCNN_LSTM_To_FC(nn.Module):
     The lstm model can be seen as a encoder, while the FC model as a decoder.
     """
 
-    def __init__(self, conv_paras, input_dims, hidden_sizes, future_frame, output_dim, cuda=True):
+    def __init__(self, cf, conv_paras, input_dims, hidden_sizes, future_frame, output_dim, cuda=True):
         '''
         :param convs: a list composed of dicts representing parameters of each conv, {'in_channels': ,
                                                                                       'out_channels': ,
@@ -300,23 +300,42 @@ class DropoutCNN_LSTM_To_FC(nn.Module):
         super(DropoutCNN_LSTM_To_FC, self).__init__()
         # cnn part
         self.convparas = conv_paras
-        self.conv = nn.Sequential(nn.Conv2d(**self.convparas[0]),
-                                  nn.ReLU(),
-                                  nn.Dropout2d(p=0.5),
-                                  nn.MaxPool2d(2),
-                                  nn.Conv2d(**self.convparas[1]),
-                                  nn.ReLU(),
-                                  nn.Dropout2d(p=0.5),
-                                  nn.MaxPool2d(2),
-                                  nn.Conv2d(**self.convparas[2]),
-                                  nn.ReLU(),
-                                  nn.Dropout2d(p=0.5),
-                                  nn.MaxPool2d(2),
-                                  nn.Conv2d(**self.convparas[3]),
-                                  nn.ReLU(),
-                                  nn.Dropout2d(p=0.5),
-                                  nn.MaxPool2d(2)
-                                  )
+        if cf.dropoutAfterMaxpooling == False:
+            self.conv = nn.Sequential(nn.Conv2d(**self.convparas[0]),
+                                      nn.ReLU(),
+                                      nn.Dropout2d(p=0.5),
+                                      nn.MaxPool2d(2),
+                                      nn.Conv2d(**self.convparas[1]),
+                                      nn.ReLU(),
+                                      nn.Dropout2d(p=0.5),
+                                      nn.MaxPool2d(2),
+                                      nn.Conv2d(**self.convparas[2]),
+                                      nn.ReLU(),
+                                      nn.Dropout2d(p=0.5),
+                                      nn.MaxPool2d(2),
+                                      nn.Conv2d(**self.convparas[3]),
+                                      nn.ReLU(),
+                                      nn.Dropout2d(p=0.5),
+                                      nn.MaxPool2d(2)
+                                      )
+        else:
[…]

### 2017-11-15 code_base/models/PyTorch_model_factory.py

@@ -211,7 +211,8 @@ class Model_Factory_LSTM():
                                       output_dim=cf.cnnLstmToFc_output_dim,
                                       cuda=cf.cuda)
         elif cf.model_name == 'DropoutCNN_LSTM_To_FC':
-            self.net = DropoutCNN_LSTM_To_FC(conv_paras=cf.cnnLstmToFc_conv_paras,
+            self.net = DropoutCNN_LSTM_To_FC(cf=cf,
+                                             conv_paras=cf.cnnLstmToFc_conv_paras,
                                              input_dims=cf.cnnLstmToFc_input_dims,
                                              hidden_sizes=cf.cnnLstmToFc_hidden_sizes,
                                              future_frame=cf.cnnLstmToFc_future,

### 2017-11-15 code_base/config/synthia_car_trajectory.py
robust dataloader for manytomany model

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'DropoutCNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
+model_name                   = 'LSTM_ManyToMany'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None

### 2017-11-15 code_base/tools/PyTorch_data_generator.py

@@ -235,9 +235,9 @@ class DataGenerator_Synthia_car_trajectory():
             self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
 
             print('\n > Loading training, valid, test set')
-            train_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, train_data, train_img_list, crop=False, flip=False)
-            valid_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, valid_data, valid_img_list,  crop=False, flip=False)
-            test_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, test_data, test_img_list, crop=False, flip=False)
+            train_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, True, train_data, train_img_list, crop=False, flip=False)
+            valid_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, False, valid_data, valid_img_list,  crop=False, flip=False)
+            test_dataset = Resized_BB_ImageDataGenerator_Synthia(cf, False, test_data, test_img_list, crop=False, flip=False)
 
             self.train_loader = DataLoader(train_dataset, batch_size=cf.batch_size_train, shuffle=True,
                                            num_workers=cf.workers, pin_memory=True)
@@ -327,7 +327,7 @@ class BB_ImageDataGenerator_Synthia(Dataset):
 
 # resized semantic image
 class Resized_BB_ImageDataGenerator_Synthia(Dataset):
-    def __init__(self, cf, trajectory_data, img_list, crop=True, flip=True):
+    def __init__(self, cf, trainornot, trajectory_data, img_list, crop=True, flip=True):
         """
         :param root_dir: Directory will all the images
         :param label_dir: Directory will all the label images
@@ -336,6 +336,7 @@ class Resized_BB_ImageDataGenerator_Synthia(Dataset):
         """
         self.trajectory_data = trajectory_data
         self.cf = cf
+        self.trainOrNot = trainornot
         self.img_list = img_list
         self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
         self.crop = crop
@@ -353,8 +354,12 @@ class Resized_BB_ImageDataGenerator_Synthia(Dataset):
         # trajectory
         trajectory = self.trajectory_data[item]
         trajectory_t = torch.FloatTensor(trajectory)
[…]

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
Section 3 added

@@
 \begin{document}
+
 \title{DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving}
@@
 
-\item We construct a time-series dataset for car trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
+\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
 
@@
 
-We first describe our overall approach for car trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
+We first describe our overall approach for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
 Our goal is via collecting the visual information from the past to predict the traffic participants future trajectory.
@@
 
-\subsection{Traffic Participants detection}
+\subsection{Generic 3D Traffic Participants Trajectory Prediction}
 
-\subsection{Instance tracking}
+We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
+Our work is most related to~\cite{xu2017end} where the problem was to predict future feasible actions of egomotion from a motion reflex perspective.
+We, instead,  predict other traffic participants' future trajectories.
+Formally, our problem can be defined as a mapping between historical trajectory $ \{h_t^p\}, t=1,\dots, T $ with auxiliary information $ \{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\{j_t^p\}, t={T+1}, \ldots$:
 
-We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
+\begin{equation}
+\bm{\mathcal{M}}_p(h, a): H \times A  \rightarrow J
+\label{eq:mapping}
+\end{equation}
+where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}. Historical and future trajectories are defined in a 3D occupancy grid:
+\begin{equation}
+H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
+\label{eq:mapping2}
+\end{equation}
+where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target acquired from the depth camera.
+Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinate $\{x_r,y_r,w_r,h_r\}$ as:
+\begin{align}
+    x_r = \frac{x}{f} \times d \\
+    y_r = \frac{y}{f} \times d
+\label{eq:focal_length}
+\end{align}
+where $d$ is distance between  the center of the lens and the center of target and we use $d_{min}$ as a close approximation.
 
-\subsection{Semantic segmentation}
-We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
+Auxiliary information $A$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.
 
-\subsection{Trajectory prediction}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
+        \caption{ {\small TODO: network detail.}}
+        \label{fig:dataset}
+\end{figure}
+\subsection{SEG-LSTM Architecture}
 
@@
 Results show that the temporal model generating intermediate output utilizing the whole historical data performs better than the frame-to-frame based output temporal model.
+
+\subsection{focal lenes back projection into real world grid}
 
@@
 
+\subsubsection{Semantic segmentation}
+We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
+
 \subsubsection{Trajectory prediction}
@@
 
-Future works include incorporating vehicle pose from the RGB input as extra source of ``privileged information"; conducting experiment on the real-world images.
+Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``privileged information"; conducting experiment on the real-world images.
 

### 2017-11-15 code_base/Synthia_car_trajectory.py
shuffle data & re-experiment

@@ -2,7 +2,7 @@ import argparse
 import os
 import sys
 import os
-os.environ['CUDA_VISIBLE_DEVICES'] = '1'
+os.environ['CUDA_VISIBLE_DEVICES'] = '3'
 # Di Wu add the following really ugly code so that python can find the path
 sys.path.append(os.getcwd())
 import time
@@ -31,9 +31,9 @@ def process(cf):
     print('\n > Building model...')
     model = Model_Factory_LSTM(cf)
 
-    # # for experimentt
-    # model.test(cf, DG.valid_loader, DG.data_mean, DG.data_std, 63)
-
+    # for experimentt
+    model.test(cf, DG.test_loader, DG.data_mean, DG.data_std)
+'''
     if cf.train_model:
         train_losses = []
         valid_losses = []
@@ -66,7 +66,7 @@ def process(cf):
         print('---> Test losses:')
         print(test_loss)
     print(' ---> Finish experiment: ' + cf.exp_name + ' <---')
-
+'''
 
 def main():
     # Get parameters from arguments

### 2017-11-15 code_base/config/synthia_car_trajectory.py

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'LSTM_ManyToMany'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
+model_name                   = 'DropoutCNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -108,18 +108,18 @@ test_model                   = True           # Predict using the model
 focal_length                 = 532.740352  # camera focal lense
 
 # Training parameters
-lr_decay_epoch               = 30          # every lr_decay_epoch, decay learning_rate by 10
+lr_decay_epoch               = 40          # every lr_decay_epoch, decay learning_rate by 10
 figure_epoch                 = 10           # every fugure_epoch, figure out the losses
 test_epoch                   = 1
 weight_decay                 = 0.              # Weight decay or L2 parameter norm penalty
-n_epochs                     = 500            # Number of epochs during training
+n_epochs                     = 303            # Number of epochs during training
 cuda                         = True
 loss                         = 'SmoothL1Loss'       # 'MSE', 'SmoothL1Loss'
 optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
-load_trained_model           = False
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Tue, 14 Nov 2017-11-14 17:47:21_LSTM_To_FC_Noshuffle_Nosemantics-TrainBatch4/Epoch:63_net_Coverage:0.6020_Center:35.22_CoverageR:0.2917_CenterR:0.79.PTH'
+load_trained_model           = True
[…]

### 2017-11-15 code_base/tools/PyTorch_model_training.py

@@ -252,12 +252,12 @@ def prepare_data_image_list(cf):
             # normalize data
             train_data, valid_data, test_data, data_mean, data_std = normalise_data(train_data, valid_data, test_data)
 
-            prepared_data = (
-            train_data, valid_data, test_data, data_mean, data_std, train_img_list, valid_img_list, test_img_list)
+            prepared_data = (train_data, valid_data, test_data, data_mean, data_std, train_img_list, valid_img_list, test_img_list)
 
             # save data
             if cf.dataloader_save_shuffle_prepare_data:
                 np.save(cf.dataloader_save_shuffle_prepare_data_path, prepared_data)
+
 
     return prepared_data
 

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
TY: figure table caption update

@@
 \usepackage{algorithmic}
-
+\usepackage{tabu,multirow}
 \DeclareCaptionLabelFormat{noname}{#2}
@@
 
-\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li\\
+\author{Di Wu, Zhennan Wang, Yi Tang,  Wenbin Zou, Xia Li, Chen Xu\\
 Shenzhen University\thanks{Shenzhen Key Lab of Advanced Telecommunication and Information Processing, College of Information Engineering, Shenzhen University.}\\
@@
         \centering
-        \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
+        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
         \caption{ {\small TODO: framework caption goes here.}}
@@
 \begin{align}
-    x_r = \frac{x}{f} \times d \\
-    y_r = \frac{y}{f} \times d
-\label{eq:focal_length}
+    x_r = \frac{x}{f}d &, y_r = \frac{y}{f} d  \label{eq:focal_length_1}  \\
+    w_r = \frac{w}{f}d &, h_r = \frac{h}{f} d  
+    \label{eq:focal_length_2} 
 \end{align}
@@
 
-\subsection{focal lenes back projection into real world grid}
+As shown in figure 3, we compare three temporal models based on LSTM cells for predicting the car trajectory.
+The first architecture(FtoF) is akin to a language model, which predicts the next occupancy grid frame-to-frame.
+At test-time, it samples current predicted 3D occupancy as feedback to the model for predicting next occupancy.
+At time-step t, the architecture utilizes all past historical trajectory up to time-step t  to predict 3D occupancy of the tracking car in next frame.
+This architecture uses a 3-hidden-layer LSTM model followed by a fully connected network at last LSTM hidden layer each time-step.
+The LSTM model has 100, 300, 300 hidden states in each layer respectively, and the fully connected network concludes one hidden layer followed by a ReLU activation layer.
+
+The second architecture(FtoS) is also composed of LSTM part and fully connected part, which are same as the one of the FtoF architecture, but the connecting method is different.
+Rather than predicting frame-to-frame, this architecture can directly predict a trajectory sequences.
+FtoS uses an LSTM as an encoder to fuse all past trajectory information into a single LSTM hidden state, corresponding to the hidden state in last LSTM layer at last time-step T.
+This state is complete, in the sense it contains all historical trajectory information of the tracking car.
+And then we use a fully connected network as decoder to directly predict trajectory during next continuous frames.
+
+In addition to  historical trajectory information, the third architecture(SEG-LSTM) also fuses semantics of  historical frames as auxiliary information.
+The input to the bottom-most LSTM layer is the 3D occupancy of historical trajectory.
+The second LSTM layer fuses the outputs of the bottom-most LSTM with the frame's semantic information, which is extracted from the semantic segmentation through a four-layer CNN, to produce a joint representation of the semantic auxiliary information and the historical trajectory.
+As described above, the 3D occupancy just has six dimensions,{x, y, w, h, dmin, dmax}.
+So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance trajectory information and the semantic information.
+The LSTM part  and fully connected part is same as the one of above two architecture, and the CNN part is composed of four convolutional block.
+Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer.
+Each convolutional layer has four channels and 3×3 kernel.
+Results show that the SEG-LSTM model performs better than the other two temporal model.
+
+%\subsection{focal lenes back projection into real world grid}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}\centering
-\ra{1.}
-\begin{tabular}{@{}llll@{}}\toprule
 
-                & \#train & \#valid & \#test\\
- \hline
- tracklets      &  10400    &  1300    & 1280 \\
- \hline
- car detection  &   7832     & 976     & 986 \\
- \hline
- semantic segmentation  &  7841  & 977  & 987 \\
- \hline
-\end{tabular}
-\caption{Dataset statistics}
-\label{tab:dataset_statistics}
-\end{table}
 \subsection{Implementations}\label{sec:Implementations}
@@
 
-To reliably detect traffic participants, we compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN ~\cite{ren2015faster_nips}.
+To reliably detect traffic participants, we compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster_nips}.
 We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
@@
 
-As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects.
+As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small objects, it's very competitive for detecting larger objects.
 In this paper, we concerns mostly about cars that are close to the driver.
@@
 Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when objects of interest are large in our problem set.
-We also compare the influence of confident score cut-off threshold and non-maximum suppression (NMS) threshold.
+We also compare the influence of the cut-off threshold for various confident scores and non-maximum suppression (NMS) threshold.
 It can been seen that both meta-architectures are robust to the cut-off confident scores.
@@
 \ra{1.}
-\begin{tabular}{@{}llllllllllll@{}}\toprule
+%\begin{tabular}{@{}llllllllllll@{}}\toprule
+\begin{tabu}{@{}llllllllllll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-12}
 \multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
@@
 \bottomrule
-\end{tabular}
+\end{tabu}
+%\end{tabular}
 \caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
@@
 \end{table*}
-
-\subsubsection{Instance tracking}
-
-The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
-However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
-In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
-Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
-For this task, we adopt the real-time scale adaptive tracker fDSST~\cite{danelljan2017discriminative}.
 
@@
         \caption{ {\small TODO: Instance association caption goes here.}}
-        \label{fig:Instance_associationn}
+        \label{fig:Instance_association}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{Semantic segmentation}
-We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
+\begin{table}\centering
+\ra{1.}
+%\begin{tabular}{@{}llll@{}}\toprule
+
+\begin{tabu}{@{}llll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-4}
+                & \#train & \#valid & \#test\\
+ \hline
+
+ tracklets      &  10400    &  1300    & 1280 \\
+ \hline
+ car detection  &   7832     & 976     & 986 \\
+ \hline
+ semantic segmentation  &  7841  & 977  & 987 \\
+ \hline
+ \end{tabu}
+%\end{tabular}
+\caption{Dataset statistics}
+\label{tab:dataset_statistics}
+\end{table}
+
+\subsubsection{Instance tracking}
+
+To associate traffic participants across different frames (\emph{i.e.}, instance tracking), we creatively combine detecting with tracking.
+The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
+However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
+In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
+Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
+For this task, we adopt the real-time scale adaptive tracker fDSST~\cite{danelljan2017discriminative} that achieves 50 FPS with scale estimation.
+
+For every newly detected target whose POR is larger than the predefined threshold of 0.2\%, we initiate the tracker with a unique target ID.
+The tracker's target model is updated every time when there is a detection whose jaccard overlap is larger than 0.3.
+We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergoing rapid out of plane rotations.
+In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{e.f.} Fig.~\ref{fig:Instance_association}).
+The target's tracker will terminate under either of the following two conditions: if the target's POR is smaller than 0.1\% (\emph{i.e.}, the vehicle is too far way from the host car); or if there are more than 5 frames of detection absence  (\emph{i.e.}, the target could be one false positive detection from the vehicle detector).
+
+%\subsubsection{Semantic segmentation}
+%We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
 
@@
 
-TODO: compare the results using Kalman filtering.
+We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus.
+DRN achieves 68\% and 82\% pixel mAP on the car and road categories.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Evaluation}
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
-        \caption{ {\small TODO: evaluation caption goes here.}}
-        \label{fig:evaluation}
-\end{figure}
-
-\begin{table}[t]
-\small
-   \centering
-        \begin{tabular}{|l|| *{2}{c}| *{2}{c} |}\hline
-            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}  & \multicolumn{2}{|c|}{\small 3D}  \\ \hline \hline
-                                                    & P20       & AUC       & P20       & AUC  \\ \hline \hline
-
-            {\small MTM }                          &  58.0     &  38.4     & 64.3      & 44.0   \\
-            \hline
-            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$    &  71.4 ${\color{red}(7.1\uparrow)}$     &  49.1 ${\color{red}(5.1\uparrow)}$\\
-            \hline
-            \hline
-            {\small MaxRes }                        &  57.5     &  38.8     &  65.8     &  45.9  \\
-            \hline
-            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   &  77.8 ${\color{red}(12.0\uparrow)}$    &  53.6 ${\color{red}(7.7\uparrow)}$ \\
-            \hline
-            \hline
-            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$      &  79.8${\color{red}(2.0\uparrow)}$      &  57.0${\color{red}(3.4\uparrow)}$    \\
-            \hline
-            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$     &  79.9${\color{red}(0.1\uparrow)}$     &  57.4${\color{red}(0.4\uparrow)}$\\\hline
-
-        \end{tabular}
-
-    \caption{ {\small
-         TODO: this table is just a place holder, currently has no meaning.}
-          } \label{table_baseline}
-\end{table}
-
-\begin{table}[t]
-\small
-   \centering
-        \begin{tabular}{|l|| *{2}{c}|}\hline
-            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}    \\ \hline \hline
-                                                  & P20       & AUC   \\ \hline \hline
-
-            {\small MTM }                          &  58.0     &  38.4      \\
-            \hline
-            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$  \\
-            \hline
-            \hline
-            {\small MaxRes }                        &  57.5     &  38.8   \\
-            \hline
-            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   \\
-            \hline
-            \hline
-            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$     \\
-            \hline
-            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$    \\\hline
-
-        \end{tabular}
-
-    \caption{ {\small
-    TODO: this table is just a place holder, currently has no meaning. WZN will update the numbers
-          Comparison with the most recent methods }
-          } \label{table_baseline2}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Evaluation Metrics}
-
-\subsubsection{Baselines}
-The Kalman filter is a popular technique for estimating the state of a system.
-Kalman filters estimate a continuous state and gives a uni-modal distribution.
-The Kalman filter represents all distributions of the Gaussians and iterates two things: (1) measurement updates; (2) motion updates
-
 \begin{figure*}[t]
@@
 
+\subsection{Evaluation}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
+        \caption{ {\small TODO: evaluation caption goes here.}}
+        \label{fig:evaluation}
+\end{figure}
+
+\noindent \textbf{2D Evaluation Methodology:}
+Following the evaluation strategy  of~\cite{wu2013online}, all trajectories are compared using two measures: precision and success.
+Precision is measured as the distance between the centres of the ground truth bounding box and the corresponding tracker generated bounding box.
+The precision plot shows the percentage of tracker bounding boxed within a given threshold distance in pixels of the ground truth.
+To rank the prediction performance, the conventional threshold of 20 pixels (\emph{P20}) is adopted.
+Success is measured as the intersection over union of pixels.
+The success plot shows the percentage of tracker bounding boxes whose overlap score is larger than a given threshold and the trackers are ranked according to the Area Under Curve (\emph{AUC}) criteria.
+% All sequences are evaluated using One-Pass Evaluation (OPE) as in~\cite{wu2013online}.
+
+\vspace{\baselineskip}
+\noindent \textbf{3D Evaluation Methodology:} Given depth map and the parameter of camera focal lens, we can formalize the problem into a 3D occupancy grid estimation.
+The real world coordinates $[x_r, y_r, w_r, h_r] $can be obtained according to Eq.~\ref{eq:focal_length_1}~\ref{eq:focal_length_2}.
+The 3D jaccard index can be similarly formalized as the volume intersection over union: $\frac{V_g \cap V_p}{V_g \cup V_p}$, where $V_g, V_p$ are the ground truth and predicted space occupancy.
+3D center error correspondingly is defined as the mean square root in 3D space.
+
+\vspace{\baselineskip}
+\noindent \textbf{Baseline: Kalman filter}, also known as linear quadratic estimation, is a popular technique for estimating the state of a system~\cite{Thrun2016}.
+For the task of trajectory prediction, Kalman filters estimate a continuous state and gives a uni-modal distribution.
+The Kalman filter represents all distributions of the Gaussians and iterates two states: (1) measurement updates; (2) motion updates.
+In the baseline, we set
+the initial uncertainly covariance as 1e4, measurement noise and motion noise are all set unit value.
+
+\vspace{\baselineskip}
+\noindent \textbf{Learning with auxiliary information}
+
+\begin{table}[t]
+\small
+   \centering
+        %\begin{tabular}{|l *{2}{c}|}\hline
+        %\begin{tabu}{|l *{2}{c}|}
+        \begin{tabu}{@{}ccc@{}}\toprule
+        [-1pt] \tabucline[1pt]{1-3}
+
+            Configuration  &     mean coverage      & center error   \\
+                       2D   &       (\%) &             (pixel)     \\ \hline
+
+            {\small Kalman Filter}             &  54.31          &  24.84             \\
+
+            {\small \textbf{FtF} }              &  66.47     &  23.43  \\
+
+            {\small \textbf{FtS}  }              &  73.93      &   15.32  \\
+
+            {\small \textbf{SEG-LSTM} }         &  \textbf{77.53  }    & \textbf{ 12.63 }   \\
+          [-1pt] \tabucline[1pt]{1-3}      
+        \end{tabu}
+        %\end{tabular}
+
+    \caption{ {\small
+    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better). Mean coverage is the average 
+     }
+          } \label{table_baseline2}
+\end{table}
+%%%%%%%%%%%%%%%%%
+
+\begin{table}[t]
+\small
+   \centering
+        %\begin{tabular}{|l *{2}{c}|}\hline
+        %\begin{tabu}{|l *{2}{c}|}
+        \begin{tabu}{@{}ccc@{}}\toprule
+        [-1pt] \tabucline[1pt]{1-3}
+
+           Configuration  &   mean coverage      & center error   \\
+                       3D   &       (\%) &             (meter)     \\
+                            \hline
+            {\small \textbf{FtF} }              &    35.67    &  0.7122   \\
+
+            {\small \textbf{FtS}  }              &   46.69	     &    0.3686 \\
+
+            {\small \textbf{SEG-LSTM} }         &  \textbf{48.49}     &   \textbf{0.3298}   \\
+          [-1pt] \tabucline[1pt]{1-3}
+        \end{tabu}
+        %\end{tabular}
+
+    \caption{ {\small
+    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better). Mean coverage is the average
+     }
+          } \label{table_baseline2}
+\end{table}
+%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsubsection{Evaluation Metrics}
+
 \section{Conclusions}
-
-Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``privileged information"; conducting experiment on the real-world images.
+In this paper, mimicking the human driver reaction time, we advocate to solve the problem of predicting traffic participants future trajectory given historical information.
+We propose a two staged system incorporating various visual inputs with a temporally recurrent neural networks.
+The recurrent network takes semantic information as an auxiliary input and further improve the predicting accuracy.
+Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``privileged information" and conducting experiments on the real-world images.
 
 \section*{Details of the Code}
- The code will be made public upon publication.
+\footnote{The code will be made public upon publication.}
 
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
figure caption draft

--- 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
@@
         \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
-        \caption{ {\small TODO: Pull figure caption goes here.}}
+        \caption{ {\small We propose a system to predict future trajectories of vehicles.
+Given a historical information, obtained by detection, tracking and semantic segmentation, a network based on Long Short Term Memory (LSTM) structure is trained to generate future information}}
         \label{fig:pull_figure}
@@
         \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
-        \caption{ {\small TODO: framework caption goes here.}}
+        \caption{ {\small The framework of our vehicle future trajectory prediction system.
+The input is the sequence data from a synthetic scene in \cite{mueller2016benchmark}.
+Historical information are extracted by detection & tracking and semantic segmentation.
+All of the information is fed into our LSTM model to predict future trajectories.}}
         \label{fig:framework}
@@
         \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
-        \caption{ {\small TODO: network detail.}}
+        \caption{ {\small Different networks to predict future trajectory. Left: FrameToFrame, .....; Middle:FrameToSeq, ....; Right:SEG-LSTM, ......}}
         \label{fig:dataset}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}\centering
-\ra{1.}
-\begin{tabular}{@{}llll@{}}\toprule
-
-                & \#train & \#valid & \#test\\
- \hline
- tracklets      &  10400    &  1300    & 1280 \\
- \hline
- car detection  &   7832     & 976     & 986 \\
- \hline
- semantic segmentation  &  7841  & 977  & 987 \\
- \hline
-\end{tabular}
-\caption{Dataset statistics}
-\label{tab:dataset_statistics}
-\end{table}
+%\begin{table}\centering
+%\ra{1.}
+%\begin{tabular}{@{}llll@{}}\toprule
+%
+%                & \#train & \#valid & \#test\\
+% \hline
+% tracklets      &  10400    &  1300    & 1280 \\
+% \hline
+% car detection  &   7832     & 976     & 986 \\
+% \hline
+% semantic segmentation  &  7841  & 977  & 987 \\
+% \hline
+%\end{tabular}
+%\caption{Dataset statistics}
+%\label{tab:dataset_statistics}
+%\end{table}
 \subsection{Implementations}\label{sec:Implementations}
@@
 
-\begin{table*}\centering
-\ra{1.}
-\begin{tabular}{@{}llllllllllll@{}}\toprule
-\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
-\hline
-\multirow{3}{*}{Faster-RCNN}
-                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
-                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
-                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
-                    \cline{2-12}
-\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
-                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
-                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
-                    \cline{2-12}
-\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
-                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
-                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
-
-\bottomrule
-\end{tabular}
-\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
-\label{tab:ssd_fasterrcnn}
-\end{table*}
+%\begin{table*}\centering
+%\ra{1.}
+%\begin{tabular}{@{}llllllllllll@{}}\toprule
+%\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
+%\hline
+%\multirow{3}{*}{Faster-RCNN}
+%                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
+%                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
+%                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+%                    \cline{2-12}
+%\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
+%                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
+%                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
+%                    \cline{2-12}
+%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+%                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+%                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+%
+%\bottomrule
+%\end{tabular}
+%\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
+%\label{tab:ssd_fasterrcnn}
+%\end{table*}
 
@@
         \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
-        \caption{ {\small TODO: evaluation caption goes here.}}
+        \caption{ {\small TODO: The evaluation of 2D and 3D prediction.
+2D: It is the bounding box to cover the whole vehicle.
+3D: The depth channel is combined with 2D bounding box to predict trajectory.}}
         \label{fig:evaluation}
@@
 
-\begin{table}[t]
-\small
-   \centering
-        \begin{tabular}{|l|| *{2}{c}| *{2}{c} |}\hline
-            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}  & \multicolumn{2}{|c|}{\small 3D}  \\ \hline \hline
-                                                    & P20       & AUC       & P20       & AUC  \\ \hline \hline
+%\begin{table}[t]
+%\small
+%   \centering
+%        \begin{tabular}{|l|| *{2}{c}| *{2}{c} |}\hline
+%            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}  & \multicolumn{2}{|c|}{\small 3D}  \\ \hline \hline
+%                                                    & P20       & AUC       & P20       & AUC  \\ \hline \hline
+%
+%            {\small MTM }                          &  58.0     &  38.4     & 64.3      & 44.0   \\
+%            \hline
+%            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$    &  71.4 ${\color{red}(7.1\uparrow)}$     &  49.1 ${\color{red}(5.1\uparrow)}$\\
+%            \hline
+%            \hline
+%            {\small MaxRes }                        &  57.5     &  38.8     &  65.8     &  45.9  \\
+%            \hline
+%            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   &  77.8 ${\color{red}(12.0\uparrow)}$    &  53.6 ${\color{red}(7.7\uparrow)}$ \\
+%            \hline
+%            \hline
+%            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$      &  79.8${\color{red}(2.0\uparrow)}$      &  57.0${\color{red}(3.4\uparrow)}$    \\
+%            \hline
+%            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$     &  79.9${\color{red}(0.1\uparrow)}$     &  57.4${\color{red}(0.4\uparrow)}$\\\hline
+%
+%        \end{tabular}
+%
+%    \caption{ {\small
+%         TODO: this table is just a place holder, currently has no meaning.}
+%          } \label{table_baseline}
+%\end{table}
 
-            {\small MTM }                          &  58.0     &  38.4     & 64.3      & 44.0   \\
-            \hline
-            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$    &  71.4 ${\color{red}(7.1\uparrow)}$     &  49.1 ${\color{red}(5.1\uparrow)}$\\
-            \hline
-            \hline
-            {\small MaxRes }                        &  57.5     &  38.8     &  65.8     &  45.9  \\
-            \hline
-            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   &  77.8 ${\color{red}(12.0\uparrow)}$    &  53.6 ${\color{red}(7.7\uparrow)}$ \\
-            \hline
-            \hline
-            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$      &  79.8${\color{red}(2.0\uparrow)}$      &  57.0${\color{red}(3.4\uparrow)}$    \\
-            \hline
-            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$     &  79.9${\color{red}(0.1\uparrow)}$     &  57.4${\color{red}(0.4\uparrow)}$\\\hline
-
-        \end{tabular}
-
-    \caption{ {\small
-         TODO: this table is just a place holder, currently has no meaning.}
-          } \label{table_baseline}
-\end{table}
-
-\begin{table}[t]
-\small
-   \centering
-        \begin{tabular}{|l|| *{2}{c}|}\hline
-            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}    \\ \hline \hline
-                                                  & P20       & AUC   \\ \hline \hline
-
-            {\small MTM }                          &  58.0     &  38.4      \\
-            \hline
-            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$  \\
-            \hline
-            \hline
-            {\small MaxRes }                        &  57.5     &  38.8   \\
-            \hline
-            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   \\
-            \hline
-            \hline
-            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$     \\
-            \hline
-            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$    \\\hline
-
-        \end{tabular}
-
-    \caption{ {\small
-    TODO: this table is just a place holder, currently has no meaning. WZN will update the numbers
-          Comparison with the most recent methods }
-          } \label{table_baseline2}
-\end{table}
+%\begin{table}[t]
+%\small
+%   \centering
+%        \begin{tabular}{|l|| *{2}{c}|}\hline
+%            {\small Configuration} & \multicolumn{2}{|c|}{\small 2D}    \\ \hline \hline
+%                                                  & P20       & AUC   \\ \hline \hline
+%
+%            {\small MTM }                          &  58.0     &  38.4      \\
+%            \hline
+%            {\small \textbf{MTFC} }  &  66.2 ${\color{red}(8.2\uparrow)}$    &  46.1 ${\color{red}(7.7\uparrow)}$  \\
+%            \hline
+%            \hline
+%            {\small MaxRes }                        &  57.5     &  38.8   \\
+%            \hline
+%            {\small \textbf{MTM (GT)} }        &  70.6${\color{red}(13.1\uparrow)}$     &  46.7  ${\color{red}(7.9\uparrow)}$   \\
+%            \hline
+%            \hline
+%            {\small \textbf{MTFC}}           &  74.0${\color{red}(3.4\uparrow)}$      &  51.8${\color{red}(5.1\uparrow)}$     \\
+%            \hline
+%            {\small \textbf{DAC}}&  74.2 ${\color{red}(0.2\uparrow)}$    &  52.1${\color{red}(0.3\uparrow)}$    \\\hline
+%
+%        \end{tabular}
+%
+%    \caption{ {\small
+%    TODO: this table is just a place holder, currently has no meaning. WZN will update the numbers
+%          Comparison with the most recent methods }
+%          } \label{table_baseline2}
+%\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
Paper writing: 2d, 3d evaluation

--- 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
@@
     \centering
-    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot.png}
+    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
     \caption{\small{Precision plot for 2D}}
@@
     \centering
-        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot.png}
+        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
         \caption{\small{Success plot 2D}}
@@
      \begin{subfigure}[c]{0.4\textwidth}
-     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot.png}
-    \caption{\small{Precision plot for 2D}}
+     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20.png}
+    \caption{\small{Precision plot for 3D}}
     \end{subfigure}%
@@
     \centering
-        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot.png}
-        \caption{\small{Success plot 2D}}
+        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
+        \caption{\small{Success plot 3D}}
     \end{subfigure}

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
figure caption draft

--- 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
@@
         \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
-        \caption{ {\small TODO: Pull figure caption goes here.}}
+        \caption{ {\small We propose a system to predict future trajectories of vehicles.
+Given a historical information, obtained by detection, tracking and semantic segmentation, a network based on Long Short Term Memory (LSTM) structure is trained to generate future information.}}
         \label{fig:pull_figure}
@@
         \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
-        \caption{ {\small TODO: framework caption goes here.}}
+        \caption{ {\small The framework of our vehicle future trajectory prediction system.
+The input is the sequence data from a synthetic scene in \cite{mueller2016benchmark}.
+Historical information are extracted by detection & tracking and semantic segmentation.
+All of the information is fed into our LSTM model to predict future trajectories.}}
         \label{fig:framework}
@@
         \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
-        \caption{ {\small TODO: network detail.}}
+        \caption{ {\small Different networks to predict future trajectory.
+Left: FrameToFrame, using historical trajectories with many-to-many LSTM to predict; Middle:FrameToSeq, using historical trajectories with many-to-many LSTM ; Right:SEG-LSTM, the proposed model by using historical trajectories and semantic segmentation information.}}
         \label{fig:dataset}
@@
 Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer.
-Each convolutional layer has four channels and 3×3 kernel.
+Each convolutional layer has four channels and 3¡Á3 kernel.
 Results show that the SEG-LSTM model performs better than the other two temporal model.
@@
         \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
-        \caption{ {\small TODO: evaluation caption goes here.}}
+        \caption{ {\small The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.}}
         \label{fig:evaluation}

### 2018-01-19 Kalman_filter_new.py
rebuttal process start

@@ -74,17 +74,21 @@ def calc_rect_int_2d(A, B):
 
 def demo_kalman_xy():
 
-    valid_data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\car_trajectory_prediction\valid_data_array.npy')
-    test_data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\car_trajectory_prediction\test_data_array.npy')
-    print('Finish Loading')
-    valid_pred = np.zeros(shape=(len(valid_data_array), 8, 6))
-    valid_pred[:, :, 5:] = valid_data_array[:, -8:, 5:]
+    data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\Kalman_filter\prepared_data_shuffle.npy')
+    test_data_array = data_array[2]
+    data_mean = data_array[3]
+    data_std = data_array[4]
+    test_data_array = (test_data_array * data_std) + data_mean
+
+    print('Finish Loading. Test array shape: ' + str(test_data_array.shape))
+    test_pred = np.zeros(shape=(len(test_data_array), 8, 6))
+    test_pred[:, :, 5:] = test_data_array[:, -8:, 5:]
     # Query the figure's on-screen size and DPI. Note that when saving the figure to
     # a file, we need to provide a DPI for that separately.
 
     x = np.matrix('0. 0. 0. 0.').T
     P = np.matrix(np.eye(4))*1000  # initial uncertainty
-    for f, data in enumerate(valid_data_array):
+    for f, data in enumerate(test_data_array):
         if f%100 == 0:
             print("process batch %d" %f)
         observed_x = np.array([d[0] for d in data])
@@ -96,24 +100,23 @@ def demo_kalman_xy():
             result.append((x[:2]).tolist())
         result_new = []
         result_new.append([result[-1][0], result[-1][1]])
-        valid_pred[f, 0, 0] = result[-1][0][0]
-        valid_pred[f, 0, 1] = result[-1][1][0]
+        test_pred[f, 0, 0] = result[-1][0][0]
+        test_pred[f, 0, 1] = result[-1][1][0]
         for t in range(7):
             x_pred = result_new[-1][0] + x[2]
             y_pred = result_new[-1][1] + x[3]
-            valid_pred[f, t + 1, 0] = np.array(x_pred)[0][0]
[…]

### 2018-01-19 code_base/animation_demo.py

@@ -1,0 +1,99 @@
+import os
+import numpy as np
+import matplotlib
+matplotlib.use('TkAgg')
+from matplotlib.animation import FuncAnimation
+import matplotlib.pyplot as plt
+from code_base.tools.kalman_filtering import kalman_xy
+import seaborn
+
+
+def get_img_list(valid_data, test_data):
+
+    valid_img_list = []
+    for d in valid_data:
+        item_list = [x[6] for x in d]
+        valid_img_list.append(item_list)
+
+    test_img_list = []
+    for d in test_data:
+        item_list = [x[6] for x in d]
+        test_img_list.append(item_list)
+
+    return  valid_img_list, test_img_list
+
+
+def get_data_with_img_list(valid_data, test_data):
+    valid_data_array = np.array(valid_data[:, :, :6]).astype('float')
+    test_data_array = np.array(test_data[:, :, :6]).astype('float')
+    return  valid_data_array, test_data_array
+
+
+def prepare_data_image_list(cf):
+    import pickle
+    with open(os.path.join(cf['trajectory_path'], cf['sequence_name'] + '_valid.npy'), 'rb') as fp:
+        valid_data = pickle.load(fp)
+    with open(os.path.join(cf['trajectory_path'], cf['sequence_name'] + '_test.npy'), 'rb') as fp:
+        test_data = pickle.load(fp)
+
+    valid_data_array, test_data_array = get_data_with_img_list(valid_data, test_data)
+    valid_img_list, test_img_list = get_img_list(valid_data, test_data)
+
+    return  valid_data_array, test_data_array, valid_img_list, test_img_list
+
+
+def demo_kalman_xy():
+
+    valid_data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\car_trajectory_prediction\valid_data_array.npy')
+    test_data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\car_trajectory_prediction\test_data_array.npy')
+    print('Finish Loading')
+
+    # Query the figure's on-screen size and DPI. Note that when saving the figure to
+    # a file, we need to provide a DPI for that separately.
+
+    x = np.matrix('0. 0. 0. 0.').T
+    P = np.matrix(np.eye(4))*1000  # initial uncertainty
+
+    for f, data in enumerate(valid_data_array[50:60]):
+        plt.cla()
+        observed_x = np.array([d[0] for d in data])
[…]

### 2018-01-19 code_base/animation_new.py

@@ -1,0 +1,100 @@
+import os
+import numpy as np
+import matplotlib
+matplotlib.use('TkAgg')
+from matplotlib.animation import FuncAnimation
+import matplotlib.pyplot as plt
+from code_base.tools.kalman_filtering import kalman_xy
+import seaborn
+
+
+def get_img_list(valid_data, test_data):
+
+    valid_img_list = []
+    for d in valid_data:
+        item_list = [x[6] for x in d]
+        valid_img_list.append(item_list)
+
+    test_img_list = []
+    for d in test_data:
+        item_list = [x[6] for x in d]
+        test_img_list.append(item_list)
+
+    return  valid_img_list, test_img_list
+
+
+def get_data_with_img_list(valid_data, test_data):
+    valid_data_array = np.array(valid_data[:, :, :6]).astype('float')
+    test_data_array = np.array(test_data[:, :, :6]).astype('float')
+    return  valid_data_array, test_data_array
+
+
+def prepare_data_image_list(cf):
+    import pickle
+    with open(os.path.join(cf['trajectory_path'], cf['sequence_name'] + '_valid.npy'), 'rb') as fp:
+        valid_data = pickle.load(fp)
+    with open(os.path.join(cf['trajectory_path'], cf['sequence_name'] + '_test.npy'), 'rb') as fp:
+        test_data = pickle.load(fp)
+
+    valid_data_array, test_data_array = get_data_with_img_list(valid_data, test_data)
+    valid_img_list, test_img_list = get_img_list(valid_data, test_data)
+
+    return  valid_data_array, test_data_array, valid_img_list, test_img_list
+
+
+def demo_kalman_xy():
+    data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\Kalman_filter\prepared_data_shuffle.npy')
+    test_data_array = data_array[2]
+    print('Finish Loading. Test array shape: ' + str(test_data_array.shape))
+    test_pred = np.zeros(shape=(len(test_data_array), 8, 6))
+    test_pred[:, :, 5:] = test_data_array[:, -8:, 5:]
+
+    # Query the figure's on-screen size and DPI. Note that when saving the figure to
+    # a file, we need to provide a DPI for that separately.
+
+    x = np.matrix('0. 0. 0. 0.').T
+    P = np.matrix(np.eye(4))*1000  # initial uncertainty
+
+    for f, data in enumerate(test_data_array[50:60]):
[…]

### 2018-01-19 code_base/final_visualisation.py

@@ -1,0 +1,47 @@
+import numpy as np
+import os
+import matplotlib
+from PIL import Image
+matplotlib.use('TkAgg')
+import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+import matplotlib.patches as patches
+
+
+def main():
+    data_array = np.load(r'C:\Users\steve\Desktop\cvpr_figure\Kalman_filter\prepared_data_shuffle.npy')
+    test_data_array = data_array[2]
+    data_mean = data_array[3]
+    data_std = data_array[4]
+    test_data_array = (test_data_array * data_std) + data_mean
+
+    item_data = test_data_array[693]
+    img_path =r'C:\Users\steve\Desktop\cvpr_figure\Final_VISUAL'
+    img_list = sorted(os.listdir(img_path))
+
+    fig = plt.figure(1)
+
+    tracking_figure_axes = fig.add_subplot(111, aspect='equal')
+    for i,item in enumerate(item_data):
+
+        rect = item[:4]
+        print(rect)
+        im = Image.open(os.path.join(img_path, img_list[i]))
+        tracking_figure_axes.imshow(im)
+        # Create a Rectangle patch
+        tracking_rect = Rectangle(
+            xy=(rect[1]-rect[3]/2., rect[0]-rect[2]/2),
+            width=rect[3],
+            height=rect[2],
+            facecolor='none',
+            edgecolor='r',
+        )
+        tracking_figure_axes.add_patch(tracking_rect)
+        plt.waitforbuttonpress(1)
+    fig.clear()
+
+
+
+# Entry point of the script
+if __name__ == "__main__":
+    main()

### 2018-01-19 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
rebuttal template added

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3790} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
The reviewers generally acknowledge the extensibility of our framework, well evaluated experiments, and the novelty of introducing ergodic state to perform segmentation and recognition within the same framework. Due to space constraints, we address only the major criticisms below.

\subsection{R2}

\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize continuous video streams for the prediction problems.
are required for the purpose of car trajectory prediction. We
collect car trajectory prediction dataset based on the SYN-
THIA [29] dataset.

Where are comparisons with other activity forecasting/trajectory
prediction works?
I think the authors should reimplement SocialLSTM for 2D data (Stanford
UAV dataset seems to be a 2D standard prediction task -- just throw
away images and just use the xy plane coordinates, e.g. center of
detected bounding box).
SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and
“final disp. Error”
What was the justification for the metrics the authors chose?
In the SocialLSTM paper’s Related Work section, there are about 20
sources that focus on “Activity forecasting”
The details about the fusion of “location” and “semantic” information into
the LSTM hidden state seemed missing (was a bit vague). A figure of the
architecture of the SEG-LSTM would go a long way in clarifying this (or
are the authors using Xu et al.'s "End-to-end Learning of Driving Models
from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's
group?).
How is this more than just an engineering pipeline, combining tracking
(distilling bounding boxes to coordinates), and then adding an LSTM?
SocialLSTM already did the second part in principle.
I was a bit confused about why the “tracking-by-detection” framework
was novel -- how is it different from “Tracking-learning-detection” (TLD),
from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?
Why are scene semantics privileged (which you also call “auxiliary”)
information?
If the pipeline relies on fusing the “location” and “semantic” stream, if
privileged information is missing at test time, then won’t the pipeline
break? (privileged information is usually present at train time, but
absent at test time).
Can multiple objects be tracked at once, or just one? The video in the
supplementary material only showed one object being tracked. What was
the average number of objects in each SYNTHIA scene frame?
The focus of the paper seems a bit unclear: apparently, the goal is to
“predict car’s future odometry given previous egomotion visual input”.
But the paper is about prediction of other vehicles’ trajectories, not
about predicting one’s own car odometry (which is different).
Odometry: “Odometry is the use of motion sensors to determine the
robot's change in position relative to some known position” (not other
robots' positions) https://groups.csail.mit.edu/drl/courses/cs54-
2001s/odometry.html
“Visual Odometry -- Estimating the motion of a camera in real time using
sequential images (i.e., egomotion)”
\verb+http://www.cs.toronto.edu/~urtasun/courses/CSC2541/03_odometry.pdf+
(but we are not trying to estimate the motion of a camera-mounted
vehicle here).
I felt like the detection/tracking theme slightly bogs down the main focus
of prediction in the paper. I think refocusing it on prediction would
strengthen the argument.
Line 124 - The authors discuss a "lack of proper metrics for evaluating
the temporal prediction result." How are the current metrics poorly
suited to the task? What would be better?

\subsection{Old}
After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers. It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers. You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-01-19 paper/cvpr2018/cvpr2018_3790.tex
rebuttal template added

--- 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
@@
 
-\def\cvprPaperID{16} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{3790} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \section{Introduction}
-
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
+        \caption{ {
+        We propose a system to predict future trajectories of vehicles.
+Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
+        \label{fig:pull_figure}
+\end{figure}
 %\textbf{\emph{1.1 What is the problem?}}
@@
 Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and then parse the scene to make a driving policy (usually by a controller with if-then-else rules); and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
-In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of vehicles given its past information.
+In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of vehicle given its past information.
 
@@
 
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
-        \caption{ {\small TODO: Pull figure caption goes here.}}
-        \label{fig:pull_figure}
-\end{figure}
-
 %\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
-Vehicles trajectory prediction is also very related to visual tracking.
+Vehicle trajectory prediction is also very related to visual tracking.
 In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
@@
 Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network.
-At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture.
+At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build an end-to-end architecture.
 Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class.
@@
         \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
-        \caption{ {\small TODO: framework caption goes here.}}
+        \caption{
+        The framework for the proposed vehicle future trajectory prediction system.
+The input is the sequential data obtained from the host car.
+Historical information is extracted by detection \& tracking.
+Along with scene semantics as an auxiliary information, multi-stream inputs are fed into our LSTM model to predict future trajectories.}
+
         \label{fig:framework}
@@
 The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
-More recently, larger project are constructed:
+More recently, larger projects are constructed:
 Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes.
@@
 The use of synthetic data has increased considerably in recent years within computer vision community.
-A synthetic dataset named Synthia is\cite{mueller2016benchmark} provide originally for urban scene semantic segmentation generation.
+A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
 %In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
 Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
-Synthetic dataset has an obvious advantage: a fine annotated images in Cityscape dataset requires on average 1.5 hours which is very labor intensive.
-Thus, the cost of scaling large project would required a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
+Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive.
+Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
 %For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
@@
 
-We first describe our overall approach for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
-Our goal is via collecting the visual information from the past to predict the traffic participants future trajectory.
-Fig.~\ref{fig:framework} shows the overall architecture of our proposed framework.
+We first describe the overall framework for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
+Our goal is via collecting visual information from the past frames to predict the traffic participants future trajectory.
+Fig.~\ref{fig:framework} shows the overall architecture of the proposed framework.
 
-\subsection{Generic 3D Traffic Participants Trajectory Prediction}
+\subsection{3D Traffic Participants Trajectory Prediction}
 
 We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
-Our work is most related to~\cite{xu2017end} where the problem was to predict future feasible actions of egomotion from a motion reflex perspective.
-We, instead,  predict other traffic participants' future trajectories.
-Formally, our problem can be defined as a mapping between historical trajectory $ \{h_t^p\}, t=1,\dots, T $ with auxiliary information $ \{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\{j_t^p\}, t={T+1}, \ldots$:
+Our work is most related to~\cite{xu2017end} where the problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
+We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
+Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $H=\{h_t^p\}, t=1,\dots, T $ with auxiliary information $ A=\{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $J=\{j_t^p\}, t={T+1}, \ldots$:
 
 \begin{equation}
-\bm{\mathcal{M}}_p(h, a): H \times A  \rightarrow J
+J \leftarrow \bm{\mathcal{M}}_p(h, a): H \times A
 \label{eq:mapping}
 \end{equation}
-where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}. Historical and future trajectories are defined in a 3D occupancy grid:
+where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}.
+In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on.
+Historical and future trajectories are defined in a 3D occupancy grid:
 \begin{equation}
@@
 \end{equation}
-where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target acquired from the depth camera.
-Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinate $\{x_r,y_r,w_r,h_r\}$ as:
+where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target (acquired from the depth camera).
+Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinates $\{x_r,y_r,w_r,h_r\}$ as:
 \begin{align}
@@
 \end{align}
-where $d$ is distance between  the center of the lens and the center of target and we use $d_{min}$ as a close approximation.
+where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ is as a close approximation.
 
@@
         \centering
-        \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
-        \caption{ {\small TODO: network detail.}}
-        \label{fig:dataset}
+        \includegraphics[width=0.52\textwidth]{figures/network_detail.pdf}
+        \caption{Illustrations of three temporal networks.
+$H$ represents historical trajectories, $J$ is the $T$ time step trajectories to be predicted.
+Left: Frame-to-Frame (FtF); Middle:Frame-to-Sequence (FtS); Right:SEG-LSTM, with extra auxiliary information as input $A$.}
+        \label{fig:lstm}
 \end{figure}
-\subsection{SEG-LSTM Architecture}
 
-We compare two temporal models based on LSTM cells for predicting the car trajectory.
-Results show that the temporal model generating intermediate output utilizing the whole historical data performs better than the frame-to-frame based output temporal model.
+\subsection{Sequence modeling}
 
-As shown in figure 3, we compare three temporal models based on LSTM cells for predicting the car trajectory.
-The first architecture(FtoF) is akin to a language model, which predicts the next occupancy grid frame-to-frame.
-At test-time, it samples current predicted 3D occupancy as feedback to the model for predicting next occupancy.
-At time-step t, the architecture utilizes all past historical trajectory up to time-step t  to predict 3D occupancy of the tracking car in next frame.
-This architecture uses a 3-hidden-layer LSTM model followed by a fully connected network at last LSTM hidden layer each time-step.
-The LSTM model has 100, 300, 300 hidden states in each layer respectively, and the fully connected network concludes one hidden layer followed by a ReLU activation layer.
+For predicting vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}.
+The first two models take sequential 3D occupancy as input.
+In the third model, we  explore using semantic segmentation as a side ``auxiliary" information to better guide the trajectory prediction.
 
-The second architecture(FtoS) is also composed of LSTM part and fully connected part, which are same as the one of the FtoF architecture, but the connecting method is different.
-Rather than predicting frame-to-frame, this architecture can directly predict a trajectory sequences.
-FtoS uses an LSTM as an encoder to fuse all past trajectory information into a single LSTM hidden state, corresponding to the hidden state in last LSTM layer at last time-step T.
-This state is complete, in the sense it contains all historical trajectory information of the tracking car.
-And then we use a fully connected network as decoder to directly predict trajectory during next continuous frames.
+\vspace{\baselineskip}
+\noindent \textbf{Frame-to-Frame (FtF) model:}
+is akin to character prediction in a language model.
+At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid.
+The model is frame to frame Markovian and the next frame trajectory $j_t$ can be estimated as:
+\begin{equation}
+j_t \leftarrow  \bm{\mathcal{M}}_p(j_{t-1}, h): H
+\label{eq:FtF}
+\end{equation}
 
-In addition to  historical trajectory information, the third architecture(SEG-LSTM) also fuses semantics of  historical frames as auxiliary information.
-The input to the bottom-most LSTM layer is the 3D occupancy of historical trajectory.
-The second LSTM layer fuses the outputs of the bottom-most LSTM with the frame's semantic information, which is extracted from the semantic segmentation through a four-layer CNN, to produce a joint representation of the semantic auxiliary information and the historical trajectory.
-As described above, the 3D occupancy just has six dimensions,{x, y, w, h, dmin, dmax}.
-So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance trajectory information and the semantic information.
-The LSTM part  and fully connected part is same as the one of above two architecture, and the CNN part is composed of four convolutional block.
-Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer.
-Each convolutional layer has four channels and 3×3 kernel.
-Results show that the SEG-LSTM model performs better than the other two temporal model.
+\vspace{\baselineskip}
+\noindent \textbf{Frame-to-Sequence (FtS) model:}
+differs from the FtF model in that instead of sampling frame by frame for predicting future trajectories,   FtS model directly predicts a trajectory sequence of length $T$ (corresponding to the total driver reaction time).
+The assumption is that current state is complete, in the sense it contains all historical information required for predicting the future trajectory of the vehicle.
+The whole trajectory  $j_{t, t+1, \ldots, T}$ to be predicted can be estimated as:
+\begin{equation}
+j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p( h): H
+\label{eq:FtS}
+\end{equation}
 
-%\subsection{focal lenes back projection into real world grid}
+\vspace{\baselineskip}
+\noindent \textbf{SEG-LSTM model:}
+ take advantages of scene semantics from  historical frames as auxiliary information $A$.
+The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information.
+Semantic inputs are one-hot encoded images with channel number $C$ as the number of semantic category.
+The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.
+As described above, the 3D occupancy just has six dimensions: $[x, y, w, h, d_{min}, d_{max}]$.
+So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance input dimensions of both trajectory information and the semantic information.
+%Results show that the SEG-LSTM model performs better than the other two temporal model.
+Note that this model differs from that of~\cite{xu2017end} in that instead of using semantic segmentation as a side task for better directing the learning process of the convnets, SEG-LSTM directly takes scene semantics as input and directs the recurrent net future trajectory prediction.
+With auxiliary $A$, the trajectory  $j_{t, t+1, \ldots, T}$  to be predicted can be estimated as:
+
+\begin{equation}
+j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p(h, a): H \times A
+\label{eq:SEG-LSTM}
+\end{equation}
 
@@
 
+We first provide the data collection procedure for vehicle trajectory prediction.
+And then we present the implementation details with performance analysis of individual modules.
+Quantitatively examination of SEG-LSTM architecture is also presented showing the advantages of using semantics directly as input can better assist the neural net's trajectory prediction.
+
 \subsection{Dataset collection}
-
-Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
-We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
-SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
-The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
-The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
-There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
-Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
-In our experiment, we used only left front camera view data.
-
-The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset.
-We especially concern about the cars that are relatively close to the driver.
-In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
-As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
-Since depth information is also provided alongside in the SYNTHIA dataset, we back-projecting the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracking vehicle.
-Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
-We follow the prediction time allocation as in~\cite{xu2017end} that the historical time-span is 3 seconds (corresponds to 15 frames with 5 Hz frame rate in the SYNTHIA dataset).
-However, in contrast with~\cite{xu2017end} where only the next 1/3rd of a second is predicted, we strive to predict the next 1.5 second's future trajectory as mentioned previously that it's the reaction time accident reconstruction specialists commonly used~\cite{mcgehee2000driver}.
-
-We follow the traditional paradigm for visual tracking to collect target's bounding box: $[x, y, w, h]$ of each frame.
-Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
-The train/valid/test are split as 80\%/10\%/10\% of the total tracklets and the total numbers are shown in Tab.~\ref{tab:dataset_statistics}.
-We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
-Some sample frames with semantic labels and depth information is shown in Fig.~\ref{fig:dataset}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{algorithm}[h]
@@
 \end{algorithm}
+
+Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
+We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
+SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
+The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
+The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
+There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
+Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
+In our experiment, we used only left front camera view data.
+
+The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset.
+We especially concern about the cars that are relatively close to the driver.
+In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
+As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
+Since depth information is also provided alongside in the SYNTHIA dataset, we back-projecting the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracking vehicle.
+Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
+We follow the prediction time allocation as in~\cite{xu2017end} that the historical time-span is 3 seconds (corresponds to 15 frames with 5 Hz frame rate in the SYNTHIA dataset).
+However, in contrast with~\cite{xu2017end} where only the next 1/3rd of a second is predicted, we strive to predict the next 1.6 second's future trajectory as mentioned previously that it's the reaction time accident reconstruction specialists commonly used~\cite{mcgehee2000driver}.
+
+We follow the traditional paradigm for visual tracking to collect target's bounding box: $[x, y, w, h]$ of each frame.
+Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
+The train/valid/test are split as 80\%/10\%/10\% of the total tracklets and the total numbers are shown in Tab.~\ref{tab:dataset_statistics}.
+We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
+Some sample frames with semantic labels and depth information is shown in Fig.~\ref{fig:dataset}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
-        \caption{ {\small Examples of collected dataset for car trajectory prediction.
-From top to bottom: RGB, semantic labeling, depth maps for three continuous frames of two dynamic light conditions.}}
+        \caption{Examples of collected dataset for vehicle trajectory prediction.
+From top to bottom: RGB, semantic labeling, depth maps for three continuous frames under two dynamic light conditions.}
         \label{fig:dataset}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Implementations}\label{sec:Implementations}
+\subsection{Implementation Details}\label{sec:Implementations}
 
@@
 
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
+        \caption{Instance association can help to disambiguate the false positive by enforcing temporal consistency requirement.
+Due to the high recall requirement for vehicle detection, there could be correspondingly higher false positive rate (\emph{e.g.}, double detection of red boxed in the far left).
+Instance association across multiple frames will discard the spurious detection.}
+        \label{fig:Instance_association}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Instance tracking}
+
+To associate traffic participants across different frames (\emph{i.e.}, instance tracking), we creatively combine detecting with tracking.
+The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
+However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
+In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
+Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
+For this task, we adopt the real-time scale adaptive tracker fDSST~\cite{danelljan2017discriminative} that achieves 50 FPS with scale estimation.
+For every newly detected target whose POR is larger than the predefined threshold of 0.2\%, we initiate the tracker with a unique target ID.
+The tracker's target model is updated every time when there is a detection whose jaccard overlap is larger than 0.3.
+We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergoing rapid out of plane rotations.
+In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{c.f.} Fig.~\ref{fig:Instance_association}).
+The target's tracker will terminate under either of the following two conditions: if the target's POR is smaller than 0.1\% (\emph{i.e.}, the vehicle is too far way from the host car); or if there are more than 5 frames of detection absence  (\emph{i.e.}, the target could be one false positive detection from the vehicle detector).
+
+\begin{table}\centering
+\ra{1.}
+%\begin{tabular}{@{}llll@{}}\toprule
+
+\begin{tabu}{@{}llll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-4}
+                & \#train & \#valid & \#test\\
+ \hline
+
+ tracklets      &  10400    &  1300    & 1280 \\
+ \hline
+ car detection  &   7832     & 976     & 986 \\
+ \hline
+ semantic segmentation  &  7841  & 977  & 987 \\
+ \hline
+ \end{tabu}
+%\end{tabular}
+\caption{Dataset statistics}
+\label{tab:dataset_statistics}
+\end{table}
+
+\subsubsection{Trajectory prediction}
 \begin{table*}\centering
@@
 %\end{tabular}
-\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
+\caption{
+Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
+It can be seen that:
+(1) both meta-architectures are robust to the cut-off confident thresholds.
+(2) SSD is more competitive in the collected dataset when targets of interest are large.
+}
 \label{tab:ssd_fasterrcnn}
@@
 
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
-        \caption{ {\small TODO: Instance association caption goes here.}}
-        \label{fig:Instance_association}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table}\centering
-\ra{1.}
-%\begin{tabular}{@{}llll@{}}\toprule
-
-\begin{tabu}{@{}llll@{}}\toprule
-[-1pt] \tabucline[1pt]{1-4}
-                & \#train & \#valid & \#test\\
- \hline
-
- tracklets      &  10400    &  1300    & 1280 \\
- \hline
- car detection  &   7832     & 976     & 986 \\
- \hline
- semantic segmentation  &  7841  & 977  & 987 \\
- \hline
- \end{tabu}
-%\end{tabular}
-\caption{Dataset statistics}
-\label{tab:dataset_statistics}
-\end{table}
-
-\subsubsection{Instance tracking}
-
-To associate traffic participants across different frames (\emph{i.e.}, instance tracking), we creatively combine detecting with tracking.
-The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
-However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
-In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
-Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
-For this task, we adopt the real-time scale adaptive tracker fDSST~\cite{danelljan2017discriminative} that achieves 50 FPS with scale estimation.
-
-For every newly detected target whose POR is larger than the predefined threshold of 0.2\%, we initiate the tracker with a unique target ID.
-The tracker's target model is updated every time when there is a detection whose jaccard overlap is larger than 0.3.
-We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergoing rapid out of plane rotations.
-In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{e.f.} Fig.~\ref{fig:Instance_association}).
-The target's tracker will terminate under either of the following two conditions: if the target's POR is smaller than 0.1\% (\emph{i.e.}, the vehicle is too far way from the host car); or if there are more than 5 frames of detection absence  (\emph{i.e.}, the target could be one false positive detection from the vehicle detector).
-
-%\subsubsection{Semantic segmentation}
-%We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.
-
-\subsubsection{Trajectory prediction}
-
-We compare two temporal models based on LSTM cells for predicting the car trajectory.
-
+For the task of sequential prediction, both FtF and FtS share the same base network structure:
+a 3-layer recurrent net with 100, 300, 300 LSTM cells.
+For SEG-LSTM, since the focus of the scene context is high way driving, auxiliary information is the scene semantics with only ``car" and ``road".
+The input semantics are one-hot encoded in the dimension of $95\times160\times2$.
+The CNN for learning high level semantics is composed of four convolutional blocks.
+Each block includes a convolutional layer, a ReLU activation layer, a maxpooling layer and a dropout layer (as we have observed overfitting during network training).
+Each convolutional layer has four channels with kernel of size 3.
 We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus.
@@
     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
-    \caption{\small{Precision plot for 2D}}
+    \caption{\small{Precision plot for 2D (pixel as x-axis)}}
     \end{subfigure}%
@@
         \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
-        \caption{\small{Success plot 2D}}
+        \caption{\small{Success plot 2D (IOU as x-axis)}}
     \end{subfigure}
@@
      \begin{subfigure}[c]{0.4\textwidth}
-     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20.png}
-    \caption{\small{Precision plot for 3D}}
+     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20cm.png}
+    \caption{\small{Precision plot for 3D (centimeter as x-axis)}}
     \end{subfigure}%
@@
         \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
-        \caption{\small{Success plot 3D}}
+        \caption{\small{Success plot 3D (IOU as x-axis)}}
     \end{subfigure}
-\caption{Precision plot and success plot of the state-of-the-art, 2D, and 3D(TODO).
+\caption{2D and 3D space precision plot and success plot .
 }
-\label{fig:precision_plot_and_success_plot_OBT100}
+\label{fig:precision_plot_and_success_plot}
 \end{figure*}
@@
         \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
-        \caption{ {\small TODO: evaluation caption goes here.}}
+        \caption{ The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.
+        }
         \label{fig:evaluation}
@@
 
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=0.95\textwidth]{figures/prediction.pdf}
+        \caption{
+        The prediction results in SYNTHIA dataset. {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
+                The results using SEG-LSTM network show that by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the predicted trajectory from the recurrent net within the most plausible path.
+Top: SEG-LSTM can help detecting neighbouring vehicles and restricts the viable path outside the space occupied by other vehicles.
+Bottom:  SEG-LSTM confines the possible car trajectories along the space above road.
+                }
+        \label{fig:final}
+\end{figure*}
+
+\vspace{\baselineskip}
+\noindent \textbf{Baseline: Kalman filter}, also known as linear quadratic estimation, is a popular technique for estimating the state of a system~\cite{Thrun2016}.
+For the task of trajectory prediction, Kalman filters estimates a continuous state and gives a uni-modal distribution.
+The Kalman filter represents all distributions of the Gaussians and iterates two states: (1) measurement updates; (2) motion updates.
+In the baseline, we set
+the initial uncertainly covariance as 1e4, measurement noise and motion noise are all set with unit value.
+
+%We evaluation the trajectory both in 2D space (using pixel as unit distance) and 3D space (using meter as unit distance) as shown in Fig.~\ref{fig:evaluation}.
+
 \noindent \textbf{2D Evaluation Methodology:}
 Following the evaluation strategy  of~\cite{wu2013online}, all trajectories are compared using two measures: precision and success.
-Precision is measured as the distance between the centres of the ground truth bounding box and the corresponding tracker generated bounding box.
+Precision is measured as the distance between the centers of the ground truth bounding box and the corresponding tracker generated bounding box.
 The precision plot shows the percentage of tracker bounding boxed within a given threshold distance in pixels of the ground truth.
@@
 The success plot shows the percentage of tracker bounding boxes whose overlap score is larger than a given threshold and the trackers are ranked according to the Area Under Curve (\emph{AUC}) criteria.
-% All sequences are evaluated using One-Pass Evaluation (OPE) as in~\cite{wu2013online}.
+% The 2D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(top) and Tab.~\ref{table_baseline_2d}.
 
@@
 \noindent \textbf{3D Evaluation Methodology:} Given depth map and the parameter of camera focal lens, we can formalize the problem into a 3D occupancy grid estimation.
-The real world coordinates $[x_r, y_r, w_r, h_r] $can be obtained according to Eq.~\ref{eq:focal_length_1}~\ref{eq:focal_length_2}.
+The real world coordinates $[x_r, y_r, w_r, h_r]$ can be obtained according to Eq.~\ref{eq:focal_length_1}~\ref{eq:focal_length_2}.
 The 3D jaccard index can be similarly formalized as the volume intersection over union: $\frac{V_g \cap V_p}{V_g \cup V_p}$, where $V_g, V_p$ are the ground truth and predicted space occupancy.
 3D center error correspondingly is defined as the mean square root in 3D space.
+%The 3D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(bottom) and Tab.~\ref{table_baseline_3d}.
 
 \vspace{\baselineskip}
-\noindent \textbf{Baseline: Kalman filter}, also known as linear quadratic estimation, is a popular technique for estimating the state of a system~\cite{Thrun2016}.
-For the task of trajectory prediction, Kalman filters estimate a continuous state and gives a uni-modal distribution.
-The Kalman filter represents all distributions of the Gaussians and iterates two states: (1) measurement updates; (2) motion updates.
-In the baseline, we set
-the initial uncertainly covariance as 1e4, measurement noise and motion noise are all set unit value.
-
-\vspace{\baselineskip}
-\noindent \textbf{Learning with auxiliary information}
+\noindent \textbf{Learning with auxiliary information:}
+ The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter.
+Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinate.
+ The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
+ Fig.~\ref{fig:final} shows the advantage of using SEG-LSTM: by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the recurrent net to output the most plausible path for vehicles and avoid collision with neighboring vehicles.
 
@@
     \caption{ {\small
-    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better). Mean coverage is the average 
+    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better).
      }
-          } \label{table_baseline2}
+          } \label{table_baseline_2d}
 \end{table}
@@
     \caption{ {\small
-    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better). Mean coverage is the average
+    Results of 3D performance evaluation on mean coverage (higher is better) and center error (lower is better).
      }
-          } \label{table_baseline2}
+          } \label{table_baseline_3d}
 \end{table}
@@
 In this paper, mimicking the human driver reaction time, we advocate to solve the problem of predicting traffic participants future trajectory given historical information.
-We propose a two staged system incorporating various visual inputs with a temporally recurrent neural networks.
+We propose a two-staged system incorporating various visual inputs with a temporally recurrent neural network.
 The recurrent network takes semantic information as an auxiliary input and further improve the predicting accuracy.
@@
 
-\section*{Details of the Code}
-\footnote{The code will be made public upon publication.}
+%\section*{Details of the Code}
+%\footnote{The code will be made public upon publication.}
 

### 2018-01-19 code_base/config/synthia_car_trajectory.py
for configuration file

@@ -37,7 +37,7 @@ formatting_ground_truth_sequence_car_trajectory = True
 draw_seq                                = 'SYNTHIA-SEQS-06-NIGHT'   # which sequence to draw, need to set the above two flags to False
 
 # Model
-model_name                   = 'DropoutCNN_LSTM_To_FC'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
+model_name                   = 'LSTM_ManyToMany'       # Model to use ['LSTM_ManyToMany', 'LSTM_To_FC', 'CNN_LSTM_To_FC', 'DropoutCNN_LSTM_To_FC']
 debug                        = False
 im_size                      = (760, 1280)
 resize_train                 = (760, 1280)      # Resize the image during training (Height, Width) or None
@@ -119,7 +119,7 @@ optimizer                    = 'sgd'      # LBFGS','adam','rmsprop','sgd'
 learning_rate                = 0.01          # Training learning rate
 momentum                     = 0.9
 load_trained_model           = True
-train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Wed, 15 Nov 2017-11-15 14:50:59_DropoutCNN_LSTM_To_FC_Shuffle/Epoch:303_net_Coverage:0.7755_Center:12.99_CoverageR:0.4895_CenterR:0.33.PTH'
+train_model_path             = '/home/wzn/PycharmProjects/autonomous_driving/Experiments/car_trajectory_prediction/SYNTHIA-SEQS-01_Wed, 15 Nov 2017-11-15 18:00:00_LSTM_ManyToMany_Shuffle/Epoch:54_net_Coverage:0.6730_Center:22.88_CoverageR:0.3607_CenterR:0.69.PTH'
 #### LSTM training variables #################
 # LSTM_ManyToMany
 lstm_input_dims               = [6, 100, 300]    # [layer1_input_dim, layer2_input_dim,...]  layer1_input_dim:[x,y,w,h, d_min, d_max]

### 2018-01-19 code_base/models/PyTorch_model_factory.py

@@ -16,6 +16,7 @@ import numpy as np
 from matplotlib import pyplot as plt
 import os
 import sys
+import pickle
 import json
 
 
@@ -343,6 +344,8 @@ class Model_Factory_LSTM():
         errCenter_realworld = []
         iou_3d = []
 
+        # for experiment: output predicted trajectory
+        predicted_trajectory = []
         for i, (sementic, input_trajectory, target_trajectory) in enumerate(valid_loader):
             # print(i)
             sementic, input_trajectory, target_trajectory = Variable(sementic.cuda(async=True)), \
@@ -354,6 +357,9 @@ class Model_Factory_LSTM():
                 input = tuple([input_trajectory])
 
             output_trajectory = self.net(*input, future=cf.lstm_predict_frame)[-1]
+            # for experiment: output predicted trajectory
+            predicted_trajectory.append(output_trajectory.data.cpu().numpy())
+
             # cal loss
             loss = self.crit(output_trajectory, target_trajectory)
             valid_losses.append(loss.data[0])
@@ -369,6 +375,10 @@ class Model_Factory_LSTM():
             iou_3d.append(evalua_values[7])
             # output_trajectories.append(output)
             # target_trajectories.append(target_trajectory)
+        # for experiment: output predicted trajectory
+        path = '/media/samsumg_1tb/cvpr_trajectory_data_final/FrameToFrame_Shuffle/predicted_trajectory.npy'
+        np.save(path, np.array(predicted_trajectory))
+
 
         # loss mean
         track_plot = {}
@@ -376,6 +386,7 @@ class Model_Factory_LSTM():
         track_plot['iou_2d'] = iou_2d
         track_plot['errCenter_realworld'] = errCenter_realworld
         track_plot['iou_3d'] = iou_3d
+
 
         self.loss = np.array(valid_losses).mean()
         # print('Valid Loss', epoch, self.loss)
@@ -402,7 +413,9 @@ class Model_Factory_LSTM():
             model_checkpoint = 'Epoch:%2d_net_Coverage:%.4f_Center:%.2f_CoverageR:%.4f_CenterR:%.2f.PTH' % \
                                (epoch, aveErrCoverage, aveErrCenter, aveErrCoverage_realworld, aveErrCenter_realworld)
             if epoch == cf.n_epochs:
-                np.save(os.path.join(self.exp_dir, 'valid'), track_plot)
[…]

### 2018-01-19 code_base/tools/PyTorch_data_generator.py

@@ -231,6 +231,9 @@ class DataGenerator_Synthia_car_trajectory():
             print('Loading data')
             train_data, valid_data, test_data, self.data_mean, self.data_std, train_img_list, valid_img_list, test_img_list = prepare_data_image_list(cf)
 
+            # # for experiment
+            # test_data[693,:,:]
+            # test_img_list[693]
             # deal images and relocate train_img_list & valid_img_list & test_img_list
             self.root_dir = '/'.join(cf.dataset_path[0].split('/')[:-1])
 
@@ -245,7 +248,6 @@ class DataGenerator_Synthia_car_trajectory():
                                            pin_memory=True)
             self.test_loader = DataLoader(test_dataset, batch_size=cf.batch_size_test, num_workers=cf.workers,
                                           pin_memory=True)
-
 
 class BB_ImageDataGenerator_Synthia(Dataset):
     def __init__(self, cf, trajectory_data, img_list, crop=True, flip=True):

### 2018-01-19 code_base/models/PyTorch_model_factory.py
merge with wzn temporal model

@@ -11,14 +11,9 @@ from torch.nn import functional as F
 from torchvision.utils import save_image
 from code_base.tools.logger import Logger
 from datetime import datetime
-import numpy as np
-
-import numpy as np
 from matplotlib import pyplot as plt
 import os
 import sys
-
-import json
 import numpy as np
 
 

### 2018-01-19 code_base/result_visualisation.py

@@ -1,0 +1,41 @@
+import numpy as np
+import os
+from matplotlib.patches import Rectangle
+import matplotlib.pyplot as plt
+from PIL import Image
+
+
+def main():
+    data_array = np.load('/media/samsumg_1tb/synthia/prepared_data_shuffle.npy')
+    test_data_array = data_array[2]
+    data_mean = data_array[3]
+    data_std = data_array[4]
+    test_data_array = (test_data_array * data_std) + data_mean
+
+    item_data = test_data_array[693]
+    img_path ='/media/samsumg_1tb/synthia/Final_VISUAL'
+    img_list = sorted(os.listdir(img_path))
+
+    fig = plt.figure(1)
+    fig.clear()
+    tracking_figure_axes = fig.add_subplot(111, aspect='equal')
+    #tracking_figure_axes.set_title('Green: detecion; Red: tracking. Image: %s' % img_name)
+
+    for i,item in enumerate(item_data[:10]):
+        rect = item[:4]
+        im = Image.open(os.path.join(img_path, img_list[i]))
+        tracking_figure_axes.imshow(im)
+        # Create a Rectangle patch
+        tracking_rect = Rectangle(
+            xy=(rect[1], rect[0]),
+            width=rect[3],
+            height=rect[2],
+            facecolor='none',
+            edgecolor='r',
+        )
+        tracking_figure_axes.add_patch(tracking_rect)
+        #tracking_figure_axes.annotate(str(car_idx), xy=(pos.left(), pos.top() + 20), color='red')
+        plt.waitforbuttonpress(0.01)
+
+if __name__ == "__main__":
+    main()

### 2018-01-19 code_base/tools/PyTorch_data_generator_car_trajectory.py

@@ -134,7 +134,7 @@ class Dataset_Generators_Synthia_Car_trajectory():
         self.std = cf.rgb_std
         # Load training set
         print('\n > Loading training set, currently we have only training set')
-        if not cf. video_sequence_prediction:
+        if not cf.video_sequence_prediction:
             dataloaders_single = {x: ImageDataGenerator_Synthia_Car_trajectory(
                 cf=cf,
                 transform=T.Compose([

### 2018-01-19 code_base/tools/bmvc_2014_pami_2014_fDSST.py

@@ -1,0 +1,717 @@
+# coding=utf-8
+"""
+Di Wu's re-implemenation of the Fast Discriminative Scale Space Tracker (fDSST) [1],
+which is an extension of the VOT2014 winning DSST tracker [2].
+The code provided by [3] is used for computing the HOG features.
+
+
+[1]	Martin Danelljan, Gustav Fahad Khan, Michael Felsberg.
+	Discriminative Scale Space Tracking.
+	Transactions on Pattern Analysis and Machine Intelligence (TPAMI).
+
+[2] Martin Danelljan, Gustav Fahad Shahbaz Khan and Michael Felsberg.
+    "Accurate Scale Estimation for Robust Visual Tracking".
+    Proceedings of the British Machine Vision Conference (BMVC), 2014.
+
+[3] Piotr Doller
+    "Piotr抯 Image and Video Matlab Toolbox (PMT)."
+    http://vision.ucsd.edu/~pdollar/toolbox/doc/index.html.
+
+Contact:
+Di Wu
+http://stevenwudi.github.io/
+email: stevenwudi@gmail.com  2017/08/01
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.misc import imresize
+import cv2
+import os
+import h5py
+import time
+import matlab.engine
+import matlab
+
+
+class bmvc_2014_pami_2014_fDSST:
+    def __init__(self,
+                 padding=2.0,
+                 output_sigma_factor=float(1/16.),
+                 scale_sigma_factor=float(1/16.),
+                 lambda_value=1e-2,
+                 interp_factor=0.025,
+                 num_compressed_dim=18,
+                 refinement_iterations=1,
+                 translation_model_max_area=np.inf,
+                 interpolate_response=1,
+                 resize_factor=1,
+                 number_of_scales=17,
+                 number_of_interp_scales=33.,
+                 scale_model_factor=1.0,
+                 scale_step=1.02,
+                 scale_model_max_area=512,
+                 s_num_compressed_dim='MAX',
+                 feature_ratio=int(4.0),
+                 compressed_features='hog_gray',
+                 non_compressed_features=None,
+                 kernel='linear',
+                 w2c_file_path='trackers/w2crs.mat',
+                 visualisation=0,
+                 matlab_legacy=True,
+                 matlab_eng=None,
+                 ):
+        """
+        :param padding: extra area surrounding the target
+        :param output_sigma_factor: standard deviation for the desired translation filter output
[…]

### 2018-01-19 code_base/tools/gt_acquisition.py

@@ -14,6 +14,7 @@ from scipy.misc import imresize
 from skimage.filters import threshold_otsu
 from skimage.filters import threshold_yen
 from skimage.filters import threshold_li
+import collections
 
 
 def convert_key_to_string(car_tracking_dict):
@@ -648,6 +649,17 @@ def get_sequence_car_tracking(DG, cf, sequence_name, show_set='train'):
     """
     print("Processing sequence: "+cf.dataset_path)
     train_set = DG.dataloader[show_set]
+    if cf.tracker == 'fDSST':
+        import time
+        from code_base.tools.bmvc_2014_pami_2014_fDSST import bmvc_2014_pami_2014_fDSST
+        print('starting matlab engine...')
+        start_time = time.time()
+        import matlab.engine
+        import matlab
+        matlab_eng = matlab.engine.start_matlab("-nojvm -nodisplay -nosplash")
+        matlab_eng.addpath('./tools/piotr_hog_matlab')
+        total_time = time.time() - start_time
+        print('matlab engine started, used %.2f second'%(total_time))
 
     car_detection_path_list = cf.savepath.split('/')
     car_detection_path_list[-2] = 'car_detection'  # this is a hard coded script, sorry
@@ -674,19 +686,24 @@ def get_sequence_car_tracking(DG, cf, sequence_name, show_set='train'):
         classes = classes_torch.numpy().astype('uint8')
         depth = depth_torch.numpy()
         img_name = sample_batched['img_name'][0]  # because for GT construction, the batch size is always 1
-        car_tracking_dict = get_car_tracking_box(cf, input_image, depth, car_tracking_dict, img_name, car_detect_dict)
+        if cf.tracker == 'fDSST':
+            car_tracking_dict = get_car_tracking_box(cf, input_image, depth, car_tracking_dict, img_name,
+                                                     car_detect_dict, matlab_eng, bmvc_2014_pami_2014_fDSST)
+        else:
+            car_tracking_dict = get_car_tracking_box(cf, input_image, depth, car_tracking_dict, img_name, car_detect_dict)
 
     # we sort the dict by keys
-    car_tracking_dict_sorted = collections.OrderedDict(sorted(car_tracking_dict.items()))
-    json_file_path = os.path.join(cf.savepath, sequence_name+'.json')
-    with open(json_file_path, 'w') as fp:
-        json.dump(car_tracking_dict_sorted, fp, indent=4)
-    print('Saving: '+json_file_path)
+    for key in car_tracking_dict.keys():
[…]

### 2018-01-19 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

@@
 \usepackage{amssymb}
-
 % Include other packages here, before hyperref.
@@
 \section{Introduction}
-The reviewers generally acknowledge the extensibility of our framework, well evaluated experiments, and the novelty of introducing ergodic state to perform segmentation and recognition within the same framework.
-Due to space constraints, we address only the major criticisms below.
+We would first like to thank the reviewers for your valuable feedback which helped us to improve the analysis of the proposed method and the overall presentation of the paper. 
+Due to space constraints with significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{http://www.texample.net/tikz/resources/}{new version of the paper}.
+we address only the major criticisms below.
+
+\subsection{Common}
+\noindent \textbf{1) Unlike stated in the paper, vehicle tracking in images has been studied for years.
+There are summary papers (e.g.
+VEHICLE DETECTION AND TRACKING TECHNIQUES: A CONCISE REVIEW Raad Ahmed Hadi1,2 , Ghazali Sulong1 and Loay Edwar George, SIPIJ).
+There is no mention of prior art.}
+
+\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}
+
+\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
+center of detected bounding box).}
+\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+
+\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
+\noindent \textbf{It is not clear if the dataset is released with the paper.}
+
+Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation.
+To our knowledge, our paper is the first attempt to utilize \textbf{\emph{continuous video streams}} for the prediction problems.
+We would like to release publicly-available prediction challenge based on Synthia to spur future research upon paper publication.
+\subsection{R1}
+
+\noindent \textbf{They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
+
+\noindent \textbf{3) 3 very similar LSTMs with different input}
+
+\noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}
+
+\noindent \textbf{There are a number of inaccuracies}
+\noindent \textbf{e.g. line 044, where the authors state that automated driving models are either neural networks or controllers with if-then-else rules}
+\noindent \textbf{or line 304, that states that the closest related work to their tracking is an ego-motion regression by Xu,Gao and Darrell}
+\noindent \textbf{Line 471 calls Synthia images photo-realistic.}
+
+\noindent \textbf{The actual contributions, and evaluation could be clearer. It took some time to understand the different metrics for detection and tracking as they are supposed to be fused.}
+
+\noindent \textbf{The actual contribution is not significant enough and could be described more clearly.}
 
@@
 
-\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
-Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation.
-To our knowledge, our paper is the first attempt to utilize continuous video streams for the prediction problems.
-are required for the purpose of car trajectory prediction. We
-collect car trajectory prediction dataset based on the SYN-
-THIA [29] dataset.
+\noindent \textbf{SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and “final disp. Error” What was the justification for the metrics the authors chose?}
 
-Where are comparisons with other activity forecasting/trajectory
-prediction works?
-I think the authors should reimplement SocialLSTM for 2D data (Stanford
-UAV dataset seems to be a 2D standard prediction task -- just throw
-away images and just use the xy plane coordinates, e.g. center of
-detected bounding box).
-SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and
-“final disp. Error”
-What was the justification for the metrics the authors chose?
-In the SocialLSTM paper’s Related Work section, there are about 20
-sources that focus on “Activity forecasting”
-The details about the fusion of “location” and “semantic” information into
-the LSTM hidden state seemed missing (was a bit vague). A figure of the
-architecture of the SEG-LSTM would go a long way in clarifying this (or
-are the authors using Xu et al.'s "End-to-end Learning of Driving Models
-from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's
-group?).
-How is this more than just an engineering pipeline, combining tracking
-(distilling bounding boxes to coordinates), and then adding an LSTM?
-SocialLSTM already did the second part in principle.
-I was a bit confused about why the “tracking-by-detection” framework
-was novel -- how is it different from “Tracking-learning-detection” (TLD),
-from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?
-Why are scene semantics privileged (which you also call “auxiliary”)
-information?
-If the pipeline relies on fusing the “location” and “semantic” stream, if
-privileged information is missing at test time, then won’t the pipeline
-break? (privileged information is usually present at train time, but
-absent at test time).
-Can multiple objects be tracked at once, or just one? The video in the
-supplementary material only showed one object being tracked. What was
-the average number of objects in each SYNTHIA scene frame?
-The focus of the paper seems a bit unclear: apparently, the goal is to
-“predict car’s future odometry given previous egomotion visual input”.
-But the paper is about prediction of other vehicles’ trajectories, not
-about predicting one’s own car odometry (which is different).
-Odometry: “Odometry is the use of motion sensors to determine the
-robot's change in position relative to some known position” (not other
-robots' positions) https://groups.csail.mit.edu/drl/courses/cs54-
-2001s/odometry.html
-“Visual Odometry -- Estimating the motion of a camera in real time using
-sequential images (i.e., egomotion)”
-\verb+http://www.cs.toronto.edu/~urtasun/courses/CSC2541/03_odometry.pdf+
-(but we are not trying to estimate the motion of a camera-mounted
-vehicle here).
-I felt like the detection/tracking theme slightly bogs down the main focus
-of prediction in the paper. I think refocusing it on prediction would
-strengthen the argument.
-Line 124 - The authors discuss a "lack of proper metrics for evaluating
-the temporal prediction result." How are the current metrics poorly
-suited to the task? What would be better?
+\noindent \textbf{Line 124 - The authors discuss a "lack of proper metrics for evaluating the temporal prediction result." How are the current metrics poorly suited to the task? What would be better?}
 
-\subsection{Old}
+\noindent \textbf{In the SocialLSTM paper’s Related Work section, there are about 20 sources that focus on “Activity forecasting”}
+
+\noindent \textbf{The details about the fusion of “location” and “semantic” information into the LSTM hidden state seemed missing (was a bit vague).
+A figure of the architecture of the SEG-LSTM would go a long way in clarifying this (or are the authors using Xu et al.'s "End-to-end Learning of Driving Models from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's group?).}
+
+\noindent \textbf{How is this more than just an engineering pipeline, combining tracking (distilling bounding boxes to coordinates), and then adding an LSTM?
+SocialLSTM already did the second part in principle.}
+
+\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
+Kalal, K.
+Mikolajczyk, and J.
+Matas.
+In TPAMI 2012?}
+
+\noindent \textbf{Why are scene semantics privileged (which you also call “auxiliary”) information?
+If the pipeline relies on fusing the “location” and “semantic” stream, if privileged information is missing at test time, then won’t the pipeline break?
+(privileged information is usually present at train time, but absent at test time).}
+
+ \noindent \textbf{Can multiple objects be tracked at once, or just one?
+The video in the supplementary material only showed one object being tracked.
+What was the average number of objects in each SYNTHIA scene frame?}
+
+ \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to “predict car’s future odometry given previous egomotion visual input”.
+But the paper is about prediction of other vehicles’ trajectories, not about predicting one’s own car odometry (which is different).}
+
+\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}
+
+\subsection{R3}
+\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
+\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here.
+In general a lot of methodology detail is actually in section 4 (implementation details).
+Maybe consider reorganizing a little bit.}
+
+\noindent \textbf{In a real car accurate depth information might not be available.
+Also, tracking and semantic segmentation results in the real world will probably be noisier than for synthetic data.
+Experiments on real data would make the results much stronger.}
+
+\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
+
+\noindent \textbf{Do you think the results you obtained with the Synthia data will transfer to real-world data?}
+
+\noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with ‘real’ physics and photo-realism similar to Synthia.
+It would be interesting to implement this system and evaluate ‘real-world’ performance.}
+
+\subsection{Original requirement}
 After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
@@
 
-%------------------------------------------------------------------------
-\section{Formatting your Response}
-
-{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}
-
-All text must be in a two-column format. The total allowable width of the text
-area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
-(0.8 cm) space between them. The top margin should begin
-1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
-1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
-11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
-bottom edge of the page.
-
-Please number all of your sections and any displayed equations.  It is important
-for readers to be able to refer to any particular equation.
-
-Wherever Times is specified, Times Roman may also be used.  Main text should be
-in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
-Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
-cm).  Figure and table captions should be 9-point Roman type as in
-Figure~\ref{fig:onecol}.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced,
-at the end of your response. When referenced in the text, enclose the citation
-number in square brackets, for example~\cite{Authors14}.  Where appropriate,
-include the name(s) of editors of referenced books.
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-Please ensure that any point you wish to make is resolvable in a printed copy of the response.
-Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
-Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
 {\small

### 2018-01-19 code_base/Synthia_car_trajectory.py
conflic

@@ -1,5 +1,4 @@
 import argparse
-import os
 import sys
 import os
 os.environ['CUDA_VISIBLE_DEVICES'] = '2'

### 2018-01-22 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
paper writing: typos by R3 corrected

@@
 
-\noindent \textbf{SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and “final disp. Error” What was the justification for the metrics the authors chose?}
+\noindent \textbf{SocialLSTM used ``Avg. disp. Error", ``Avg. non-linear disp. error" , and ``final disp. Error" What was the justification for the metrics the authors chose?}
+
+\noindent The ``Average displacement error" is
 
@@
 
-\subsection{Original requirement}
-After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
-Please follow the steps and style guidelines outlined below for submitting your author response.
-
-Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers.
-It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers.
-You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.
-
-The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.
-
-%-------------------------------------------------------------------------
-
-Author responses must be no longer than 1 page in length including any references and figures.
-Overlength responses will simply not be reviewed.
-This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-
 {\small

### 2018-01-22 paper/cvpr2018/cvpr2018_3790.tex
paper writing: typos by R3 corrected

@@
 Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
-In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
+In this paper, we raise the question of ``can we predict the car's future odometry given previous egomotion visual input?".
 The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
@@
 We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
- We also show the effectiveness of using privileged information (e.g., scene semantics) further boost the prediction accuracy across diverse traffic conditions.
+ We also show the effectiveness of using privileged information (e.g., scene semantics) to further boost the prediction accuracy across diverse traffic conditions.
 \end{abstract}
@@
 We need to know not just where other cars are, as in the localization case, but also how fast they are moving in order to avoid collisions.
-For a human driver, reaction time is a crucial factor that includes recognizing the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake).
+For a human driver, reaction time is a crucial factor that includes recognizing the light has changed, deciding to continue or brake, and whether to stop engaging the brake (remove foot from accelerator and apply brake).
 Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
-Therefore, the ability to predict traffic participants' \emph{future} trajectories will greatly benefits the mediated perception approach's driving policy decision making.
+Therefore, the ability to predict traffic participants' \emph{future} trajectories will greatly benefit the mediated perception approach's driving policy decision making.
 
@@
 Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
-In addition, scene parsing results contain quite some spurious information.
+In addition, the scene parsing results contain quite some spurious information.
 Existing methods for scene parsing also mainly focus on static images.
-However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by sequence of input frames instead of simply one static frame.
+However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by a sequence of input frames instead of simply one static frame.
 Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.
@@
 Vehicle trajectory prediction is also very related to visual tracking.
-In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
+In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
 However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks).
@@
 %Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
-KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks.
+KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks.
 However, a limited 430 labelled images are provided for semantic segmentation.
@@
 \end{equation}
-where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}.
+where the traffic participants $p$ can be vehicles, cyclists, pedestrians, \emph{etc}.
 In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on.
@@
 \end{align}
-where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ is as a close approximation.
+where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ as a close approximation.
 
@@
 
-For predicting vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}.
+For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}.
 The first two models take sequential 3D occupancy as input.
@@
 \noindent \textbf{SEG-LSTM model:}
- take advantages of scene semantics from  historical frames as auxiliary information $A$.
+ takes advantages of scene semantics from  historical frames as auxiliary information $A$.
 The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information.
@@
   }
-\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with step size 1:
+\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with stepsize 1:
 {\bindent
@@
 Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
-We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
+We collect a car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
 SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
@@
 The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset.
-We especially concern about the cars that are relatively close to the driver.
+We are especially concerned about the cars that are relatively close to the driver.
 In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
 As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
-Since depth information is also provided alongside in the SYNTHIA dataset, we back-projecting the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracking vehicle.
+Since depth information is also provided alongside in the SYNTHIA dataset, we back-project the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracked vehicle.
 Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
@@
 
-As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small objects, it's very competitive for detecting larger objects.
-In this paper, we concerns mostly about cars that are close to the driver.
+As is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small objects, it's very competitive for detecting larger objects.
+In this paper, we are mostly concerned about cars that are close to the driver.
 Hence, given 0.1\% POR as the the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
@@
 The tracker's target model is updated every time when there is a detection whose jaccard overlap is larger than 0.3.
-We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergoing rapid out of plane rotations.
+We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergo rapid out of plane rotations.
 In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{c.f.} Fig.~\ref{fig:Instance_association}).
@@
 a 3-layer recurrent net with 100, 300, 300 LSTM cells.
-For SEG-LSTM, since the focus of the scene context is high way driving, auxiliary information is the scene semantics with only ``car" and ``road".
+For SEG-LSTM, since the focus of the scene context is high-way driving, auxiliary information is the scene semantics with only ``car" and ``road".
 The input semantics are one-hot encoded in the dimension of $95\times160\times2$.

### 2018-01-24 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
paper writing. TODO: writing exp section with social lstm.

@@
 
+We have rewritten our contributions in Section 1 and make our contributions more clearly.
+
+We have restructured our methodology in section 3 and further explain the intuition behind the chosen architecture.
+
 \subsection{Common}
+
+\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
+center of detected bounding box).}
+
+\noindent We have re-implemented Social-LSTM for 2D data. blablabla details...
+
 \noindent \textbf{1) Unlike stated in the paper, vehicle tracking in images has been studied for years.
@@
 There is no mention of prior art.}
+\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}
+\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
 
-\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}
-
-\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
-center of detected bounding box).}
-\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+We have restructured our related works. Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``RNN for sequence prediction" part.
 
@@
 
-Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation.
+\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+
+\noindent Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation.
 To our knowledge, our paper is the first attempt to utilize \textbf{\emph{continuous video streams}} for the prediction problems.
 We would like to release publicly-available prediction challenge based on Synthia to spur future research upon paper publication.
-\subsection{R1}
 
+\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
+Kalal, K.
+Mikolajczyk, and J.
+Matas.
+In TPAMI 2012?}
+\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
 \noindent \textbf{They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
 
+\noindent  Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking.
+In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
+Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations.
+This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
+In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
+Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting.
+Hence the tracker is served solely as instance associator for the traffic participant.
+
+\subsection{R1}
 \noindent \textbf{3) 3 very similar LSTMs with different input}
-
 \noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}
 
-\noindent \textbf{There are a number of inaccuracies}
-\noindent \textbf{e.g. line 044, where the authors state that automated driving models are either neural networks or controllers with if-then-else rules}
-\noindent \textbf{or line 304, that states that the closest related work to their tracking is an ego-motion regression by Xu,Gao and Darrell}
-\noindent \textbf{Line 471 calls Synthia images photo-realistic.}
-
-\noindent \textbf{The actual contributions, and evaluation could be clearer. It took some time to understand the different metrics for detection and tracking as they are supposed to be fused.}
-
-\noindent \textbf{The actual contribution is not significant enough and could be described more clearly.}
+\noindent Explain the intuition....
 
@@
 
-\noindent The ``Average displacement error" is
+\noindent The ``average displacement error" is essentially the same as the ``center error" in Tab.3 of our paper and the subtle difference is that the former is in unit space and the latter is in pixel space.
+Similarly ``Final displacement error" is the last frame's ``center error" is unit space.
+``average non-linear displacement error"
 
@@
 SocialLSTM already did the second part in principle.}
-
-\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
-Kalal, K.
-Mikolajczyk, and J.
-Matas.
-In TPAMI 2012?}
 
@@
 
+\noindent We thank the reviewer for the very meticulous review.
+We have refined our contributions in the introduction section and restructured the methodology section.
+We have also corrected the grammatical misuses accordingly.
+
 \noindent \textbf{In a real car accurate depth information might not be available.
@@
 Experiments on real data would make the results much stronger.}
-
-\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
-
 \noindent \textbf{Do you think the results you obtained with the Synthia data will transfer to real-world data?}
-
 \noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with ‘real’ physics and photo-realism similar to Synthia.
 It would be interesting to implement this system and evaluate ‘real-world’ performance.}
+
+\noindent We have indeed noticed the recently released photo-realistic simulators CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV}.
+And we found that CARLA is especially suited as a further extension to verify our proposed system due to the availability of continuous video streams and ground truth segmentation.
+In terms of transferring to real-world data, from the semantic segmentation results of Synthia, we have observed that model trained on synthetic dataset produced good segmentations by itself on real datasets, and dramatically boosted accuracy in combination with real data.
+Hence, we believe the hybrid of synthetic data and real-world data would be the most data efficient and promising way for the model generalization.
+Model verification on public real-world datasets, e.g., Comma.ai~\cite{santana2016learning} Udacity~\cite{udacity} dataset would be our forthcoming imminent works.
 

### 2018-01-24 paper/cvpr2018/cvpr2018_3790.tex
paper writing. TODO: writing exp section with social lstm.

@@
 \usepackage{tabu,multirow}
+\usepackage[toc,page]{appendix}
 \DeclareCaptionLabelFormat{noname}{#2}
@@
 We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
- We also show the effectiveness of using privileged information (e.g., scene semantics) to further boost the prediction accuracy across diverse traffic conditions.
+We also show the effectiveness of combining various levels of abstractions(e.g., scene semantics, detection bounding boxes) further boost the prediction accuracy across diverse traffic conditions.
 \end{abstract}
@@
         \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
-        \caption{ {
+        \caption{ \small{
         We propose a system to predict future trajectories of vehicles.
@@
 Existing methods for scene parsing also mainly focus on static images.
-However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by a sequence of input frames instead of simply one static frame.
+However, autonomous driving is intrinsically a dynamic problem. Human drivers make decisions by a sequence of input frames instead of one static frame.
 Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.
@@
 Vehicle trajectory prediction is also very related to visual tracking.
-In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
-However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks).
+In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
+However, traffic participants generally exhibit regular trajectories by obeying a large number of common sense rulesp (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks).
 Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
-Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.
+Nonetheless, due to the missing bridge between the traditional visual tracking community and the current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.
 
@@
 This material doubles as an outline of the rest of the paper, saving space and eliminating redundancy.
-In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction as shown in Fig.~\ref{fig:pull_figure}.Our contributions are as follows:
+We address this issue through building a system that takes advantage of multiple streams with various levels of abstraction.
+In our approach, there are three key components: traffic participants detection, instance tracking and future trajectory prediction as shown in Fig.~\ref{fig:pull_figure}.Our main contributions are as follows:
+\begin{itemize}
+\itemsep0em
+\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia}\footnote{Dataset will be released upon paper publication.} and verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception.
 
-\begin{itemize}
+\item We take advantage of various levels of abstractions from multiple streams via recurrent network based temporal models and demonstrate the effectiveness of using ``auxiliary information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.
 
-\item We verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception.
-The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
-
-\item We present a novel ``tracking-by-detection" framework for robust vehicle tracking.
-By updating tracker's target representation via detection association, we also solve the problem of instance association between frames.
-
-\item We design various temporal models for the problem of predicting future trajectories based on historical data.
-Results show that the temporal model generating intermediate representation performs better than the frame-to-frame based temporal model.
-
-\item We demonstrate the effectiveness of using ``privileged information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.
-
-\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
+\item Preliminary results by incorporating ``social" factor demonstrate the potential of learning common sense rules with neighboring traffic participants in complex real world  environment.
 
 \end{itemize}
+%\begin{itemize}
+%
+%\item We verify the feasibility of predicting vehicles' future trajectories for assisting mediated perception.
+The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
+%
+%\item We present a novel ``tracking-by-detection" framework for robust vehicle tracking.
+By updating tracker's target representation via detection association, we also solve the problem of instance association between frames.
+%
+%\item We design various temporal models for the problem of predicting future trajectories based on historical data.
+Results show that the temporal model generating intermediate representation performs better than the frame-to-frame based temporal model.
+%
+%\item We demonstrate the effectiveness of using ``privileged information"(\emph{e.g.}, scene semantics) further boost the prediction accuracy.
+%
+%
+%\item We construct a time-series dataset for vehicle trajectory prediction based on the SYNTHIA dataset~\cite{ros2016synthia} and  formalize the problem into a 3D occupancy grid problem given depth information.
+%
+%\end{itemize}
 
@@
 %\subsection{Traffic participants detection and tracking: object detection and instance association}
-\subsection{Object detection}
-Vehicle detection is one key component of an autonomous driving system. Typical algorithms output bounding boxes on detected vehicles.
-A lot of progess has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
-Modern object detectors based on these networks -- such as the line of works on the R-CNN~\cite{girshick2014rich},
-Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
+\noindent \textbf{Traffic participants detection} Traffic participants detection is one key component of an autonomous driving system.
+Vehicle detection has been well studied for static high-way mounted cameras: ~\cite{hadi2014vehicle} present a concise overview of image processing methods and analysis tools before the ``deep learning eras".
+%Typical algorithms output bounding boxes on detected vehicles.
+A lot of progress has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
+Modern object detectors~\cite{girshick2014rich, Girshick2015Fast, ren2015faster_nips, He2015Spatial, he2017mask, redmon2016you, liu2016ssd} are now good enough to be deployed in a consumer products.
+Faster R-CNN~\cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN~\cite{Girshick2015Fast} to build an end-to-end architecture.
+SSD \cite{liu2016ssd} similarly uses a series of boxes and directly gives the probability for each object class.
+
+Typical algorithms output bounding boxes on detected objects for a static image.
+And the deep neural nets can be transferred and fine-tuned to another set of classes for traffic participants  we actually care about in the context of autonomous driving.
+% on the R-CNN~\cite{girshick2014rich},
+%Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
 % Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
 % However, after the proposal of
- R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
- % At the beginning, R-CNN is a step-by-step and inefficient method. Then,
-  SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features.
+%R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
+%% At the beginning, R-CNN is a step-by-step and inefficient method. Then,
+%SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features.
 Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network.
@@
 
-\subsection{Instance association}
-Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.
-3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the present of large displacement or local ambiguities.
+\noindent \textbf{Instance association} Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.
+3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the presence of large displacement or local ambiguities.
 %Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
-However, a total runtime of 10 minutes per frame is way too prohibitive for the deployment in the context of autonomous driving.
+However, a total runtime of 10 minutes per frame is computationally prohibitive for the real-time deployment.
 To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking.
 Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
-Built upon their seminal work, there has been a plethora of recent improvements~\cite{wang2016stct, wang2015visual, hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.
+Built upon their seminal work, there has been a plethora of recent improvements~\cite{hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.
+
+Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking.
+In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
+Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations.
+This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
+In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
+Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting.
+Hence the tracker is served solely as instance associator for the traffic participant.
 
@@
         \caption{
-        The framework for the proposed vehicle future trajectory prediction system.
-The input is the sequential data obtained from the host car.
-Historical information is extracted by detection \& tracking.
-Along with scene semantics as an auxiliary information, multi-stream inputs are fed into our LSTM model to predict future trajectories.}
-
+        \small{The framework for the proposed vehicle future trajectory prediction system.
+The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car.
+Target vehicles' sequential bounding boxes are extracted by detection \& tracking module.
+Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
+        }
         \label{fig:framework}
 \end{figure*}
+%\noindent \textbf{RNN for sequence prediction}
 
-\subsection{Recurrent neural networks}
+%Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
+\noindent \textbf{Activity forecasting} Activity forecasting is the task of predicting the motion or the action to be carried out by objects in a video. 
+A body of work~\cite{chalasani2013deep, clark2013whatever, egner2010expectation} explores various hierarchical models in face of different quality of data representation. 
+ Recently recurrent neural networks (RNN) and their variants including Long Short Term Memory (LSTM)~\cite{hochreiter1997long} and Gated Recurrent Units (GRU)~\cite{chung2014empirical} have proven to be very successful for sequence prediction tasks.
+ An action-conditioned video prediction model~\cite{finn2016unsupervised} that explicitly models pixel motion, by predicting a distribution over pixel motion from previous frames is proposed to learn from unsupervised video data.
+ %The discrepancy between training and inference can yield errors that can accumulate quickly along the generated sequence when using a recurrent neural network.p
+ A curriculum learning strategy is proposed in~\cite{bengio2015scheduled} to gently change the training process from a fully guided scheme using the true previous token, towards a less guided scheme which mostly uses the generated token instead.
+A combination of a fully-convolutional network and an LSTM is proposed in~\cite{xu2017end} to learn from large-scale vehicle action data and  is trained as a pilot network in the context of behaviour reflex approaches.
+Their goal is to predict future egomotion including multi-modal discrete and continuous driving behaviors.
+Inverse turning radius is predicted by a LSTM network in~\cite{kim2017interpretable}: a heat map of attention is generated at each time step conditioned on the previous hidden states as a more succinct visual explanations.
 
-Recent advances in recurrent neural network for modeling visual sequential data are also related to our work.
-%Recently, RNN(recurrent network) and its variant LSTM(long short-term memory) have been successfully used in autonomous driving, due to its advantages for modeling sequential data in vision problems.
-Mostly, RNN is trained as a pilot network in the context of behaviour reflex approaches.
-Long Short Term Memory (LSTM) cells are usually exploited as one intermediate component of an end-to-end driving model.
- A combination of a fully-convolutional network and an LSTM is proposed in~\cite{xu2017end} to learn from large-scale vehicle action data.
-Their goal is to predict future egomotion including multi-modal discrete and continuous driving behaviors.
- Inverse turning radius is predicted by a LSTM network in~\cite{kim2017interpretable}: they generate a heat map of attention at each time step conditioned on the previous hidden states and a current convolutional feature cube  to produce more succinct visual explanations.
-~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
+More recent works also attempt to take the ``social factor" into consideration.
+Social-LSTM~\cite{alahi2016social} focus on modeling dynamics crowd interactions for path prediction by introducing a ``social tensor" from a spatial-temporal neighborhood.
+Based on the social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
+%~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
 In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.
 
-\subsection{Dataset for autonomous driving}
-
-Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
+\noindent \textbf{Datasets for autonomous driving} Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
 %Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK.
@@
 The use of synthetic data has increased considerably in recent years within computer vision community.
-A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
+CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV} are two recent endeavours that take advantage of simulated environment to support development, training and validation of autonomous urban driving systems.
+A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is collected for investigating how useful synthetic images can be for semantic segmentation.
 %In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
@@
 
-\subsection{3D Traffic Participants Trajectory Prediction}
+\subsection{Problem formulation}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
+        \caption{
+        \small{Illustrations of three temporal networks.
+$\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.
+Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with extra auxiliary information as input $\mathcal{A}$.
+$\mathcal{S}$ is the social tensor that can be inserted into existing recurrent networks.}
+        }
+        \label{fig:lstm}
+\end{figure}
 
 We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
-Our work is most related to~\cite{xu2017end} where the problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
-We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
-Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $H=\{h_t^p\}, t=1,\dots, T $ with auxiliary information $ A=\{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $J=\{j_t^p\}, t={T+1}, \ldots$:
+%Our work is most related to~\cite{xu2017end} where their problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
+%We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
+Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $\mathcal{J_H}=\{j_p^t\}, t=1,\dots, T $ with auxiliary information $ \mathcal{A}=\{a_p^t\},t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\mathcal{J_F}=\{j_p^t\}, t={T+1}, \ldots, T_F$:
 
 \begin{equation}
-J \leftarrow \bm{\mathcal{M}}_p(h, a): H \times A
+\mathcal{J_F} \leftarrow \bm{\mathcal{M}}_p(j, a): \mathcal{J_H} \times \mathcal{A}
 \label{eq:mapping}
@@
 where the traffic participants $p$ can be vehicles, cyclists, pedestrians, \emph{etc}.
-In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on.
+In this paper, we focus on vehicle as the sole traffic participant category and ignore the subscript $p$ from now on.
+$T_F$ is the length of future trajectory to be predicted (corresponding to the total driver reaction time). 
 Historical and future trajectories are defined in a 3D occupancy grid:
 \begin{equation}
-H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
+\mathcal{J_H, J_F} \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
 \label{eq:mapping2}
@@
 
-Auxiliary information $A$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.
-
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.52\textwidth]{figures/network_detail.pdf}
-        \caption{Illustrations of three temporal networks.
-$H$ represents historical trajectories, $J$ is the $T$ time step trajectories to be predicted.
-Left: Frame-to-Frame (FtF); Middle:Frame-to-Sequence (FtS); Right:SEG-LSTM, with extra auxiliary information as input $A$.}
-        \label{fig:lstm}
-\end{figure}
+%Auxiliary information $\mathcal{A}$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.
 
@@
 
-For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}.
+For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells.
+A ``social pooling tensor" that implicitly reasons about the motion of neighboring traffic participants can be inserted into existing recurrent network architectures without any extra training supervision or modification to the optimization process as shown in Fig.~\ref{fig:lstm}.
 The first two models take sequential 3D occupancy as input.
-In the third model, we  explore using semantic segmentation as a side ``auxiliary" information to better guide the trajectory prediction.
+In the third model, we  explore using semantic segmentation as a side ``auxiliary" information $\mathcal{A}$ to better guide the trajectory prediction.
 
@@
 \noindent \textbf{Frame-to-Frame (FtF) model:}
-is akin to character prediction in a language model.
+is akin to  sequence generation model from Graves~\cite{graves2013generating}.
 At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid.
-The model is frame to frame Markovian and the next frame trajectory $j_t$ can be estimated as:
+The model is frame to frame Markovian and the next frame trajectory $j_{t+1}$ can be estimated as:
 \begin{equation}
-j_t \leftarrow  \bm{\mathcal{M}}_p(j_{t-1}, h): H
+j_{t+1} \leftarrow  \bm{\mathcal{M}}(j_t, j_H): \mathcal{J_H}
 \label{eq:FtF}
@@
 \noindent \textbf{Frame-to-Sequence (FtS) model:}
-differs from the FtF model in that instead of sampling frame by frame for predicting future trajectories,   FtS model directly predicts a trajectory sequence of length $T$ (corresponding to the total driver reaction time).
-The assumption is that current state is complete, in the sense it contains all historical information required for predicting the future trajectory of the vehicle.
-The whole trajectory  $j_{t, t+1, \ldots, T}$ to be predicted can be estimated as:
+differs from the FtF model in that instead of sampling frame by frame for predicting future trajectories, FtS model directly predicts a trajectory sequence of length.
+As it pointed out in~\cite{bengio2015scheduled} that FtF training paradigm, predicting one token at a time, conditioned on the state and the previous correct token, is different from how we actually use them during inference and thus is prone to the accumulation of errors along the decision paths.
+Therefore, a curriculum learning approach is proposed to slowly change the training objective from an easy task, where the previous token is known, to a realistic one, where it is provided by the model itself.
+The aforementioned learning strategy applies to inference for time-varying sequence where an \textless EOS\textgreater token is needed to signify the end of the sequence.
+For our continuous prediction task, we stipulate the length of the prediction is predefined as $T_F$.
+Hence we have the assumption that current state is complete, in the sense it contains all historical information required for predicting the future trajectory of the vehicle. 
+The whole trajectory  $j_{t+1, \ldots, T_F}$ to be predicted can be estimated as:
 \begin{equation}
-j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p( h): H
+j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H): \mathcal{J_H}
 \label{eq:FtS}
+\end{equation}
+The whole sequence inference paradigm is more stable than the first FtF approach because of the elimination of the dependency of previous token.
+Such dependency will introduce the discrepancy between how the model is used at training and inference.
+Inference with the whole sequence will generate smoother predictions.
+
+\vspace{\baselineskip}
+\noindent \textbf{SEG-LSTM model:}
+ takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$.
+The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embeddings with higher level semantic information.
+Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.[????].
+The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.
+
+ As described above, the input in the form of 3D occupancy has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information.
+So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both trajectory information and the semantic information.
+%Results show that the SEG-LSTM model performs better than the other two temporal model.
+
+Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and directs the recurrent net future trajectory prediction.
+With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
+
+\begin{equation}
+j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times \mathcal{A}
+\label{eq:SEG-LSTM}
 \end{equation}
@@
 \vspace{\baselineskip}
-\noindent \textbf{SEG-LSTM model:}
- takes advantages of scene semantics from  historical frames as auxiliary information $A$.
-The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information.
-Semantic inputs are one-hot encoded images with channel number $C$ as the number of semantic category.
-The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.
-As described above, the 3D occupancy just has six dimensions: $[x, y, w, h, d_{min}, d_{max}]$.
-So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance input dimensions of both trajectory information and the semantic information.
-%Results show that the SEG-LSTM model performs better than the other two temporal model.
-Note that this model differs from that of~\cite{xu2017end} in that instead of using semantic segmentation as a side task for better directing the learning process of the convnets, SEG-LSTM directly takes scene semantics as input and directs the recurrent net future trajectory prediction.
-With auxiliary $A$, the trajectory  $j_{t, t+1, \ldots, T}$  to be predicted can be estimated as:
-
+\noindent \textbf{Social tensor:} is firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space.
+Naturally, in the context of high-way driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories.
+The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors.
+While pooling the information, the spatial information is preserved by grid based pooling.
+The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene.
+This representation can be shared with neighbors by building a social hidden tensor $s^i_t$:
 \begin{equation}
-j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p(h, a): H \times A
-\label{eq:SEG-LSTM}
+s^i_t = \sum_{j \in \mathcal{N}_i} \mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t] \centerdot  h^j_{t-1}
+\label{eq:social_tensor}
+\end{equation}
+where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to person $i$.
+This social tensor can be inserted in to the hidden layer of LSTM and update can be formulated as a neighboring batch update scheme.
+The trajectory  to be predicted can be estimated as:
+\begin{equation}
+j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, s^i_H): \mathcal{J_H}  \times \mathcal{S}
+\label{eq:FtS}
 \end{equation}
@@
 \subsection{Dataset collection}
-\begin{algorithm}[h]
+\begin{algorithm}[t]
 \begin{algorithmic}
-\caption{\textbf{Car trajectory ground truth collection}}\label{list:dataset_collection}
+\caption*{\textbf{Ground truth collection for car trajectory prediction}}\label{list:dataset_collection}
+\small{
 \STATE \textbf{Step 1} $\rightarrow $ acquiring traffic participants from ground truth annotations with only ``car" as instances.
@@
   \eindent}
-
+}
 \end{algorithmic}
 \end{algorithm}
+
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
+        \caption{
+        \small{Examples of collected dataset for vehicle trajectory prediction. From top to bottom: RGB, semantic labeling, depth maps for three continuous frames under two dynamic light conditions.}
+        }
+        \label{fig:dataset}
+\end{figure}
 
@@
 Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
-The train/valid/test are split as 80\%/10\%/10\% of the total tracklets and the total numbers are shown in Tab.~\ref{tab:dataset_statistics}.
-We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
+The train/valid/test are split as 80\%/10\%/10\% of the total tracklets and the total numbers are shown in Tab.~\ref{tab:dataset}.
+%We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}.
 Some sample frames with semantic labels and depth information is shown in Fig.~\ref{fig:dataset}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
-        \caption{Examples of collected dataset for vehicle trajectory prediction.
-From top to bottom: RGB, semantic labeling, depth maps for three continuous frames under two dynamic light conditions.}
-        \label{fig:dataset}
-\end{figure}
 
@@
 \subsection{Implementation Details}\label{sec:Implementations}
+\begin{table}[t]\centering
+\ra{1.}
+\begin{tabu}{@{}llll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-4}
+                & \#train & \#valid & \#test\\ \hline
+ tracklets      &  10400    &  1300    & 1280 \\ \hline
+ car detection  &   7832     & 976     & 986 \\ \hline
+ semantic segmentation  &  7841  & 977  & 987 \\
+ \hline
+ \end{tabu}
+%\end{tabular}
+\caption{\small{Dataset statistics}}
+\label{tab:dataset}
+\end{table}
 
@@
 
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
-        \caption{Instance association can help to disambiguate the false positive by enforcing temporal consistency requirement.
-Due to the high recall requirement for vehicle detection, there could be correspondingly higher false positive rate (\emph{e.g.}, double detection of red boxed in the far left).
-Instance association across multiple frames will discard the spurious detection.}
-        \label{fig:Instance_association}
-\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{Instance tracking}
+\subsubsection{Instance association via tracking}
 
@@
 
-\begin{table}\centering
-\ra{1.}
-%\begin{tabular}{@{}llll@{}}\toprule
-
-\begin{tabu}{@{}llll@{}}\toprule
-[-1pt] \tabucline[1pt]{1-4}
-                & \#train & \#valid & \#test\\
- \hline
-
- tracklets      &  10400    &  1300    & 1280 \\
- \hline
- car detection  &   7832     & 976     & 986 \\
- \hline
- semantic segmentation  &  7841  & 977  & 987 \\
- \hline
- \end{tabu}
-%\end{tabular}
-\caption{Dataset statistics}
-\label{tab:dataset_statistics}
-\end{table}
-
 \subsubsection{Trajectory prediction}
-\begin{table*}\centering
-\ra{1.}
-%\begin{tabular}{@{}llllllllllll@{}}\toprule
-\begin{tabu}{@{}llllllllllll@{}}\toprule
-[-1pt] \tabucline[1pt]{1-12}
-\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
-\hline
-\multirow{3}{*}{Faster-RCNN}
-                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
-                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
-                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
-                    \cline{2-12}
-\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
-                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
-                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
-                    \cline{2-12}
-\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
-                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
-                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
-
-\bottomrule
-\end{tabu}
-%\end{tabular}
-\caption{
-Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
-It can be seen that:
-(1) both meta-architectures are robust to the cut-off confident thresholds.
-(2) SSD is more competitive in the collected dataset when targets of interest are large.
-}
-\label{tab:ssd_fasterrcnn}
-\end{table*}
+%\begin{table*}\centering
+%\small{
+%\ra{1.}
+%%\begin{tabular}{@{}llllllllllll@{}}\toprule
+%\begin{tabu}{@{}llllllllllll@{}}\toprule
+%[-1pt] \tabucline[1pt]{1-12}
+%\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
+%\hline
+%\multirow{3}{*}{Faster-RCNN}
+%                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
+%                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
+%                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+%                    \cline{2-12}
+%\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
+%                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
+%                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
+%                    \cline{2-12}
+%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+%                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+%                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+%
+%\bottomrule
+%\end{tabu}
+%%\end{tabular}
+%\caption{
+%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
+%It can be seen that:
+%(1) both meta-architectures are robust to the cut-off confident thresholds.
+%(2) SSD is more competitive in the collected dataset when targets of interest are large.
+%}
+%\label{tab:ssd_fasterrcnn}
+%}
+%\end{table*}
 
@@
 The input semantics are one-hot encoded in the dimension of $95\times160\times2$.
-The CNN for learning high level semantics is composed of four convolutional blocks.
+The CNN for learning high level semantics is composed of 4 convolutional blocks.
 Each block includes a convolutional layer, a ReLU activation layer, a maxpooling layer and a dropout layer (as we have observed overfitting during network training).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[t]
+%   \centering
+%    \begin{subfigure}[c]{0.25\textwidth}
+%    \centering
+%    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
+%    \caption{\small{Precision plot for 2D (pixel as x-axis)}}
+%    \end{subfigure}%
+%    \begin{subfigure}[c]{0.25\textwidth}
+%    \centering
+%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
+%        \caption{\small{Success plot 2D ()}}
+%    \end{subfigure}
+%     \begin{subfigure}[c]{0.25\textwidth}
+%     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20cm.png}
+%    \caption{\small{Precision plot for 3D (centimeter as x-axis)}}
+%    \end{subfigure}%
+%    \begin{subfigure}[c]{0.25\textwidth}
+%    \centering
+%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
+%        \caption{\small{Success plot 3D (IOU as x-axis)}}
+%    \end{subfigure}
+%\caption{\small{ 2D and 3D space precision plot and success plot.}}
+%\label{fig:precision_plot_and_success_plot}
+%\end{figure*}
+
+%\setlength{\fboxsep}{1pt}%
+%\setlength{\fboxrule}{1pt}%
 \begin{figure*}[t]
        \centering
-    \begin{subfigure}[c]{0.4\textwidth}
+        \begin{subfigure}[c]{0.24\textwidth}
         \centering
-    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
-    \caption{\small{Precision plot for 2D (pixel as x-axis)}}
-    \end{subfigure}%
-    \begin{subfigure}[c]{0.4\textwidth}
+                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_2d.png}
+    \caption{\small{2D Precision plot}}
+        \end{subfigure}
+        \begin{subfigure}[c]{0.24\textwidth}
         \centering
-        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
-        \caption{\small{Success plot 2D (IOU as x-axis)}}
+                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_2d.png}
+        \caption{\small{2D success plot}}
         \end{subfigure}
-    \\
-     \begin{subfigure}[c]{0.4\textwidth}
-     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20cm.png}
-    \caption{\small{Precision plot for 3D (centimeter as x-axis)}}
-    \end{subfigure}%
-    \begin{subfigure}[c]{0.4\textwidth}
+       \begin{subfigure}[c]{0.24\textwidth}
         \centering
-        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
-        \caption{\small{Success plot 3D (IOU as x-axis)}}
+                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_3d_20cm.png}
+    \caption{\small{3D precision plot}}
         \end{subfigure}
-\caption{2D and 3D space precision plot and success plot .
-}
+               \begin{subfigure}[c]{0.24\textwidth}
+        \centering
+                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_3d.png}
+        \caption{\small{3D Success plot}}
+        \end{subfigure}
+
+\caption{\small{ 2D and 3D space precision plot and success plot. x-axis for (a) to (d) are: pixel, IOU, centimeter and IOU as x-axis.}}
 \label{fig:precision_plot_and_success_plot}
@@
 \subsection{Evaluation}
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
-        \caption{ The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.
-        }
-        \label{fig:evaluation}
-\end{figure}
 
@@
         \caption{
-        The prediction results in SYNTHIA dataset. {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
+        \small{The prediction results in SYNTHIA dataset. {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
         The results using SEG-LSTM network show that by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the predicted trajectory from the recurrent net within the most plausible path.
-Top: SEG-LSTM can help detecting neighbouring vehicles and restricts the viable path outside the space occupied by other vehicles.
-Bottom:  SEG-LSTM confines the possible car trajectories along the space above road.
+Top: SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles.
+Bottom:  SEG-LSTM confines the possible car trajectories along the space above road.}
                 }
@@
 
+\vspace{\baselineskip}
+\noindent \textbf{Learning with social tensor:}
+Tab.~\ref{tab:social_lstm}
+
 \begin{table}[t]
@@
         [-1pt] \tabucline[1pt]{1-3}
-
             Configuration  &     mean coverage      & center error   \\
                        2D   &       (\%) &             (pixel)     \\ \hline
-
             {\small Kalman Filter}             &  54.31          &  24.84             \\
-
             {\small \textbf{FtF} }              &  66.47     &  23.43  \\
-
             {\small \textbf{FtS}  }              &  73.93      &   15.32  \\
-
             {\small \textbf{SEG-LSTM} }         &  \textbf{77.53  }    & \textbf{ 12.63 }   \\
@@
     \caption{ {\small
-    Results of 2D performance evaluation on mean coverage (higher is better) and center error (lower is better).
+    Results of 2D performance evaluation (pixel as unit) on mean coverage (higher is better) and center error (lower is better).
      }
@@
             {\small \textbf{FtF} }              &    35.67    &  0.7122   \\
-
             {\small \textbf{FtS}  }              &   46.69	     &    0.3686 \\
-
             {\small \textbf{SEG-LSTM} }         &  \textbf{48.49}     &   \textbf{0.3298}   \\
@@
     \caption{ {\small
-    Results of 3D performance evaluation on mean coverage (higher is better) and center error (lower is better).
-     }
-          } \label{table_baseline_3d}
+    Results of 3D performance evaluation (centimeter as unit) on mean coverage (higher is better) and center error (lower is better).
+     }} \label{table_baseline_3d}
 \end{table}
 %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{Evaluation Metrics}
+\begin{table}[t]
+\small
+   \centering
+        %\begin{tabular}{|l *{2}{c}|}\hline
+        %\begin{tabu}{|l *{2}{c}|}
+        \begin{tabu}{@{}ccc@{}}\toprule
+        [-1pt] \tabucline[1pt]{1-3}
+                                                    &   ave. disp. error      & final disp. error   \\ \hline
+            {\small Vanilla LSTM }                 &    0.0257                &  0.0440   \\
+            {\small \textbf{Social LSTM} }         &  \textbf{0.0247}         & \textbf{0.0418}   \\
+          [-1pt] \tabucline[1pt]{1-3}
+        \end{tabu}
+        %\end{tabular}
+
+    \caption{ {\small Results of 3D performance evaluation on mean coverage (higher is better) and center error (lower is better).
+     }} \label{tab:social_lstm}
+\end{table}
 
@@
 The recurrent network takes semantic information as an auxiliary input and further improve the predicting accuracy.
-Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``privileged information" and conducting experiments on the real-world images.
+Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``auxiliary information" and conducting experiments on the real-world images.
 
@@
 }
+
+\clearpage
+\begin{appendices}
+
+\section{Traffic participants detection}
+\begin{table}[H]\centering
+\small{
+\ra{1.}
+%\begin{tabular}{@{}llllllllllll@{}}\toprule
+\begin{tabu}{@{}lllll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-5}
+\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
+\multirow{3}{*}{Faster-RCNN}
+                                &   precision & 81.2    & 81.1  & 80.0\\
+                                &   recall    & 91.4    & 91.3  & 90.2\\
+                                &   f-score   & 86.0    & 86.0  & 84.8\\
+                                    \cline{2-5}
+\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
+                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
+                                &   f-score   & 87.1 &86.5  &84.0\\
+                                    \cline{2-5}
+\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
+                                &   recall  & 92.3 & 91.4 & 87.7\\
+                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
+\bottomrule
+\end{tabu}
+%\end{tabular}
+\caption{
+Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
+It can be seen that:
+(1) both meta-architectures are robust to the cut-off confident thresholds.
+(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
+}
+\label{tab:ssd_fasterrcnn}
+}
+\end{table}
+
+\section{Instance association via tracking}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
+        \caption{
+        \small{Instance association can help to disambiguate the false positive by enforcing temporal consistency requirement.
+Due to the high recall requirement for vehicle detection, there could be correspondingly higher false positive rate (\emph{e.g.}, double detection of red boxed in the far left).
+Instance association across multiple frames will discard the spurious detection.}
+        }
+        \label{fig:Instance_association}
+\end{figure}
+
+\section{2D and 3D occupancy grid}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
+        \caption{
+        \small{The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.}
+        }
+        \label{fig:evaluation}
+\end{figure}
+
+\end{appendices}
+
 \end{document}

### 2018-01-24 paper/cvpr2018/cvpr2018_3790.tex
Paper writing, result plot figure resize

@@
 
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
+        \caption{
+        \small{TODO: SEGLSTM HERE!}
+        }
+        \label{fig:SEGLSTM}
+\end{figure}
 \subsection{Sequence modeling}
@@
 The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embeddings with higher level semantic information.
-Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.[????].
+Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}.
 The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.
@@
         \centering
-                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_2d.png}
+                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/precision_plot_2d.png}
     \caption{\small{2D Precision plot}}
@@
         \centering
-                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_2d.png}
+                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/success_plot_2d.png}
         \caption{\small{2D success plot}}
@@
         \centering
-                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_3d_20cm.png}
+                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/precision_plot_3d_20cm.png}
     \caption{\small{3D precision plot}}
@@
         \centering
-                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_3d.png}
+                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/success_plot_3d.png}
         \caption{\small{3D Success plot}}

### 2018-01-25 paper/cvpr2018/cvpr2018_3790.tex
Paper writing. TODO: final illustration image

@@
 $\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.
-Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with extra auxiliary information as input $\mathcal{A}$.
-$\mathcal{S}$ is the social tensor that can be inserted into existing recurrent networks.}
+Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with auxiliary information as input $\mathcal{A}$.
+The social tensor $\mathcal{S}$ can be inserted into existing recurrent networks .}
         }
@@
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
+        \includegraphics[width=0.45\textwidth]{figures/SEGLSTM.pdf}
         \caption{
-        \small{TODO: SEGLSTM HERE!}
+        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics used under the context of high-way driving).
+The higher level semantics are extracted through a four-layer CNN, producing a joint representation of the auxiliary semantic information and the co-ordinate trajectory information.}
         }
@@
  takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$.
-The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embeddings with higher level semantic information.
-Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}.
-The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.
-
- As described above, the input in the form of 3D occupancy has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information.
-So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both trajectory information and the semantic information.
-%Results show that the SEG-LSTM model performs better than the other two temporal model.
-
-Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and directs the recurrent net future trajectory prediction.
+The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embedding with higher level semantic information.
 With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
-
 \begin{equation}
@@
 \end{equation}
+ Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}.
+The higher level semantic is extracted through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the co-ordinate trajectory information.
+ As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information.
+So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both co-ordinate information and the semantic information.
+%Results show that the SEG-LSTM model performs better than the other two temporal model.
+
+Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and directs the recurrent net future trajectory prediction.
 
 \vspace{\baselineskip}
-\noindent \textbf{Social tensor:} is firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space.
-Naturally, in the context of high-way driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories.
+\noindent \textbf{Social tensor:} was firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space.
+Naturally, in the context of autonomous driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories.
 The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors.
@@
 \end{equation}
-where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to person $i$.
-This social tensor can be inserted in to the hidden layer of LSTM and update can be formulated as a neighboring batch update scheme.
+where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to target $i$.
 The trajectory  to be predicted can be estimated as:
@@
 \end{equation}
+This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM and training can be formulated as a neighboring batch update scheme.
+An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer.
+At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene.
 
@@
 \subsection{Dataset collection}
+
+Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
+We collect a car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
+SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
+The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
+The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
+There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
+Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
+In our experiment, we used only left front camera view data.
+
 \begin{algorithm}[t]
@@
 
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
-        \caption{
-        \small{Examples of collected dataset for vehicle trajectory prediction. From top to bottom: RGB, semantic labeling, depth maps for three continuous frames under two dynamic light conditions.}
-        }
-        \label{fig:dataset}
-\end{figure}
-
-Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
-We collect a car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
-SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
-The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups.
-The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
-There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
-Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.
-In our experiment, we used only left front camera view data.
-
 The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Implementation Details}\label{sec:Implementations}
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.5\textwidth]{figures/dataset.pdf}
+        \caption{
+        \small{Examples of collected dataset for vehicle trajectory prediction. From top to bottom: RGB, semantic labeling, depth maps for three continuous frames under two dynamic light conditions.}
+        }
+        \label{fig:dataset}
+\end{figure}
+
 \begin{table}[t]\centering
@@
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Implementation Details}\label{sec:Implementations}
 
@@
 In this paper, we are mostly concerned about cars that are close to the driver.
-Hence, given 0.1\% POR as the the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
-Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when objects of interest are large in our problem set.
-We also compare the influence of the cut-off threshold for various confident scores and non-maximum suppression (NMS) threshold.
-It can been seen that both meta-architectures are robust to the cut-off confident scores.
-In terms of the effect of NMS cut-off threshold, allowing larger threshold enables the detector to have slightly higher recall, it comes at a cost of multiple redundant overlapping detections and much lower f-score overall.
-In the following experiment, we adopt SSD with confident score of 0.5 as the cut-off threshold and 0.45 as the default jaccard overlap for NMS.
+Hence, given 0.1\% POR as the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
+Tab.~\ref{tab:ssd_fasterrcnn} verifies that SSD is indeed more competitive when objects of interests are large in our problem set.
+We also compare the influence of the cut-off threshold for various confident scores and non-maximum suppression (NMS) thresholds.
+It can been seen that both meta-architectures are robust to cut-off confident scores.
+Allowing larger NMS threshold enables the detector to have slightly higher recall, it comes at a cost of multiple redundant overlapping detections and much lower f-score overall.
+In the following experiment, we adopt SSD with a confident score of 0.5 as the cut-off threshold and 0.45 as the default jaccard overlap for NMS.
 
@@
 
-To associate traffic participants across different frames (\emph{i.e.}, instance tracking), we creatively combine detecting with tracking.
-The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
+To associate traffic participants across different frames (\emph{i.e.}, instance association), we creatively combine detecting with tracking.
+%The marriage between DCF~\cite{henriques2015high}, which has the advantage of being efficient in training translational images in the fourier space, and deep features, which excel at image representation, further advances the visual tracking community~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco}.
 However, in the pursuit of ever increasing tracking accuracy, their characteristic speed and realtime capability have gradually faded.
-In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
+%In the context of autonomous driving, accurate scale estimation of a target is also a prerequisite.
 Most state-of-the-art methods employ an exhaustive scale search to estimate the target size which is computationally expensive and struggles when encountering with large scale variations.
@@
 For every newly detected target whose POR is larger than the predefined threshold of 0.2\%, we initiate the tracker with a unique target ID.
+
 The tracker's target model is updated every time when there is a detection whose jaccard overlap is larger than 0.3.
-We argue that this ``tracking by detection" framework is essential for robust object tracking, especially when the objects undergo rapid out of plane rotations.
-In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{c.f.} Fig.~\ref{fig:Instance_association}).
+We argue that force update of tracker model via the detection template is essential when the target undergo rapid out of plane rotations.
+Trackers~\cite{qi2016hedged, danelljan2016eccv, wu2017kernalised, danelljan2017eco} focus on the ``class-agnostic" settings.
+In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking.
+Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker’s model to overcome the problem of model drifting.
+Hence the tracker is served solely as instance associator for the traffic participant.
+In return, the instance association scheme helps to alleviate the problem of false positive detection (\emph{c.f.} Fig.~\ref{fig:Instance_association}) from the detection result.
 The target's tracker will terminate under either of the following two conditions: if the target's POR is smaller than 0.1\% (\emph{i.e.}, the vehicle is too far way from the host car); or if there are more than 5 frames of detection absence  (\emph{i.e.}, the target could be one false positive detection from the vehicle detector).
@@
 \subsubsection{Trajectory prediction}
-%\begin{table*}\centering
-%\small{
-%\ra{1.}
-%%\begin{tabular}{@{}llllllllllll@{}}\toprule
-%\begin{tabu}{@{}llllllllllll@{}}\toprule
-%[-1pt] \tabucline[1pt]{1-12}
-%\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
-%\hline
-%\multirow{3}{*}{Faster-RCNN}
-%                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
-%                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
-%                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
-%                    \cline{2-12}
-%\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
-%                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
-%                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
-%                    \cline{2-12}
-%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
-%                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
-%                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
-%
-%\bottomrule
-%\end{tabu}
-%%\end{tabular}
-%\caption{
-%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
-%It can be seen that:
-%(1) both meta-architectures are robust to the cut-off confident thresholds.
-%(2) SSD is more competitive in the collected dataset when targets of interest are large.
-%}
-%\label{tab:ssd_fasterrcnn}
-%}
-%\end{table*}
 
@@
 a 3-layer recurrent net with 100, 300, 300 LSTM cells.
-For SEG-LSTM, since the focus of the scene context is high-way driving, auxiliary information is the scene semantics with only ``car" and ``road".
-The input semantics are one-hot encoded in the dimension of $95\times160\times2$.
+For SEG-LSTM, since the focus of the scene context is high-way driving, auxiliary information is the scene semantics with number of channels $\mathcal{C}$ sets as 2 (``car" and ``road").
+We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus.
+DRN achieves 68\% and 82\% pixel mAP on the car and road categories.
+The input semantics $\mathcal{A}$ are one-hot encoded in the dimension of $95\times160\times2$.
 The CNN for learning high level semantics is composed of 4 convolutional blocks.
@@
 Each convolutional layer has four channels with kernel of size 3.
-We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus.
-DRN achieves 68\% and 82\% pixel mAP on the car and road categories.
 
+For the social tensor configuration, we incorporate all vehicles in the same time-step as their neighbors.
+In contrast with~\cite{alahi2016social} where a spatial constraint is required in order to be counted as a neighbor, all the vehicles in the same scene are relevant for the social interactions under our high-way driving context.
+Grid size is set as 4 and the embedding size is 64 so the social tensor $\mathcal{S}$ is a $4\times 4\times 64$ matrix.
+The learning is set to 0.001 and RMS-prop~\cite{tieleman2012lecture} with a gradient clipping of 3 to avoid divergence.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\caption{\small{ 2D and 3D space precision plot and success plot. x-axis for (a) to (d) are: pixel, IOU, centimeter and IOU as x-axis.}}
+\caption{\small{ 2D and 3D space precision plot and success plot. x-axis for (a) to (d) are: pixel, IOU, centimeter and IOU.}}
 \label{fig:precision_plot_and_success_plot}
@@
 \end{figure*}
-
-\vspace{\baselineskip}
-\noindent \textbf{Baseline: Kalman filter}, also known as linear quadratic estimation, is a popular technique for estimating the state of a system~\cite{Thrun2016}.
-For the task of trajectory prediction, Kalman filters estimates a continuous state and gives a uni-modal distribution.
-The Kalman filter represents all distributions of the Gaussians and iterates two states: (1) measurement updates; (2) motion updates.
-In the baseline, we set
-the initial uncertainly covariance as 1e4, measurement noise and motion noise are all set with unit value.
-
-%We evaluation the trajectory both in 2D space (using pixel as unit distance) and 3D space (using meter as unit distance) as shown in Fig.~\ref{fig:evaluation}.
-
-\noindent \textbf{2D Evaluation Methodology:}
-Following the evaluation strategy  of~\cite{wu2013online}, all trajectories are compared using two measures: precision and success.
-Precision is measured as the distance between the centers of the ground truth bounding box and the corresponding tracker generated bounding box.
-The precision plot shows the percentage of tracker bounding boxed within a given threshold distance in pixels of the ground truth.
-To rank the prediction performance, the conventional threshold of 20 pixels (\emph{P20}) is adopted.
-Success is measured as the intersection over union of pixels.
-The success plot shows the percentage of tracker bounding boxes whose overlap score is larger than a given threshold and the trackers are ranked according to the Area Under Curve (\emph{AUC}) criteria.
-% The 2D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(top) and Tab.~\ref{table_baseline_2d}.
-
-\vspace{\baselineskip}
-\noindent \textbf{3D Evaluation Methodology:} Given depth map and the parameter of camera focal lens, we can formalize the problem into a 3D occupancy grid estimation.
-The real world coordinates $[x_r, y_r, w_r, h_r]$ can be obtained according to Eq.~\ref{eq:focal_length_1}~\ref{eq:focal_length_2}.
-The 3D jaccard index can be similarly formalized as the volume intersection over union: $\frac{V_g \cap V_p}{V_g \cup V_p}$, where $V_g, V_p$ are the ground truth and predicted space occupancy.
-3D center error correspondingly is defined as the mean square root in 3D space.
-%The 3D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(bottom) and Tab.~\ref{table_baseline_3d}.
-
-\vspace{\baselineskip}
-\noindent \textbf{Learning with auxiliary information:}
- The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter.
-Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinate.
- The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
- Fig.~\ref{fig:final} shows the advantage of using SEG-LSTM: by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the recurrent net to output the most plausible path for vehicles and avoid collision with neighboring vehicles.
-
-\vspace{\baselineskip}
-\noindent \textbf{Learning with social tensor:}
-Tab.~\ref{tab:social_lstm}
 
@@
 \end{table}
+
+%\vspace{\baselineskip}
+\noindent \textbf{Baseline: Kalman filter}, also known as linear quadratic estimation, is a popular technique for estimating the state of a system~\cite{Thrun2016}.
+For the task of trajectory prediction, Kalman filters estimates a continuous state and gives a uni-modal distribution.
+The Kalman filter represents all distributions of the Gaussians and iterates two states: (1) measurement updates; (2) motion updates.
+In the baseline, we set
+the initial uncertainly covariance as 1e4, measurement noise and motion noise are all set with unit value.
+%We evaluation the trajectory both in 2D space (using pixel as unit distance) and 3D space (using meter as unit distance) as shown in Fig.~\ref{fig:evaluation}.
+
+\noindent \textbf{2D Evaluation Methodology:}
+Following the evaluation strategy  of~\cite{wu2013online}, all trajectories are compared using two measures: precision and success.
+Precision is measured as the distance between the centers of the ground truth bounding box and the corresponding tracker generated bounding box.
+The precision plot shows the percentage of tracker bounding boxed within a given threshold distance in pixels of the ground truth.
+To rank the prediction performance, the conventional threshold of 20 pixels (\emph{P20}) is adopted.
+Success is measured as the intersection over union of pixels.
+The success plot shows the percentage of tracker bounding boxes whose overlap score is larger than a given threshold and the trackers are ranked according to the Area Under Curve (\emph{AUC}) criteria.
+% The 2D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(top) and Tab.~\ref{table_baseline_2d}.
+%\vspace{\baselineskip}
+
+\noindent \textbf{3D Evaluation Methodology:} Given depth map and the parameter of camera focal lens, we can formalize the problem into a 3D occupancy grid estimation.
+The real world coordinates $[x_r, y_r, w_r, h_r]$ can be obtained according to Eq.~\ref{eq:focal_length_1}~\ref{eq:focal_length_2}.
+The 3D jaccard index can be similarly formalized as the volume intersection over union: $\frac{V_g \cap V_p}{V_g \cup V_p}$, where $V_g, V_p$ are the ground truth and predicted space occupancy.
+3D center error correspondingly is defined as the mean square root in 3D space.
+%The 3D space evaluation result is shown in Fig.~\ref{fig:precision_plot_and_success_plot}(bottom) and Tab.~\ref{table_baseline_3d}.
+
 %%%%%%%%%%%%%%%%%
@@
         [-1pt] \tabucline[1pt]{1-3}
-                                                    &   ave. disp. error      & final disp. error   \\ \hline
+                                                    &   Ave. disp. error      & Final disp. error   \\ \hline
             {\small Vanilla LSTM }                 &    0.0257                &  0.0440   \\
@@
 
-    \caption{ {\small Results of 3D performance evaluation on mean coverage (higher is better) and center error (lower is better).
-     }} \label{tab:social_lstm}
+    \caption{ {\small Results comparing vanilla LSTM and social LSTM in  unit space.
+\emph{Ave.
+disp.
+error} is the mean square error over all estimated points of a trajectory and the true points.
+\emph{Final disp.
+error} is the distance beween the predicted final destination and the true final destination at the end of the prediction period $T_F$.
+     }
+    } \label{tab:social_lstm}
 \end{table}
+
+%\vspace{\baselineskip}
+\noindent \textbf{Learning with auxiliary information:}
+ The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter.
+Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinate.
+ The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
+ Fig.~\ref{fig:final} shows the advantage of using SEG-LSTM: by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the recurrent net to output the most plausible path for vehicles and avoid collision with neighboring vehicles.
+
+%\vspace{\baselineskip}
+\noindent \textbf{Learning with social tensor:}
+On average, there is around 3 cars of interests in a high-way driving scene.
+Tab.~\ref{tab:social_lstm} shows that considering social interactions between cars improves the prediction accuracy than the isolation case. 
+And we believe that in a more complex social scene such as urban driving, the improvement will be more pronounced.
 
@@
 We propose a two-staged system incorporating various visual inputs with a temporally recurrent neural network.
-The recurrent network takes semantic information as an auxiliary input and further improve the predicting accuracy.
+The recurrent network takes semantic information as an auxiliary input and further improve the predicting accuracy with the incorporation of social factor.
 Future works include incorporating vehicle pose from the RGB/depth input as extra source of ``auxiliary information" and conducting experiments on the real-world images.
@@
 \section{Traffic participants detection}
-\begin{table}[H]\centering
+
+\begin{table*}\centering
 \small{
@@
 %\begin{tabular}{@{}llllllllllll@{}}\toprule
-\begin{tabu}{@{}lllll@{}}\toprule
-[-1pt] \tabucline[1pt]{1-5}
-\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
+\begin{tabu}{@{}llllllllllll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-12}
+\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
+\hline
 \multirow{3}{*}{Faster-RCNN}
-                                &   precision & 81.2    & 81.1  & 80.0\\
-                                &   recall    & 91.4    & 91.3  & 90.2\\
-                                &   f-score   & 86.0    & 86.0  & 84.8\\
-                                    \cline{2-5}
-\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
-                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
-                                &   f-score   & 87.1 &86.5  &84.0\\
-                                    \cline{2-5}
-\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
-                                &   recall  & 92.3 & 91.4 & 87.7\\
-                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
+                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
+                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
+                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+                    \cline{2-12}
+\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
+                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
+                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
+                    \cline{2-12}
+\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+
 \bottomrule
@@
 (1) both meta-architectures are robust to the cut-off confident thresholds.
-(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
+(2) SSD is more competitive in the collected dataset when targets of interest are large.
 }
@@
 }
-\end{table}
+\end{table*}
+
+%
+%\begin{table}[H]\centering
+%\small{
+%\ra{1.}
+%%\begin{tabular}{@{}llllllllllll@{}}\toprule
+%\begin{tabu}{@{}lllll@{}}\toprule
+%[-1pt] \tabucline[1pt]{1-5}
+%\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
+%\multirow{3}{*}{Faster-RCNN}
+%                                &   precision & 81.2    & 81.1  & 80.0\\
+%                                &   recall    & 91.4    & 91.3  & 90.2\\
+%                                &   f-score   & 86.0    & 86.0  & 84.8\\
+%                                    \cline{2-5}
+%\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
+%                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
+%                                &   f-score   & 87.1 &86.5  &84.0\\
+%                                    \cline{2-5}
+%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
+%                                &   recall  & 92.3 & 91.4 & 87.7\\
+%                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
+%\bottomrule
+%\end{tabu}
+%%\end{tabular}
+%\caption{
+%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
+%It can be seen that:
+%(1) both meta-architectures are robust to the cut-off confident thresholds.
+%(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
+%}
+%\label{tab:ssd_fasterrcnn}
+%}
+%\end{table}
 
@@
 Due to the high recall requirement for vehicle detection, there could be correspondingly higher false positive rate (\emph{e.g.}, double detection of red boxed in the far left).
-Instance association across multiple frames will discard the spurious detection.}
+Instance association across multiple frames will discard the spurious detection while remain temporal consistency.}
         }
@@
         \caption{
-        \small{The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.}
+        \small{The evaluation of 2D and 3D prediction. 2D: The bounding box is set to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict 3D occupancy.}
         }

### 2018-01-25 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
Rebuttal

@@
 % Include other packages here, before hyperref.
+
+% https://tex.stackexchange.com/questions/251186/is-there-a-way-to-toggle-comments
+% If there is always a blank line after then you could do (untested)
+% below will swallow the comment
+\def\tcom#1\par{}
+% below will show the comment
+%\def\tcom#1{}
 
@@
 \begin{document}
-
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here
+\title{DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving}  % **** Enter the paper title here
 
@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section{Introduction}
-We would first like to thank the reviewers for your valuable feedback which helped us to improve the analysis of the proposed method and the overall presentation of the paper.
-Due to space constraints with significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{http://www.texample.net/tikz/resources/}{new version of the paper}.
-we address only the major criticisms below.
+We would first like to thank the reviewers for the supportive comments and the constructive criticism.
+Your valuable feedbacks help us further improve the analysis of the proposed method and the overall presentation of the paper.
+Due to the significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{https://drive.google.com/open?id=18RwGHG-Rbwfv-4bwmjjSfSl9jAHI-vbM}{new version of the paper}.
 
-We have rewritten our contributions in Section 1 and make our contributions more clearly.
+% Because of the space constraint we address only the major comments below.
 
-We have restructured our methodology in section 3 and further explain the intuition behind the chosen architecture.
+\noindent \textbf{Modifications:} In what follows, we give an overview of the main changes made to the manuscript.
 
-\subsection{Common}
+\noindent (1) We have implemented SocialLSTM[2] as requested by R2 and preliminary results on 2D space exhibit that the ``social interaction" further improve the prediction accuracy.
 
-\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
-center of detected bounding box).}
+\noindent (2) We have restructured our methodology in section 3 and further explain the intuition behind the chosen architectures.
 
-\noindent We have re-implemented Social-LSTM for 2D data. blablabla details...
+\noindent (3) We have rewritten our contributions in Section 1 and make our contributions more clearly.
 
-\noindent \textbf{1) Unlike stated in the paper, vehicle tracking in images has been studied for years.
+\noindent \textbf{Common issues:} We would like to address the issues that are common to reviewers respectfully as follows:
+
+\tcom 
+\noindent \textbf{R1: Unlike stated in the paper, vehicle tracking in images has been studied for years.
 There are summary papers (e.g.
@@
 There is no mention of prior art.}
-\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}
-\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+\noindent \textbf{R1: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+\noindent \textbf{R2: Where are comparisons with other activity forecasting/trajectory prediction works?}
 
-We have restructured our related works. Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``RNN for sequence prediction" part.
+\noindent \textbf{Prior works on sequence prediction}:
+We found that the first version of the draft is indeed weak in presenting prior works on sequence prediction.
+We have restructured our related works.
+Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``Activity forecasting" part.
 
-\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
-\noindent \textbf{It is not clear if the dataset is released with the paper.}
+\tcom 
+\noindent \textbf{R1: It is not clear if the dataset is released with the paper.}
+\noindent \textbf{R2: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+\noindent \textbf{R2: Who else has experimented on the SYNTHIA dataset?
+Or are the authors the first ones?
+Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
 
-\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
+\noindent \textbf{SYNTHIA and release of the dataset}:
+\noindent Currently, experiments on the SYNTHIA dataset[27, 37] focus on single frame, static images for semantic labeling or scene representation.
+To our knowledge, our paper is the first attempt to utilize \emph{continuous video streams} for the prediction problem.
+We would like to release publicly-available dataset for prediction challenge based on SYNTHIA to spur future research upon paper publication.
 
-\noindent Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation.
-To our knowledge, our paper is the first attempt to utilize \textbf{\emph{continuous video streams}} for the prediction problems.
-We would like to release publicly-available prediction challenge based on Synthia to spur future research upon paper publication.
-
-\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
+\tcom 
+\noindent \textbf{R1: They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
+\noindent \textbf{R2: I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
 Kalal, K.
@@
 In TPAMI 2012?}
-\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
-\noindent \textbf{They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
+\noindent \textbf{R3: Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}
 
@@
 
-\subsection{R1}
+We would like to address the concerns respectfully as follows:
+%####################################################################################################################################################################################
+\noindent \textbf{R1}
 \noindent \textbf{3) 3 very similar LSTMs with different input}
@@
 
-\subsection{R2}
+%####################################################################################################################################################################################
+
+\noindent \textbf{R2}
+
+\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
+center of detected bounding box).}
+
+\noindent We have re-implemented Social-LSTM for 2D data. blablabla details...
 
@@
 
-\subsection{R3}
+%####################################################################################################################################################################################
+
+\noindent \textbf{R3}
 \noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}

### 2018-01-25 paper/cvpr2018/cvpr2018_3790.tex
Rebuttal

@@
 CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV} are two recent endeavours that take advantage of simulated environment to support development, training and validation of autonomous urban driving systems.
-A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is collected for investigating how useful synthetic images can be for semantic segmentation.
+A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark, HernandezBMVC17} is collected for investigating how useful synthetic images can be for semantic segmentation.
 %In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations.
@@
 \end{equation}
-This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM and training can be formulated as a neighboring batch update scheme.
+This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM.
 An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer.
-At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene.
+At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.
 
@@
                                                     &   Ave. disp. error      & Final disp. error   \\ \hline
-            {\small Vanilla LSTM }                 &    0.0257                &  0.0440   \\
-            {\small \textbf{Social LSTM} }         &  \textbf{0.0247}         & \textbf{0.0418}   \\
+            {\small Vanilla LSTM }                 &     0.0514              &  0.0880   \\
+            {\small \textbf{Social LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
           [-1pt] \tabucline[1pt]{1-3}
@@
 
-\begin{table*}\centering
+%\begin{table*}[H]\centering
+%\small{
+%\ra{1.}
+%%\begin{tabular}{@{}llllllllllll@{}}\toprule
+%\begin{tabu}{@{}llllllllllll@{}}\toprule
+%[-1pt] \tabucline[1pt]{1-12}
+%\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
+%\hline
+%\multirow{3}{*}{Faster-RCNN}
+%                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
+%                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
+%                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
+%                    \cline{2-12}
+%\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
+%                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
+%                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
+%                    \cline{2-12}
+%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
+%                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
+%                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
+%
+%\bottomrule
+%\end{tabu}
+%%\end{tabular}
+%\caption{
+%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
+%It can be seen that:
+%(1) both meta-architectures are robust to the cut-off confident thresholds.
+%(2) SSD is more competitive in the collected dataset when targets of interest are large.
+%}
+%\label{tab:ssd_fasterrcnn}
+%}
+%\end{table*}
+
+\begin{table}[H]\centering
 \small{
@@
 %\begin{tabular}{@{}llllllllllll@{}}\toprule
-\begin{tabu}{@{}llllllllllll@{}}\toprule
-[-1pt] \tabucline[1pt]{1-12}
-\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
-\hline
+\begin{tabu}{@{}lllll@{}}\toprule
+[-1pt] \tabucline[1pt]{1-5}
+\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
 \multirow{3}{*}{Faster-RCNN}
-                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
-                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
-                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
-                    \cline{2-12}
-\multirow{3}{*}{SSD (NMS:0.60)}&   precision &  82.1  & 81.9  & 81.8  & 81.8  & 81.6  & 81.1 & 80.9  & 80.4 & 80.0  & 79.2\\
-                            &    recall   & \textbf{92.7} & 92.5 & 92.3  & 92.3 & 92.0 & 91.5 & 91.3 & 90.7  & 90.2 & 89.4\\
-                            &    f-score  & 87.1  & 86.9  & 86.7   &86.7&86.5& 86.0  & 85.8 &85.2 & 84.8 &84.0\\
-                    \cline{2-12}
-\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
-                                &    recall  & 92.3  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
-                                &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
-
+                                &   precision & 81.2    & 81.1  & 80.0\\
+                                &   recall    & 91.4    & 91.3  & 90.2\\
+                                &   f-score   & 86.0    & 86.0  & 84.8\\
+                                    \cline{2-5}
+\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
+                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
+                                &   f-score   & 87.1 &86.5  &84.0\\
+                                    \cline{2-5}
+\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
+                                &   recall  & 92.3 & 91.4 & 87.7\\
+                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
 \bottomrule
@@
 (1) both meta-architectures are robust to the cut-off confident thresholds.
-(2) SSD is more competitive in the collected dataset when targets of interest are large.
+(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
 }
@@
 }
-\end{table*}
-
-%
-%\begin{table}[H]\centering
-%\small{
-%\ra{1.}
-%%\begin{tabular}{@{}llllllllllll@{}}\toprule
-%\begin{tabu}{@{}lllll@{}}\toprule
-%[-1pt] \tabucline[1pt]{1-5}
-%\multicolumn{2}{c}{conf}                       & 0.50    &0.70   & 0.95\\ \hline
-%\multirow{3}{*}{Faster-RCNN}
-%                                &   precision & 81.2    & 81.1  & 80.0\\
-%                                &   recall    & 91.4    & 91.3  & 90.2\\
-%                                &   f-score   & 86.0    & 86.0  & 84.8\\
-%                                    \cline{2-5}
-%\multirow{3}{*}{SSD (NMS:0.60)} &   precision &  82.1   & 81.6  & 79.2 \\
-%                                &   recall    & \textbf{92.7} & 92.0 & 89.4 \\
-%                                &   f-score   & 87.1 &86.5  &84.0\\
-%                                    \cline{2-5}
-%\multirow{3 }{*}{SSD (NMS:0.45)}&   precision & \textbf{92.0} & 91.1 & 87.4\\
-%                                &   recall  & 92.3 & 91.4 & 87.7\\
-%                                &   f-score  & \textbf{92.2}& 91.3 & 87.6\\
-%\bottomrule
-%\end{tabu}
-%%\end{tabular}
-%\caption{
-%Comparison of SSD and Faster-RCNN for vehicle detection on the collected SYNTHIA dataset.
-%It can be seen that:
-%(1) both meta-architectures are robust to the cut-off confident thresholds.
-%(2) SSD is more competitive in the collected dataset when targets of interest are comparatively plarge.
-%}
-%\label{tab:ssd_fasterrcnn}
-%}
-%\end{table}
+\end{table}
 
@@
 \section{2D and 3D occupancy grid}
-\begin{figure}[h]
+\begin{figure}[t]
         \centering

### 2018-01-25 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
link update

@@
 Your valuable feedbacks help us further improve the analysis of the proposed method and the overall presentation of the paper.
-Due to the significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{https://drive.google.com/open?id=18RwGHG-Rbwfv-4bwmjjSfSl9jAHI-vbM}{new version of the paper}.
+Due to the significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{https://drive.google.com/open?id=1D18rOofLQqZKBsOwkljSOUF_CqZgGetB}{new version of the paper}.
+% and We would like to address the concerns respectfully as follows.
 
@@
 
-\noindent (1) We have implemented SocialLSTM[2] as requested by R2 and preliminary results on 2D space exhibit that the ``social interaction" further improve the prediction accuracy.
+\tcom
+\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
+center of detected bounding box).}
+
+\noindent (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space exhibit that the inclusion of ``social interaction" further improves the prediction accuracy.
 
@@
 
-\noindent \textbf{Common issues:} We would like to address the issues that are common to reviewers respectfully as follows:
+%\noindent \textbf{Common issues:} 
+We would like to address the issues that are common to reviewers respectfully as follows:
 
@@
 \noindent \textbf{SYNTHIA and release of the dataset}:
-\noindent Currently, experiments on the SYNTHIA dataset[27, 37] focus on single frame, static images for semantic labeling or scene representation.
+\noindent Currently, experiments on the SYNTHIA dataset [27, 37] focus on single frame, static images for semantic labeling or scene representation.
 To our knowledge, our paper is the first attempt to utilize \emph{continuous video streams} for the prediction problem.
@@
 
-\noindent  Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking.
-In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
-Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations.
-This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
+\noindent \textbf{Instance association via tracking}:
+\noindent  We would like to clarify the overloaded term ``tracking by detection" used in our paper.
+Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking: in order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
+This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames.
 In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
 Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting.
-Hence the tracker is served solely as instance associator for the traffic participant.
+Hence the tracker is served solely as\emph{ instance associator} for the traffic participant.
 
-We would like to address the concerns respectfully as follows:
+% We would like to address the concerns respectfully as follows:
 %####################################################################################################################################################################################
-\noindent \textbf{R1}
+\tcom
 \noindent \textbf{3) 3 very similar LSTMs with different input}
@@
 
-\noindent Explain the intuition....
+\noindent \textbf{R1:} Explain the intuition of three LSTMs.
 
 %####################################################################################################################################################################################
+\tcom
 
-\noindent \textbf{R2}
-
-\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g.
-center of detected bounding box).}
-
-\noindent We have re-implemented Social-LSTM for 2D data. blablabla details...
-
-\noindent \textbf{SocialLSTM used ``Avg. disp. Error", ``Avg. non-linear disp. error" , and ``final disp. Error" What was the justification for the metrics the authors chose?}
+\noindent \textbf{R2:}
 

### 2018-01-25 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
rebuttal

@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-We would first like to thank the reviewers for the supportive comments and the constructive criticism.
-Your valuable feedbacks help us further improve the analysis of the proposed method and the overall presentation of the paper.
-Due to the significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{https://drive.google.com/open?id=1D18rOofLQqZKBsOwkljSOUF_CqZgGetB}{new version of the paper}.
+We would first like to thank the reviewers for the supportive comments and the constructive criticisms.
+Your valuable feedbacks help us further improve the analysis and the overall presentation of the paper.
+Because of the significant improvement made to the new version of the paper, we would kindly ask reviewers refer to the \href{https://www.jianguoyun.com/p/De5QypAQ9cyhBhjb10E}{new version of the paper}.
+Due to space constraint, we address only the major
+criticisms below.
 % and We would like to address the concerns respectfully as follows.
@@
 
-\noindent \textbf{Modifications:} In what follows, we give an overview of the main changes made to the manuscript.
+\noindent \textbf{Modifications:} (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space exhibit that the inclusion of ``social interaction" further improves the prediction accuracy.
+(2) We have restructured our methodology in Sec.
+3 and further explain the intuition behind the chosen architectures.
 
+% In what follows, we give an overview of the main changes made to the manuscript.
 \tcom
@@
 center of detected bounding box).}
+\noindent \textbf{The details about the fusion of location” and semantic” information into the LSTM hidden state seemed missing (was a bit vague).
+A figure of the architecture of the SEG-LSTM would go a long way in clarifying this (or are the authors using Xu et al.'s "End-to-end Learning of Driving Models from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's group?).}
 
-\noindent (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space exhibit that the inclusion of ``social interaction" further improves the prediction accuracy.
+\noindent 
+\tcom
+\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}
+\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
+\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here.
+In general a lot of methodology detail is actually in section 4 (implementation details).
+Maybe consider reorganizing a little bit.}
 
-\noindent (2) We have restructured our methodology in section 3 and further explain the intuition behind the chosen architectures.
+%\noindent (2) We have restructured our methodology in Sec. 3 and further explain the intuition behind the chosen architectures.
 
-\noindent (3) We have rewritten our contributions in Section 1 and make our contributions more clearly.
+%\noindent (3) We have rewritten and crystalized our contributions at the end of Sec. 1.
 
 %\noindent \textbf{Common issues:}
-We would like to address the issues that are common to reviewers respectfully as follows:
+%We would like to address the issues that are common to reviewers respectfully as follows:
 
@@
 \noindent \textbf{Prior works on sequence prediction}:
-We found that the first version of the draft is indeed weak in presenting prior works on sequence prediction.
+We agree that the first version of the draft is indeed weak in presenting prior works on sequence prediction.
 We have restructured our related works.
-Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``Activity forecasting" part.
+Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``Activity forecasting" part in Sec 2.
 
@@
 Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
+\noindent \textbf{In the SocialLSTM paper Related Work section, there are about 20 sources that focus on Activity forecasting.}
 
@@
 \noindent \textbf{R1: They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
-\noindent \textbf{R2: I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z.
+\noindent \textbf{R2: I was a bit confused about why the tracking-by-detection” framework was novel -- how is it different from tracking-learning-detection” (TLD),from Z.
 Kalal, K.
@@
 \noindent \textbf{Instance association via tracking}:
-\noindent  We would like to clarify the overloaded term ``tracking by detection" used in our paper.
-Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking: in order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
-This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames.
+\noindent  We would like to clarify the overloaded term ``tracking by detection" used in the first version of our manuscript.
+Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking\footnote{In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame.
+This excessive update strategy causes both lower frame-rates and degradation of robustness due to model drifting caused by scale variations, deformations, and out-of-plane rotations.}.
 In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
-Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting.
+Therefore, with this extra source of information, we propose to use the neural nets object detection template to forcibly update the tacker's model to overcome the problem of model drifting.
 Hence the tracker is served solely as\emph{ instance associator} for the traffic participant.
+During our qualitative examination, we find out that this simple combination achieves more robust result for instance association than those of state-of-the-art ``class-agnostic" trackers.
 
@@
 
-\noindent \textbf{R1:} Explain the intuition of three LSTMs.
+\noindent \textbf{R1:}
+Explain the intuition of three LSTMs.
 
@@
 \tcom
-
-\noindent \textbf{R2:}
-
-\noindent The ``average displacement error" is essentially the same as the ``center error" in Tab.3 of our paper and the subtle difference is that the former is in unit space and the latter is in pixel space.
-Similarly ``Final displacement error" is the last frame's ``center error" is unit space.
-``average non-linear displacement error"
-
 \noindent \textbf{Line 124 - The authors discuss a "lack of proper metrics for evaluating the temporal prediction result." How are the current metrics poorly suited to the task? What would be better?}
 
-\noindent \textbf{In the SocialLSTM paper’s Related Work section, there are about 20 sources that focus on “Activity forecasting”}
+\noindent \textbf{R2:} Our preliminary result using 2D information shows that social tensor generates slightly better prediction than the isolation case (Tab.4, Fig.7, bottom row).
+Note that our mean error in unit space is much lower than the pedestrian trajectory prediction in Social-LSTM[2] (0.049 vs.
+0.27).
+We analyze the following two factors:  car trajectory is a simpler case: both in time (prediction frame is 8 in our case and 12 in [2]) and in space (car trajectory is more linear and confined in our problem setting).
+However, the relevant improvement using social tensor is lower for the car trajectory prediction (4\% vs.
+38\%).
+We reckon it's due to  only around 3 cars of interests on average appearing in our high-way driving scene.
+And we believe in a more complex social scene such as urban driving, the improvement will be more pronounced.
 
-\noindent \textbf{The details about the fusion of “location” and “semantic” information into the LSTM hidden state seemed missing (was a bit vague).
-A figure of the architecture of the SEG-LSTM would go a long way in clarifying this (or are the authors using Xu et al.'s "End-to-end Learning of Driving Models from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's group?).}
+\tcom
+\noindent \textbf{SocialLSTM used avg. disp. Error”, avg. non-linear disp. error” , and final disp. Error” what was the justification for the metrics the authors chose?}
 
+\noindent \textbf{R2:} The ``avg.
+disp.
+error" is essentially the same as the ``center error" in Tab.2 of our paper.
+The subtle difference is that the former is in unit space and the latter is in pixel space.
+The ``avg.
+non-linear disp.
+error" considers the non-linear turns from human-human interactions and the heuristic for choosing the non-linear regions of a trajectory is problem dependent.
+The metrics adopted in our paper consider the coverage of the target from a tracking perspective.
+Moreover, the 3D occupancy grid is more pertinent in the context of autonomous driving than the 2D co-ordinates.
+
+\tcom
 \noindent \textbf{How is this more than just an engineering pipeline, combining tracking (distilling bounding boxes to coordinates), and then adding an LSTM?
 SocialLSTM already did the second part in principle.}
-
-\noindent \textbf{Why are scene semantics privileged (which you also call “auxiliary”) information?
-If the pipeline relies on fusing the “location” and “semantic” stream, if privileged information is missing at test time, then won’t the pipeline break?
+\noindent \textbf{Why are scene semantics privileged (which you also call auxiliary”) information?
+If the pipeline relies on fusing the location” and semantic” stream, if privileged information is missing at test time, then wont the pipeline break?
 (privileged information is usually present at train time, but absent at test time).}
-
  \noindent \textbf{Can multiple objects be tracked at once, or just one?
@@
 What was the average number of objects in each SYNTHIA scene frame?}
+  \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to predict cars future odometry given previous egomotion visual input”.
+But the paper is about prediction of other vehicles’ trajectories, not about predicting one own car odometry (which is different).}
 
- \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to “predict car’s future odometry given previous egomotion visual input”.
-But the paper is about prediction of other vehicles’ trajectories, not about predicting one’s own car odometry (which is different).}
-
-\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}
+ \noindent \textbf{R2:} Semantics in our paper are presented both in the training and the test time and we rectified them as as ``auxiliary" information.
+They are used directly as a tensor embedding for the recurrent network.
+ In the supplementary material we try to avoid extra cluttering, hence we visualized only one object being tracked.
+Nonetheless, multiple objects are detected and tracked simultaneously in our system and we redraw the figures to make multiple tracking more conspicuous.
 
@@
 
-\noindent \textbf{R3}
-\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
-\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here.
-In general a lot of methodology detail is actually in section 4 (implementation details).
-Maybe consider reorganizing a little bit.}
+%We have refined our contributions in the introduction section and restructured the methodology section. We have also corrected the grammatical misuses accordingly.
 
-\noindent We thank the reviewer for the very meticulous review.
-We have refined our contributions in the introduction section and restructured the methodology section.
-We have also corrected the grammatical misuses accordingly.
-
+\tcom
 \noindent \textbf{In a real car accurate depth information might not be available.
@@
 \noindent \textbf{Do you think the results you obtained with the Synthia data will transfer to real-world data?}
-\noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with ‘real’ physics and photo-realism similar to Synthia.
-It would be interesting to implement this system and evaluate ‘real-world’ performance.}
+\noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with real’ physics and photo-realism similar to Synthia.
+It would be interesting to implement this system and evaluate real-world’ performance.}
 
-\noindent We have indeed noticed the recently released photo-realistic simulators CARLA~\cite{CARLA} and Sim4CV~\cite{Sim4CV}.
+\noindent \textbf{R3:} We thank the reviewer for the very meticulous review.
+We have indeed noticed the recently released photo-realistic simulators CARLA and Sim4CV.
 And we found that CARLA is especially suited as a further extension to verify our proposed system due to the availability of continuous video streams and ground truth segmentation.
-In terms of transferring to real-world data, from the semantic segmentation results of Synthia, we have observed that model trained on synthetic dataset produced good segmentations by itself on real datasets, and dramatically boosted accuracy in combination with real data.
+%In terms of transferring to real-world data, 
+From the semantic segmentation results of Synthia, we have observed that model trained on synthetic dataset produced good segmentations by itself on real datasets, and dramatically boosted accuracy in combination with real data.
 Hence, we believe the hybrid of synthetic data and real-world data would be the most data efficient and promising way for the model generalization.
-Model verification on public real-world datasets, e.g., Comma.ai~\cite{santana2016learning} Udacity~\cite{udacity} dataset would be our forthcoming imminent works.
+%Model verification on public real-world datasets, e.g., Comma.ai~\cite{santana2016learning} Udacity~\cite{udacity} dataset would be our forthcoming imminent works.
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
+%
+%{\small
+%\bibliographystyle{ieee}
+%\bibliography{egbib}
+%}
 

### 2018-01-25 paper/cvpr2018/cvpr2018_3790.tex
rebuttal

@@
 Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
-In this paper, we raise the question of ``can we predict the car's future odometry given previous egomotion visual input?".
+In this paper, we raise the question of ``can we predict other traffic participant's future trajectory given previous egomotion visual input?".
 The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
@@
         We propose a system to predict future trajectories of vehicles.
-Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
+Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream recurrent neural network is trained to generate future trajectory.}}
         \label{fig:pull_figure}

### 2018-01-26 paper/cvpr2018/cvpr2018_3790.tex
update

@@
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
+        \includegraphics[width=0.42\textwidth]{figures/pull_figure.pdf}
         \caption{ \small{
@@
         \centering
-        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
+        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
         \caption{
@@
 
-We first describe the overall framework for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
-Our goal is via collecting visual information from the past frames to predict the traffic participants future trajectory.
-Fig.~\ref{fig:framework} shows the overall architecture of the proposed framework.
+We first formalized the proposed problem and describe the overall framework as shown in Fig.~\ref{fig:framework}.
 
@@
         \centering
-        \includegraphics[width=0.45\textwidth]{figures/SEGLSTM.pdf}
+        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
         \caption{
@@
 \begin{equation}
-j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times \mathcal{A}
+j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times convnet(\mathcal{A})
 \label{eq:SEG-LSTM}
@@
         \centering
-        \includegraphics[width=0.95\textwidth]{figures/prediction.pdf}
+        \includegraphics[width=0.95\textwidth]{figures/prediction_2.pdf}
         \caption{
-        \small{The prediction results in SYNTHIA dataset. {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
-        The results using SEG-LSTM network show that by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the predicted trajectory from the recurrent net within the most plausible path.
-Top: SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles.
-Bottom:  SEG-LSTM confines the possible car trajectories along the space above road.}
+        \small{Visualization of prediction results.
+Top two rows show the advantage of using semantics in temporal model: {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
+        SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles (row 1) and confines the plausible car trajectory along the space above road (row 2).
+        Row 3 and 4 show the benefit  of incorporating social factors.
+        Row 3 is the visualization for vanilla LSTM.
+The bottom left car prediction (denoted by red dots) is considered in isolation and could surpass the host car, moving dangerously close to the two front cars.
+Row 4 is the visualization of social LSTM: by considering two front cars in the scene, the predicted keeps the red dot car in a safer distance from two front cars.
+        }
         }

### 2018-01-26 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex
rebutaal

@@
 Because of the significant improvement made to the new version of the paper, we would kindly ask reviewers refer to the \href{https://www.jianguoyun.com/p/De5QypAQ9cyhBhjb10E}{new version of the paper}.
-Due to space constraint, we address only the major
-criticisms below.
+We address only the major criticisms below.
 % and We would like to address the concerns respectfully as follows.
@@
 
-\noindent \textbf{Modifications:} (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space exhibit that the inclusion of ``social interaction" further improves the prediction accuracy.
+\noindent \textbf{Modifications:} (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space show that the inclusion of ``social interaction" further improves the prediction accuracy.
 (2) We have restructured our methodology in Sec.
@@
 We have restructured our related works.
-Specifically, we have supplemented works on activity forecasting/trajectory prediction works in the ``Activity forecasting" part in Sec 2.
+Specifically, we have supplemented prior works on activity forecasting/trajectory prediction in Sec 2.
 
@@
 Therefore, with this extra source of information, we propose to use the neural nets object detection template to forcibly update the tacker's model to overcome the problem of model drifting.
-Hence the tracker is served solely as\emph{ instance associator} for the traffic participant.
-During our qualitative examination, we find out that this simple combination achieves more robust result for instance association than those of state-of-the-art ``class-agnostic" trackers.
+Hence the tracker is served solely as\emph{ instance associator}.
+During our qualitative examination, we find out that this combination achieves more robust result for instance association than using ``class-agnostic" tracker alone.
 
@@
 
-\noindent \textbf{R1:}
-Explain the intuition of three LSTMs.
+\noindent \textbf{R1:} To our knowledge, our paper is the first attempt to take advantage of different level of abstractions from multiple streams to tackle the trajectory predictions with the practical use-case in mind (e.g.
+reaction time of humans).
+The limit of FtF temporal model shares the similarity mentioned in [4]: sampling frame by frame conditioned on the state and the previous correct token with an \textless EOS\textgreater token as a prerequisite.
+We stipulate the length of the prediction fixed as T.
+Hence we have the assumption that current state is complete (Markovian), in the sense it contains all historical information required for predicting the future trajectory and the experimental results verify our intuition.
+Hence, we believe our paper serves as a good proof-of-concept and opens the doors for this challenging yet practical trajectory problem in the context of autonomous driving.
 
@@
 38\%).
-We reckon it's due to  only around 3 cars of interests on average appearing in our high-way driving scene.
+We reckon it's due to  only around 3 cars of interests on average appearing in our high-way driving scenario.
 And we believe in a more complex social scene such as urban driving, the improvement will be more pronounced.
@@
  \noindent \textbf{R2:} Semantics in our paper are presented both in the training and the test time and we rectified them as as ``auxiliary" information.
-They are used directly as a tensor embedding for the recurrent network.
+They are used directly as a tensor embedding via a convnet.
  In the supplementary material we try to avoid extra cluttering, hence we visualized only one object being tracked.

### 2018-01-26 paper/cvpr2018/cvpr2018_3790.tex
Final version pdf

@@
 
+\begin{figure*}[t]
+        \centering
+        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
+        \caption{
+        \small{The framework for the proposed vehicle future trajectory prediction system.
+The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car.
+Target vehicles' sequential bounding boxes are extracted by detection \& tracking module.
+Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
+        }
+        \label{fig:framework}
+\end{figure*}
 \noindent \textbf{Instance association} Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.
@@
 This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
-In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
+
+%In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists).
 Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting.
@@
 
-\begin{figure*}[t]
-        \centering
-        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
-        \caption{
-        \small{The framework for the proposed vehicle future trajectory prediction system.
-The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car.
-Target vehicles' sequential bounding boxes are extracted by detection \& tracking module.
-Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
-        }
-        \label{fig:framework}
-\end{figure*}
 %\noindent \textbf{RNN for sequence prediction}
@@
 Social-LSTM~\cite{alahi2016social} focus on modeling dynamics crowd interactions for path prediction by introducing a ``social tensor" from a spatial-temporal neighborhood.
-Based on the social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
+Based on the Social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
 %~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation.
@@
 \subsection{Problem formulation}
-\begin{figure}[t]
-        \centering
-        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
-        \caption{
-        \small{Illustrations of three temporal networks.
-$\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.
-Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with auxiliary information as input $\mathcal{A}$.
-The social tensor $\mathcal{S}$ can be inserted into existing recurrent networks .}
-        }
-        \label{fig:lstm}
-\end{figure}
 
@@
 %We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
-Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $\mathcal{J_H}=\{j_p^t\}, t=1,\dots, T $ with auxiliary information $ \mathcal{A}=\{a_p^t\},t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\mathcal{J_F}=\{j_p^t\}, t={T+1}, \ldots, T_F$:
+Formally, our problem can be defined as a mapping $\mathcal{M}$ from historical trajectory $\mathcal{J_H}=\{j_p^t\}, t=1,\dots, T $ with auxiliary information $ \mathcal{A}=\{a_p^t\},t=1,\dots, T $ for traffic participant $p$ to the future trajectory $\mathcal{J_F}=\{j_p^t\}, t={T+1}, \ldots, T_F$:
 
@@
 %Auxiliary information $\mathcal{A}$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.
-
 \begin{figure}[t]
         \centering
-        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
+        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
         \caption{
-        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics used under the context of high-way driving).
-The higher level semantics are extracted through a four-layer CNN, producing a joint representation of the auxiliary semantic information and the co-ordinate trajectory information.}
+        \small{Illustrations of three temporal networks.
+$\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.
+Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with auxiliary information as input $\mathcal{A}$.
+The social tensor $\mathcal{S}$ can be inserted into existing recurrent networks .}
         }
-        \label{fig:SEGLSTM}
+        \label{fig:lstm}
 \end{figure}
+
 \subsection{Sequence modeling}
@@
 For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells.
-A ``social pooling tensor" that implicitly reasons about the motion of neighboring traffic participants can be inserted into existing recurrent network architectures without any extra training supervision or modification to the optimization process as shown in Fig.~\ref{fig:lstm}.
+A ``social pooling tensor" that implicitly reasons the motion of neighboring traffic participants can be inserted into existing recurrent network architectures without any extra training supervision or modification to the optimization process as shown in Fig.~\ref{fig:lstm}.
 The first two models take sequential 3D occupancy as input.
@@
 At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid.
-The model is frame to frame Markovian and the next frame trajectory $j_{t+1}$ can be estimated as:
+The model is frame-to-frame Markovian and the next frame trajectory $j_{t+1}$ can be estimated as:
 \begin{equation}
@@
 
+\begin{figure}[t]
+        \centering
+        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
+        \caption{
+        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics  under the context of high-way driving).
+The higher level semantics are extracted through a four-layer CNN.
+A joint representation is produced by the auxiliary semantic information and the coordinates trajectory information.}
+        }
+        \label{fig:SEGLSTM}
+\end{figure}
 \vspace{\baselineskip}
@@
  takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$.
-The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embedding with higher level semantic information.
+The second LSTM layer fuses the output from the bottom-most LSTM that encodes coordinates embedding with higher level semantic information.
 With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
 \begin{equation}
-j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times convnet(\mathcal{A})
+j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times \mathcal{A}
 \label{eq:SEG-LSTM}
@@
  Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}.
-The higher level semantic is extracted through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the co-ordinate trajectory information.
- As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information.
-So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both co-ordinate information and the semantic information.
+The higher level semantic is extracted through a four-layer CNN.
+A joint representation is produced  by the semantic auxiliary information and the coordinates trajectory information.
+ As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the coordinates information.
+So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both coordinates information and the semantic information.
 %Results show that the SEG-LSTM model performs better than the other two temporal model.
 
-Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and directs the recurrent net future trajectory prediction.
+Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and embeds them to a hidden-state tensor by a convolutional neural network.
 
@@
 While pooling the information, the spatial information is preserved by grid based pooling.
+
 The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene.
@@
 \end{equation}
-This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM.
+This social pooling layer does not introduce any additional parameters and can be inserted into the hidden layer of LSTM.
 An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer.
-At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.
+At every time-step, the updates are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.
 
@@
 Grid size is set as 4 and the embedding size is 64 so the social tensor $\mathcal{S}$ is a $4\times 4\times 64$ matrix.
-The learning is set to 0.001 and RMS-prop~\cite{tieleman2012lecture} with a gradient clipping of 3 to avoid divergence.
+The learning rate is set to 0.001 with RMS-prop~\cite{tieleman2012lecture} with a gradient clipping of 3 to avoid divergence.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Top two rows show the advantage of using semantics in temporal model: {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
-        SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles (row 1) and confines the plausible car trajectory along the space above road (row 2).
+        SEG-LSTM can help detecting neighboring vehicles and restrict the viable path outside the space occupied by other vehicles (row 1); and confine the plausible car trajectory along the space above road (row 2).
         Row 3 and 4 show the benefit  of incorporating social factors.
-        Row 3 is the visualization for vanilla LSTM.
-The bottom left car prediction (denoted by red dots) is considered in isolation and could surpass the host car, moving dangerously close to the two front cars.
-Row 4 is the visualization of social LSTM: by considering two front cars in the scene, the predicted keeps the red dot car in a safer distance from two front cars.
+        Row 3 is the visualization of vanilla LSTM: the bottom left car predictions (denoted by red dots) are considered in isolation, moving dangerously close to the two front cars.
+        Row 4 is the visualization of Social-LSTM: by considering two front cars in the scene, the prediction keeps the red dot car in a safer distance from the two front cars.
         }
@@
             {\small Vanilla LSTM }                 &     0.0514              &  0.0880   \\
-            {\small \textbf{Social LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
+            {\small \textbf{Social-LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
           [-1pt] \tabucline[1pt]{1-3}
@@
 
-    \caption{ {\small Results comparing vanilla LSTM and social LSTM in  unit space.
+    \caption{ {\small Results comparing vanilla LSTM and Social-LSTM in  unit space.
 \emph{Ave.
@@
  The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter.
-Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinate.
+Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinates.
  The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
@@
 On average, there is around 3 cars of interests in a high-way driving scene.
-Tab.~\ref{tab:social_lstm} shows that considering social interactions between cars improves the prediction accuracy than the isolation case.
+Tab.~\ref{tab:social_lstm} shows that considering social interactions between cars improves the prediction accuracy over the isolation case.
 And we believe that in a more complex social scene such as urban driving, the improvement will be more pronounced.
